\documentclass[legalpaper, 8pt]{book}
\usepackage[chordbk]{songbook}
\usepackage[legalpaper, layoutheight=12.8in, layoutwidth=8.5in]{geometry}
\pagestyle {empty}
\newcommand{\RelDate}{23~October,~2012}
\newcommand{\RevDate}{\today}\begin{document}
\makeTitleIndex         %% Title and First Line Index.
\makeTitleContents      %% Table of Contents.
\makeKeyIndex           %% Index of song by key.
\makeArtistIndex        %% Index of song by artist.
\font\myTinySF=cmss8    at  8pt
\font\myHugeSF=cmssbx10 at 22pt
\setlength{\oddsidemargin}{0.5pt} 
\setlength{\evensidemargin}{0.5pt}
\newcommand{\myTitleFont}{\Huge\myHugeSF}
\newcommand{\mySubTitleFont}{\large\sf}
\special{papersize=6in, 10.24in}
\begin{song}{Above All}{G}
{Paul Baloche}
{Paul Baloche}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G	}{Abo}v\Ch{C}{e a}ll powers,

\Ch{D}{Abo}ve all \Ch{G}{kin}gs,

Above all \Ch{C}{nat}ure and \Ch{D		}{all} \Ch{G}{cre}ated things,

A\Ch{D/F#}{bov}e all \Ch{Em}{wis}dom and \Ch{D}{all} the ways of \Ch{C}{man},  \Ch{G/B}{   }

\Ch{Am}{You} were here \Ch{Am/G}{bef}ore the \Ch{D/F#}{wor}ld began.

\Ch{G}{Abo}ve all \Ch{C}{kin}gdoms,

\Ch{D}{Abo}ve all \Ch{G}{thr}ones,

Above all \Ch{C	}{won}ders \Ch{D		}{the} worl\Ch{G}{d h}as ever known.

A\Ch{D/F#}{bov}e all \Ch{Em}{wea}lth and \Ch{D}{tre}asures of the \Ch{C}{ear}th,  \Ch{G/B}{   }

\Ch{Am}{The}re's no way to \Ch{Am/G}{mea}sure what You're \Ch{B7/F#}{wor}th.
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Cru}ci\Ch{C}{fie}d

\Ch{D/F#}{Lai}d behind the \Ch{G}{sto}ne

You lived to \Ch{C}{die}

\Ch{D/F#}{Rej}ected and \Ch{G}{alo}ne

\Ch{D/F#}{Lik}e a \Ch{Em}{Ros}e

\Ch{D}{Tra}mpled on the \Ch{C}{gro}und \Ch{G/B}{   }

You took the \Ch{Am7}{fal}l

And \Ch{G/B}{tho}ught of \Ch{C}{me }   \Ch{D}{   }

Above \Ch{G}{all}
\end{SBVerse}

\end{song}\begin{song}{Agnus Dei}{G}
{Michael W. Smith}
{Michael W. Smith}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{All}eluia, Allel\Ch{C}{uia}

For our Lord God Almight\Ch{G}{y r}eigns

Alleluia, All\Ch{C}{elu}ia

For our Lord God Almight\Ch{G}{y r}eigns

Allel\Ch{C}{uia}

Ho\Ch{G}{ly,} \Ch{C}{Hol}\Ch{G}{y  }

Are You \Ch{C}{Lor}d \Ch{G	}{God} Almig\Ch{D	}{hty}

Worthy is the \Ch{C}{Lam}b
\end{SBVerse}
\begin{SBVerse}
Worthy is the Lamb

You are Ho\Ch{G}{ly }

\Ch{C}{Hol}\Ch{G}{y a}re You \Ch{C}{Lor}d \Ch{G}{God} Almight\Ch{D}{y  }

Worthy is the L\Ch{C}{amb}
\end{SBVerse}
\begin{SBVerse}
Worthy is the Lamb

Am\Ch{G}{en }
\end{SBVerse}
\end{song}\begin{song}{All Because of Jesus}{C}
{Steve Fee}
{Steve Fee}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{   }Giver of \Ch{F}{eve}ry breath I br\Ch{C}{eat}he

Author of a\Ch{F}{ll }eternit\Ch{C}{y  }

Giver of e\Ch{F}{ver}y perfect \Ch{Am7}{thi}ng

to you be the \Ch{Gsus}{glo}ry \Ch{G/B}{   }
\end{SBVerse}
\begin{SBVerse}
Maker of h\Ch{F}{eav}en and of e\Ch{C}{art}h

no one can c\Ch{F}{omp}rehend your w\Ch{C}{ort}h

King over \Ch{F}{all} the uni\Ch{Am7}{ver}se

to you be the \Ch{Gsus}{glo}ry  \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
And \Ch{Am7}{ I } am alive beca\Ch{Em}{use} I'm alive in\Ch{Fmaj9}{ Yo}u
\end{SBVerse}
\begin{SBVerse}
It's \Ch{C}{all} because of J\Ch{Dm7}{esu}s I'm a\Ch{F2}{liv}e

it's \Ch{C}{all} because the \Ch{Dm7}{blo}od of Jesus C\Ch{F2}{hri}st

that \Ch{Bb}{cov}ers me and r\Ch{F/A}{ais}ed this dead man's l\Ch{C}{ife}

it's \Ch{Bb}{all} because of J\Ch{F/A}{esu}s  (To Bridge)

I'm al\Ch{F}{ive}  \Ch{C}{  I}'m al\Ch{F}{ive}  \Ch{C}{  I}'m al\Ch{F}{ive}   \Ch{Am7}{   }  \Ch{Gsus}{   }   \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{F}{Eve}ry sunrise s\Ch{G}{ing}s Your p\Ch{Am7}{rai}se

the \Ch{F}{uni}verse cries o\Ch{G}{ut }your pr\Ch{Dm7}{ais}e

I'm s\Ch{F}{ing}ing freedom a\Ch{G}{ll }my d\Ch{Am7}{ays}

\Ch{Bb}{now} that I'm a\Ch{Gsus}{liv}e
\end{SBVerse}
\end{song}\begin{song}{All Creatures Of Our God And King}{C}
{William Henry Draper}
{William Henry Draper}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{All} creatures of our God and King,

\Ch{G}{Lif}t up your v\Ch{C2}{oic}e and with us s\Ch{D}{ing},

\Ch{C2}{All}e\Ch{G}{lui}a! \Ch{C2}{All}el\Ch{D}{uia}!

\Ch{G}{Tho}u burning s\Ch{C2}{un }with golden be\Ch{D}{am,}

\Ch{G}{Tho}u silver mo\Ch{C2}{on }with softer gl\Ch{D}{eam}!

\Ch{C2}{O p}rai\Ch{G}{se }Him, O\Ch{C2}{ pr}ais\Ch{G}{e H}im!

\Ch{C2}{All}el\Ch{G}{uia}! \Ch{C2}{All}el\Ch{G}{uia}! \Ch{C2}{All}elu-\Ch{G}{u-i}a!
\end{SBVerse}
\begin{SBVerse}
Thou rushing wind that art so strong,

Ye clouds that sail in heav'n along,

O praise Him! Alleluia!

Thou rising morn, in praise rejoice,

Ye lights of evening, find a voice!

O praise Him, O praise Him!

Alleluia! Alleluia! Alleluia!
\end{SBVerse}
\begin{SBVerse}
And all ye men of tender heart,

Forgiving others, take your part,

O sing ye! Alleluia!

Ye who long pain and sorrow bear,

Praise GOd and on Him cast your care!

O praise Him, O praise Him!

Alleluia! Alleluia! Alleluia!
\end{SBVerse}
\begin{SBVerse}
Let all things their Creator bless,

And worship Him in humbleness,

O praise Him! Alleluia!

Praise, praise the Father, praise the Son,

And praise the Spirit, Three in One!

O praise Him, O praise Him!

Alleluia! Alleluia! Alleluia!
\end{SBVerse}

\end{song}\begin{song}{All Who Are Thirsty}{D}
{Brenton Brown}
{Brenton Brown}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Com}e, \Ch{D2}{Lor}d \Ch{Dsus}{Je }- \Ch{D}{sus},\Ch{G}{ co}me.

\Ch{D}{Com}e, \Ch{D2}{Lor}d \Ch{Dsus}{Je }- \Ch{D}{sus},\Ch{G}{ co}me.
\end{SBVerse}
\begin{SBVerse}
All who are \Ch{D}{thi}rsty,

All who are \Ch{F#m7}{wea}k,

Come to the \Ch{G}{fou}ntain,

Dip your heart in the \Ch{Em7}{str}eam \Ch{D/F#}{of }  l\Ch{G}{ife}

Let the \Ch{G}{pai}n and the \Ch{D}{sor}row

\Ch{D}{Be }washed a\Ch{F#m7}{way}

In the waves of his \Ch{G}{mer}cy

As deep cries \Ch{Em7}{out}  \Ch{D/F#}{to }  d\Ch{G}{eep} (\Ch{A}{We }sing)
\end{SBVerse}

\end{song}\begin{song}{Amazing Grace}{D}
{John Newton}
{John Newton}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Ama}zing \Ch{D/F#}{gra}ce how \Ch{G}{swe}et the \Ch{D}{sou}nd

That \Ch{D}{sav}ed a wretch like \Ch{A}{me }

I \Ch{D}{onc}e was \Ch{D/F#}{los}t, but \Ch{G}{now} am \Ch{D}{fou}nd

Was \Ch{D}{bli}nd but \Ch{G}{now} \Ch{A}{I s}\Ch{D}{ee }
\end{SBVerse}
\begin{SBVerse}
T'was grace that taught my heart to fear,

And grace my fears;

How precious did that grace appear

The hour I first believed. 
\end{SBVerse}
\begin{SBVerse}
Through many dangers, toil and snares,

I have already come;

'Tis grace has brought me safe thus far,

And grace will lead me home. 
\end{SBVerse}
\begin{SBVerse}
When we've been there ten thousand years

Bright shining as the sun,

We've no less days to sing God's praise

Than when we've first begun. 
\end{SBVerse}
\end{song}\begin{song}{Amazing Grace (My Chains Are Gone)}{G}
{Louie Giglio}
{Louie Giglio}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Ama}zing grace how \Ch{C}{swe}et the \Ch{G}{sou}nd

That \Ch{G}{sav}ed a wretch like \Ch{D}{me }

I \Ch{G}{onc}e was lost, but \Ch{C}{now} I'm \Ch{G}{fou}nd

Was \Ch{G}{bli}nd but \Ch{D}{now} I \Ch{G}{see}
\end{SBVerse}
\begin{SBVerse}
My chains are \Ch{C}{gon}e, I've been set\Ch{G}{ fr}ee.

My God, My\Ch{C}{ Sa}vior has ransomed\Ch{G}{ me}.

And like a\Ch{C}{ fl}ood his mercy\Ch{Em}{ re}igns.

Un-ending\Ch{D}{ lo}ve, amazing \Ch{G}{gra}ce
\end{SBVerse}
\begin{SBVerse}
'Twas grace that taught my heart to fear,

And grace my fears relieved;

How precious did that grace appear,

The hour I first believed!
\end{SBVerse}
\begin{SBVerse}
The Lord has promised good to me,

His word my hope secures;

He will my shield and portion be,

As long as life endures.
\end{SBVerse}
\begin{SBVerse}
The earth shall soon dissolve like snow,

The sun forbear to shine;

But God, who call'd me here below,

Will be forever mine.

(Will be forever mine)

(You are forever mine)
\end{SBVerse}

\end{song}\begin{song}{Ancient of Days}{D}
{Jamie Harvill}
{Jamie Harvill}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Ble}ssing and honor, glory and power

Be unto the Ancient of \Ch{Bm}{Day}s  \Ch{A}{   }

\Ch{D}{Fro}m every nation, all of creation

\Ch{Bm}{Bow} before the Ancient of \Ch{A}{Day}\Ch{D}{s..}.
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Eve}ry tongue in \Ch{Em7}{hea}ven and e\Ch{A}{art}h

Shall decl\Ch{D}{are} Y\Ch{D/F#m}{our} glory 

\Ch{G}{Eve}ry knee shall \Ch{Em7}{bow} at Your th\Ch{A}{ron}e in \Ch{D}{wor}- \Ch{D/F#m}{shi}p

\Ch{G}{You} will be exalt\Ch{Em7}{ed,} O G\Ch{A}{od,}

\Ch{D}{and} \Ch{D/F#m}{You}r king\Ch{G}{dom} shall \Ch{Em}{not} pass a\Ch{A}{way}

\Ch{G}{O A}ncient \Ch{A}{of }da\Ch{D}{ys }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{You}r kingdom shall reign over all the earth

\Ch{C}{Sin}g un\Ch{G}{to }the A\Ch{Am}{nci}e\Ch{G}{nt }of D\Ch{D}{ays}

\Ch{D}{For} none can compare to Your matchless worth

\Ch{C}{Sin}g un\Ch{G}{to }the A\Ch{Am}{nci}e\Ch{G}{nt }of D\Ch{D}{ays}
\end{SBVerse}

\end{song}\begin{song}{And Can It Be That I Should Gain?}{E}
{Charles Wesley}
{Charles Wesley}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{And} can it be, that \Ch{A}{I  }\Ch{B}{  s}hould \Ch{E}{gai}n  an \Ch{A}{in-} \Ch{B}{ter}est \Ch{E}{in }the \Ch{B}{Sav}i\Ch{F#}{our}'s \Ch{B}{blo}od?

\Ch{B}{Die}d He for me, who \Ch{E}{cau}sed His \Ch{B}{pai}n?  For\Ch{A}{ me}, who \Ch{E}{Him} to \Ch{B}{dea}th pur\Ch{E}{sue}d?

\Ch{E}{A- } \Ch{B}{maz}ing \Ch{E}{lov}e, how \Ch{A}{can} \Ch{F#/A#}{it }   \Ch{B}{be?}  that \Ch{E}{Tho}u, my \Ch{A}{God}, shouldst \Ch{B}{die} for \Ch{E}{me?}
\end{SBVerse}
\begin{SBVerse}
Refrain:

A- \Ch{E}{maz}ing \Ch{B}{lov}e, how \Ch{B/D#}{can} it \Ch{E}{be?}  that \Ch{A}{Tho}u, my \Ch{E}{God}, \Ch{A}{sho}uldst \Ch{E/B}{die}   \Ch{B}{for}  \Ch{E}{me?}
\end{SBVerse}
\begin{SBVerse}
He left His Father's throne above, so free, so infinite His grace;

Emptied Himself of all but love, and bled for Adam's helpless race;

'Tis mercy all, immense and free; for, O my God, it found out me.
\end{SBVerse}
\begin{SBVerse}
Long my imprisoned spirit lay  fast bound in sin and nature's night;

Thine eye diffused a quick'ning ray,  I woke, the dungeon flamed with light -

My chains fell off, my heart was free;  I rose, went forth, and followed Thee!
\end{SBVerse}
\end{song}\begin{song}{Arms of Love}{G}
{Craig  Musseau}
{Craig  Musseau}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{I s}ing a \Ch{D/F#}{sim}ple song of l\Ch{Em}{ove},

To my S\Ch{C}{avi}or, \Ch{Em}{to }my J\Ch{D}{esu}s.

\Ch{G}{I'm} grateful \Ch{D/F#}{for} the things You've \Ch{Em}{don}e,

My loving S\Ch{C}{avi}o\Ch{Em}{r, }O precious J\Ch{D}{esu}s.
\end{SBVerse}
\begin{SBVerse}
\Ch{Am}{My }heart is \Ch{Em}{gla}d that You've c\Ch{D}{all}ed me Your o\Ch{G}{wn.}

\Ch{Am}{The}re's no p\Ch{Em}{lac}e I'd rather \Ch{D}{be,}
\end{SBVerse}
\begin{SBVerse}
(Than) In Your \Ch{G}{arm}\Ch{Bm7}{s  }of l\Ch{C}{ove} 

In Your \Ch{G}{arm}\Ch{Bm7}{s  }of l\Ch{C}{ove} 

Holding me s\Ch{Em}{til}l, \Ch{Bm7}{hol}ding me n\Ch{C}{ear},

In Your a\Ch{D}{rms} of l\Ch{G}{ove}.
\end{SBVerse}
\end{song}\begin{song}{As the Deer}{C}
{Martin J. Nystrom}
{Martin J. Nystrom}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{As }the d\Ch{G}{eer} panteth \Ch{Am}{for} the \Ch{C/E}{wat}er

So my s\Ch{F}{oul} longeth a\Ch{G}{fte}r y\Ch{C}{ou } \Ch{Am}{   } \Ch{G}{   }

\Ch{C}{You} a\Ch{G}{lon}e are my he\Ch{Am}{art}'s desire

And I l\Ch{F}{ong} to wo\Ch{G}{rsh}ip y\Ch{C}{ou }\Ch{Am}{   } \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{Am}{You} alone are my st\Ch{F}{ren}gth, my s\Ch{C}{hie}ld

To y\Ch{F}{ou }alone will my sp\Ch{Dm}{iri}t y\Ch{E}{iel}d

\Ch{C}{You} a\Ch{G}{lon}e are my h\Ch{Am}{ear}t's desire

And I l\Ch{F}{ong} to wo\Ch{G}{rsh}ip y\Ch{C}{ou }
\end{SBVerse}
\begin{SBVerse}
You're my friend, and You are my brother

Even though You are a King

I love You more than any other

So much more than anything
\end{SBVerse}
\end{song}\begin{song}{Awesome God}{A}
{Rich Mullins}
{Rich Mullins}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{F#m}{Oh }when He rolls up his sleeves he ain't just puttin' on the ritz,

Our \Ch{Bm7}{God} is an \Ch{C#m7}{awe}some \Ch{F#m}{God}.
\end{SBVerse}
\begin{SBVerse}
There is thunder in his footsteps and lightning in his fists,

Our \Ch{Bm7}{God} is an \Ch{C#m7}{awe}some \Ch{F#m}{God}.
\end{SBVerse}
\begin{SBVerse}
And the \Ch{Bm7}{Lor}d wasn't joking when He kicked 'em out of Eden.

It \Ch{C#m7}{was}n't for no reason that He shed his blood.

His ret\Ch{D}{urn} is very soon and so you'd \Ch{D/B}{bet}ter be be\Ch{D/F#}{lie}vin' that

Our \Ch{Bm7}{God} is an \Ch{C#m7}{awe}some \Ch{F#m}{God}.
\end{SBVerse}
\begin{SBVerse}
Our \Ch{D}{God} is an \Ch{A}{awe}some God.

He r\Ch{E}{eig}ns from \Ch{F#m}{hea}ven above

with \Ch{D}{wis}dom, p\Ch{A}{ow'}r and love

Our \Ch{Bm7}{God} is an \Ch{C#m7}{awe}some \Ch{F#m}{God}
\end{SBVerse}
\begin{SBVerse}
And when the sky was starless in the void of the night,

Our God is an awesome God.

He spoke into the darkness and created the light,

Our God is an awesome God.
\end{SBVerse}
\begin{SBVerse}
And judgment and wrath He poured out on Sodom.

Mercy and grace He gave us at the cross.

I hope that we have not too quickly forgotten that

Our God is an awesome God
\end{SBVerse}
\end{song}\begin{song}{Awesome Is The Lord Most High}{G}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Gre}at are you Lord. Mighty in st\Ch{D}{ren}gth.

\Ch{C2}{You} are faithful. You will ever \Ch{G}{be.}

\Ch{G}{We }will praise You, all of our d\Ch{D}{ays}.

\Ch{C2}{It'}s for Your glory, we offer every\Ch{Em7}{thi}ng. \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
Raise your \Ch{G}{han}ds, all Your nations.

Shout to \Ch{D}{God}, all creation.

How \Ch{Em7}{awe}some is the Lord most \Ch{C2}{hig}h.
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Whe}n you send us, God we will \Ch{D}{go.}

\Ch{C2}{You}'re the answer, we want the world to \Ch{G}{kno}w.

\Ch{G}{We }will trust You. When You call our \Ch{D}{nam}es.

\Ch{C2}{Whe}n you lead us, we'll follow all the w\Ch{Em7}{ay.}  \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
Raise your \Ch{G}{han}ds, all Your nations.

Shout to \Ch{D}{God}, all creation.

How \Ch{Em7}{awe}some is the Lord most \Ch{C2}{hig}h.

We will \Ch{G}{pra}ise You together.

For \Ch{D}{now} and forever.

How \Ch{Em7}{awe}some is the Lord most \Ch{C2}{hig}h.
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Hal}lelujah  \Ch{D}{Hal}lelujah

How \Ch{Em7}{awe}some is the Lord most \Ch{C2}{hig}h.
\end{SBVerse}

\end{song}\begin{song}{Be Glorified}{G}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{You}r \Ch{C2}{lov}e has \Ch{F}{cap}tured \Ch{C2}{me,} \Ch{G}{You}r \Ch{C2}{gra}ce has \Ch{D}{set} me free

\Ch{G}{You}r \Ch{C2}{lif}e, the \Ch{F}{air} I \Ch{C2}{bre}athe,\Ch{C/A}{   } Be glorif\Ch{D}{ied} in me\Ch{G}{   \Ch{C2}{}  }\Ch{F}{   \Ch{C2}{}  }
\end{SBVerse}
\begin{SBVerse}
\Ch{C2}{You} set my feet to dancing, \Ch{G}{You} set my heart on fire

In the pr\Ch{C2}{ese}nce of a thousand kings you ar\Ch{G}{e m}y one desire

\Ch{C2}{And} I stand before you now with tr\Ch{Em}{emb}ling ha\Ch{D}{nds} lifted hi\Ch{C2}{gh }

Be glorified \Ch{G}{   \Ch{C2}{}  }\Ch{F}{   \Ch{C2}{}  }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{  B}e \Ch{G/B}{glo}ri\Ch{C}{fie}d, in \Ch{D}{me }

  Be \Ch{G/B}{glo}ri\Ch{C}{fie}d, in \Ch{D}{me }

  Be \Ch{G/B}{glo}ri\Ch{C}{fie}d, in \Ch{D}{me }

  Be \Ch{G/B}{glo}ri\Ch{C}{fie}d

  Be \Ch{G/B}{glo}ri\Ch{C}{fie}d
\end{SBVerse}
\end{song}\begin{song}{Be Magnified}{G}
{Lynn DeShazo}
{Lynn DeShazo}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{ I }have \Ch{Em}{mad}e You too sma\Ch{D}{ll }in my e\Ch{Am}{yes}

 \Ch{G/B}{O L}or\Ch{C}{d, }\Ch{D}{ fo}rgive \Ch{Em}{me;}

 \Ch{Em/B}{And}   I\Ch{Em}{ ha}ve believed\Ch{D}{ in} a l\Ch{Am}{ie }

 \Ch{G/B}{Tha}t Y\Ch{C}{ou }were una\Ch{D}{ble} to h\Ch{Em}{elp} me.

 \Ch{D/F#}{But} no\Ch{G}{w, }O Lo\Ch{D}{rd,} I s\Ch{Am}{ee }my wro\Ch{C}{ng }

 Heal my he\Ch{D}{art} and sho\Ch{G}{w Y}ourself stro\Ch{D}{ng;}

\Ch{G}{ An}d in my e\Ch{D}{yes} and wi\Ch{Am}{th }my s\Ch{C}{ong}

 O Lord, be m\Ch{D}{agn}if\Ch{Em}{ied}

 O \Ch{Am7}{Lor}d, be \Ch{Dsus}{mag} -\Ch{D}{ ni}f\Ch{G}{ied}.
\end{SBVerse}
\begin{SBVerse}
 Be m\Ch{G}{agn}if\Ch{D}{ied}, O L\Ch{Am}{ord} \Ch{G/B}{   }

\Ch{C}{ Yo}u are hi\Ch{G}{ghl}y exa\Ch{F}{lte}d; \Ch{Dsus}{   }   \Ch{D/C}{   }

\Ch{Bm}{ An}d there is \Ch{Em}{not}hing Y\Ch{C}{ou }can't d\Ch{G/B}{o  }

\Ch{Am7}{ O }Lo\Ch{D}{rd,} my ey\Ch{Em}{es }are on Yo\Ch{D}{u. }

 Be m\Ch{C}{agn}\Ch{D}{ifi}\Ch{Em}{ed,}

 O L\Ch{Am7}{ord}, be \Ch{Dsus}{mag} - \Ch{D}{nif}i\Ch{G}{ed.}
\end{SBVerse}
\begin{SBVerse}
 I have leaned on the wisdom of men

 O Lord, forgive me;

 And I have responded to them

 Instead of Your light and Your mercy.

 But now, O Lord, I see my wrong

 Heal my heart and show Yourself strong;

 And in my eyes with my song

 O Lord, be magnified

 O Lord, be magnified.
\end{SBVerse}
\end{song}\begin{song}{Be The Center}{D}
{Michael Frye}
{Michael Frye}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Jes}us, be the cent\Ch{D}{er }

\Ch{D}{Be }my \Ch{A/C#}{sou}rce, be my \Ch{G/B}{lig}ht, J\Ch{D}{esu}s
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Jes}us, be the cen\Ch{D}{ter}

\Ch{D}{Be }my \Ch{A/C#}{hop}e, be my so\Ch{G/B}{ng,} Jesu\Ch{D}{s  }
\end{SBVerse}
\begin{SBVerse}
Be the \Ch{A/C#}{fir}e, in the hea\Ch{D}{rt }

Be the \Ch{A}{win}d, in these \Ch{D}{sai}ls

Be the \Ch{A/C#}{rea}son that I \Ch{D}{liv}e, \Ch{A/C#}{Jes}us, \Ch{G/B}{Jes}us \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Jes}us, be my vis\Ch{D}{ion}

\Ch{D}{Be }my \Ch{A/C#}{pat}h, be my \Ch{G/B}{gui}de, Je\Ch{D}{sus} 
\end{SBVerse}
\end{song}\begin{song}{Be Thou My Vision}{G}
{Mary E. Byrne}
{Mary E. Byrne}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Be }thou my vision, oh Lo\Ch{G}{rd }of my he\Ch{D}{art}

\Ch{A}{Nau}ght be all else to me, s\Ch{G}{ave} that thou a\Ch{A}{rt }

\Ch{G}{Tho}u my best t\Ch{D/F#}{hou}ght, by \Ch{Bm}{day} or by n\Ch{G}{igh}\Ch{A}{t  }

\Ch{Bm}{Wak}ing or sl\Ch{F#m}{eep}ing, thy pre\Ch{G}{sen}ce \Ch{A}{my }li\Ch{D}{ght}
\end{SBVerse}
\begin{SBVerse}
Be thou my wisdom and thou my true word

I ever with thee and thou with me, Lord

Thou my great Father, and I thy true son

Thou in my dwelling, and I with thee one
\end{SBVerse}
\begin{SBVerse}
Riches I need not, nor man's empty praise

Thou mine inheritance, now and always

Thou and thou only, first in my heart

High King of heaven, my treasure thou art
\end{SBVerse}
\begin{SBVerse}
High King of heaven, my victory won

May I reach heaven's joys, O bright heaven's sun

Heart of my own heart, whatever befall

Still be my vision, O ruler of all
\end{SBVerse}
\end{song}\begin{song}{Be Unto Your Name}{C}
{Lynn DeShazo}
{Lynn DeShazo}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{We }are a mome\Ch{G}{nt,} You are f\Ch{Dm}{ore}ver.    \Ch{Am}{   }

\Ch{F}{Lor}d of the ages,\Ch{C}{ Go}d be\Ch{Bb}{for}e time.     \Ch{Gsus}{   }   \Ch{G}{   }

\Ch{C}{We }are a vapo\Ch{G}{r, }You are\Ch{Dm}{ et}ernal. \Ch{Am}{   }

\Ch{F}{Lov}e everlasti\Ch{C}{ng,} reigni\Ch{Bb}{ng }on high.  \Ch{Gsus}{   }   \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{Am}{Hol}y, \Ch{F}{hol}y Lo\Ch{C}{rd }God Almighty   \Ch{G}{   }

\Ch{Am}{Wor}thy is\Ch{F}{ th}e Lamb\Ch{C}{ wh}o was slain.      \Ch{G}{   }

\Ch{Am}{Hig}hest pra\Ch{F}{ise}s, hono\Ch{C}{r, }and glory   \Ch{G}{   }

\Ch{Dm}{Be } \Ch{Am}{unt}o Your\Ch{Gsus}{ na}me,\Ch{G}{  b}\Ch{D}{e u}\Ch{Am}{nto} Your na\Ch{Gsus}{me.}   \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
We are the broken, You are the healer 

Jesus Redeemer, mighty to save. 

You are the love song, we'll sing forever 

Bowing before You, blessing Your name. 
\end{SBVerse}
\end{song}\begin{song}{Beautiful One}{D}
{Tim Hughes}
{Tim Hughes}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Won}derful, So \Ch{A}{Won}derful

Is \Ch{D}{You}r Unfailing \Ch{D/F#}{Lov}e,

Your \Ch{G}{cro}ss has spoken \Ch{A}{mer}cy over \Ch{Bm7}{me }
\end{SBVerse}
\begin{SBVerse}
No \Ch{G}{eye} has seen, no \Ch{A}{ear} has heard

No \Ch{D}{hea}rt could fully \Ch{D/F#}{kno}w,

How \Ch{G}{glo}rious, how \Ch{A}{bea}utiful You \Ch{D}{are}
\end{SBVerse}
\begin{SBVerse}
Beautiful \Ch{G}{One}, I l\Ch{A}{ove} You

Beautiful \Ch{G}{One}, I a\Ch{A}{dor}e

Beautiful \Ch{G}{One} my \Ch{A}{sou}l must s\Ch{D}{ing}
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Pow}erful, so P\Ch{A}{owe}rful

Your g\Ch{D}{lor}y fills the s\Ch{D/F#}{kie}s

Your m\Ch{G}{igh}ty works displ\Ch{A}{aye}d for all to \Ch{Bm7}{see}

\Ch{G}{The} beauty of Your m\Ch{A}{aje}sty

Aw\Ch{D}{ake}s my heart to \Ch{D/F#}{sin}g;

How \Ch{G}{mar}velous, How \Ch{A}{won}derful You a\Ch{D}{re }
\end{SBVerse}
\begin{SBVerse}
You've \Ch{G}{ope}ned my eyes to Your wo\Ch{A}{nde}rs anew

You ca\Ch{G}{ptu}red my heart with this l\Ch{A}{ove}

'Cos nothin\Ch{G}{g o}n earth is as be\Ch{A}{aut}iful as \Ch{D}{You}
\end{SBVerse}
\begin{SBVerse}
My s\Ch{G}{oul}, my soul must s\Ch{A}{ing}

My s\Ch{Bm}{oul}, my soul must \Ch{A/C#}{sin}g

My s\Ch{G}{oul}, my soul must s\Ch{A}{ing}

Beautiful O\Ch{D}{ne }
\end{SBVerse}
\end{song}\begin{song}{Befriended}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Bef\Ch{Em7}{rie}nded, bef\Ch{Asus}{rie}nded by the King above all ki\Ch{D}{ngs}

Sur\Ch{Em7}{ren}dered, sur\Ch{Asus}{ren}dered to the friend above all fr\Ch{D}{ien}ds
\end{SBVerse}
\begin{SBVerse}
In\Ch{Em7}{vit}ed, i\Ch{Asus}{nvi}ted deep into this myst\Ch{D}{ery}

De\Ch{Em7}{lig}hted, de\Ch{Asus}{lig}hted by the wonders I have s\Ch{D}{een}
\end{SBVerse}
\begin{SBVerse}
This will be my st\Ch{G}{ory} \Ch{Em7}{   }  \Ch{Asus}{   }

This will be my s\Ch{D}{ong}

You'll always be my Sa\Ch{G}{vio}\Ch{Em7}{ur,}   \Ch{Asus}{Jes}us

You will always have my h\Ch{D}{ear}t
\end{SBVerse}
\begin{SBVerse}
As\Ch{Em7}{tou}nded, as\Ch{Asus}{tou}nded that Your gospel beckoned \Ch{D}{me }

Sur\Ch{Em7}{rou}nded, su\Ch{Asus}{rro}unded but I've never been so fr\Ch{D}{ee }
\end{SBVerse}
\begin{SBVerse}
De\Ch{Bm7}{ter}mined, de\Ch{Asus}{ter}mined now to live this life for Y\Ch{D}{ou }

Your so w\Ch{Bm7}{ort}hy my gr\Ch{Asus}{eat}est gift would be the least You're d\Ch{D}{ue }
\end{SBVerse}
\end{song}\begin{song}{Believer}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A7}{I d}ream of tongues of fire 

\Ch{A7sus}{res}ting on Your people,

\Ch{C/G}{I d}ream of all  the mi\Ch{Em7/D}{rac}les to come.

\Ch{A7}{I h}ope to see the coming

\Ch{A7sus}{hea}ling of the nations,

\Ch{C/G}{I l}ong to see th\Ch{Em7/D}{e p}rodigals return.

\Ch{Csus}{So }many \Ch{Em7/D}{hop}es and longings in you

\Ch{Csus}{whe}n will all the \Ch{Em7/D}{dre}ams come true?
\end{SBVerse}
\begin{SBVerse}
\Ch{A2}{I'm} a belie\Ch{G}{ver} in your kindom,

\Ch{D/F#}{I a}m a seek\Ch{A2}{er }of the new things,

I am a d\Ch{G}{rea}mer of some old dreams,

\Ch{D/F#}{let} them now come \Ch{A2}{   } 

(will you now come?)
\end{SBVerse}
\begin{SBVerse}
I hope to see you come down,

Rend the mighty heavens,

And let Your glory cover all the earth;

to see Your sons and daughters

Come to know and love You,

And find a purer passion in the church.

These are the things my heart will pursue;

When will all the dreams come true?
\end{SBVerse}
\begin{SBVerse}
May Your church now reach out,

Sowing truth and justice,

Learning to love the poor and help the weak.

When your kindom's coming

It will touch the broken,

Place the lonley ina family.

So many hopes and longings in You;

When will all the dreams come true?
\end{SBVerse}
\end{song}\begin{song}{Better Is One Day}{E}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
How l\Ch{E}{ove}ly is Your dwelling place,

\Ch{A2}{ oh} Lord Almi\Ch{Bsus}{ght}y

M\Ch{E}{y s}oul longs and even faints for Y\Ch{Bsus}{ou }

For h\Ch{E}{ere} my heart is satisfied,

\Ch{A2}{ wi}thin Your pre\Ch{Bsus}{sen}ce

I s\Ch{E}{ing} beneath the shadow of Your w\Ch{Bsus}{ing}s
\end{SBVerse}
\begin{SBVerse}
Better is o\Ch{A2}{ne }day in Your courts

Better is o\Ch{Bsus}{ne }day in Your house

Better is o\Ch{A2}{ne }day in Your courts

Than thousands e\Ch{Bsus}{lse}where
\end{SBVerse}
\begin{SBVerse}
One th\Ch{E}{ing} I ask and I would seek,

\Ch{A2}{ to} see Your bea\Ch{Bsus}{uty}

To f\Ch{E}{ind} You in the place Your glory dw\Ch{Bsus}{ell}s
\end{SBVerse}
\begin{SBVerse}
\Ch{C#m7}{ My} heart and flesh cry o\Ch{Bsus}{ut,}

\Ch{A}{ fo}r You the living G\Ch{Bsus}{od }

\Ch{C#m7}{ Yo}ur spirit's water f\Ch{Bsus}{or }my soul\Ch{A}{   } \Ch{Bsus}{   }

\Ch{C#m7}{ I'}ve tasted and I've s\Ch{Bsus}{een},

\Ch{A2}{ co}me once again to me

\Ch{C#m7}{ I }will draw near to You

\Ch{A2}{ I }will draw near to Yo\Ch{A2/F#m}{u  }
\end{SBVerse}
\end{song}\begin{song}{Bless His Name}{B}
{Tony Sanchez}
{Tony Sanchez}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{B}{Com\Ch{		}{}e,} let us\Ch{F#}{ si}ng for joy

Let us s\Ch{G#m}{hou}t aloud to our K\Ch{E}{ing}

\Ch{B}{Com}e, let us \Ch{F#}{wor}ship God

Lifting \Ch{G#m}{hol}y hands, bless His n\Ch{E}{ame} 
\end{SBVerse}
\begin{SBVerse}
Lord, we come to meet with You a\Ch{B/A#}{gai}n

To worship with one v\Ch{B/A}{oic}e in ad\Ch{G#m}{ora}--\Ch{F#}{tio}n

Y\Ch{B}{ou }deserve our every p\Ch{B/A#}{rai}se

That echoes in this p\Ch{B/A}{lac}e, You're the \Ch{G#m}{wor}thy \Ch{F#}{One}
\end{SBVerse}
\begin{SBVerse}
Lord, we c\Ch{B}{ome} with gratitude that f\Ch{B/A#}{low}s

From deep within our \Ch{B/A}{sou}ls, we re\Ch{G#m}{joi}ce in \Ch{F#}{You}

(And) \Ch{B}{We }will glory in Your \Ch{B/A#}{nam}e

With a shout our lips pr\Ch{B/A}{ocl}aim the praises st\Ch{G#m}{irr}ing in our h\Ch{F#}{ear}ts
\end{SBVerse}
\begin{SBVerse}
E\Ch{B}{ver}y creature in Heaven and Earth b\Ch{F#}{elo}w
\end{SBVerse}
\end{song}\begin{song}{Blessed Assurance}{D}
{Phoebe P. Knapp}
{Phoebe P. Knapp}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{Ble}ssed as\Ch{D}{sur}ance, \Ch{G}{Jes}us is \Ch{D}{min}e!

Oh what a \Ch{Bm}{for}e\Ch{A}{tas}te of \Ch{E}{glo}ry di\Ch{A}{vin}e!

\Ch{A}{Hei}r of sa\Ch{D}{lva}tion, \Ch{G}{pur}chase of \Ch{D}{God},

\Ch{D}{Bor}n of His \Ch{G}{Spi}rit, \Ch{A}{was}hed in His \Ch{D}{blo}od.
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{Thi}s is my \Ch{D}{sto}ry, \Ch{G}{thi}s is my \Ch{D}{son}g, praising my \Ch{Bm}{Sav}iour, \Ch{E}{all} the day \Ch{A}{lon}g;

\Ch{A}{Thi}s is my \Ch{D}{sto}ry, \Ch{G}{thi}s is my \Ch{D}{son}g, praising my \Ch{G}{Sav}i\Ch{Em}{our}, \Ch{A}{all} the day \Ch{D}{lon}g.
\end{SBVerse}
\begin{SBVerse}
Visions of rapture now burst on my sight.

Perfect submission, perfect delight,

Angels descending, bring from above

Echoes of mercy, whispers of love.
\end{SBVerse}
\begin{SBVerse}
Perfect submission, all is at rest,

I in my Saviour am happy and blest;

Watching and waiting, looking above,

Filled with His goodness, lost in His love.
\end{SBVerse}
\end{song}\begin{song}{Blessed be the name of the Lord}{G}
{Don Moen}
{Don Moen}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Ble}ssed be the name of the Lord,

\Ch{G}{ble}ssed be the name of the \Ch{G}{Lor}\Ch{A2}{d, }

\Ch{D			}{Ble}ssed\Ch{G}{ be} the na\Ch{A2}{me }of the Lord Most High
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Ble}ssed be the name of the Lord,

\Ch{G}{ble}ssed be the name of the \Ch{G}{Lor}\Ch{A2}{d, }

\Ch{D			}{Ble}ssed\Ch{G}{ be} the na\Ch{D}{me }of the Lord Most High
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{The} name of the Lord is

\Ch{G}{A s}trong t\Ch{D}{owe}r \Ch{(G-D)}{   }

The righteous run i\Ch{A2}{nto} \Ch{G}{it }

And t\Ch{G}{hey} are s\Ch{D}{ave}d (2x)
\end{SBVerse}
\begin{SBVerse}
Holy is the name of the Lord

Holy is the name of the Lord

Holy is the name of the Lord on high
\end{SBVerse}
\begin{SBVerse}
Glory to the name of the Lord

Glory to the name of the Lord

Glory to the name of the Lord on high
\end{SBVerse}
\end{song}\begin{song}{Blessed Be Your Name}{A}
{Beth Redman}
{Beth Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{ Bl}essed be\Ch{E}{ Yo}ur name in the \Ch{F#m7}{lan}d that is p\Ch{D}{len}tiful

Where Your \Ch{A}{str}eams of a\Ch{E}{bun}dance flow

Blessed\Ch{D}{ be} Your name

\Ch{A}{ An}d blessed be\Ch{E}{ Yo}ur name when I'm \Ch{F#m7}{fou}nd in the \Ch{D}{des}ert place

Though I \Ch{A}{wal}k through the \Ch{E}{wil}derness

Blessed\Ch{D}{ be} Your name
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{ Ev}ery blessing \Ch{E}{You} pour out I'll

\Ch{F#m7}{ tu}rn back to\Ch{D}{ pr}aise

\Ch{A}{ An}d when the darkness\Ch{E}{ cl}oses in, Lord

\Ch{F#m7}{ St}ill I will \Ch{D}{say}
\end{SBVerse}
\begin{SBVerse}
Blessed be the \Ch{A}{nam}e of the Lord \Ch{E}{   }

Blessed be Your \Ch{F#m7}{nam}e   \Ch{D}{   }

Blessed be the \Ch{A}{nam}e of the Lord \Ch{E}{   }

Blessed be Your \Ch{F#m7}{glo}rious \Ch{D}{nam}e
\end{SBVerse}
\begin{SBVerse}
Blessed be Your name when the sun's shining down on me

When the world's "all as it should be"

Blessed be Your name

And blessed be Your name on the road marked with suffering

Though there's pain in the offering

Blessed be Your name
\end{SBVerse}
\begin{SBVerse}
You \Ch{A}{giv}e and take a\Ch{E}{way}

You \Ch{F#m7}{giv}e and take a\Ch{D}{way}

My \Ch{A}{hea}rt will choose to \Ch{E}{say}

Lord, \Ch{F#m7}{ble}ssed be Your \Ch{D}{nam}e
\end{SBVerse}
\end{song}\begin{song}{Breathe}{G}
{Marie Barnett}
{Marie Barnett}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Thi}s is the \Ch{Gsus}{air} I breathe

\Ch{G}{Thi}s is the \Ch{Gsus}{air} I breathe

\Ch{G}{You}r h\Ch{D}{oly} pr\Ch{Em}{ese}nce\Ch{D}{ li}\Ch{C}{vin}g\Ch{Em}{ in} \Ch{D}{me }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Thi}s is my da\Ch{Gsus}{ily} bread

\Ch{G}{Thi}s is my da\Ch{Gsus}{ily} bread

\Ch{G}{You}r v\Ch{D}{ery} w\Ch{Em}{ord} \Ch{D}{spo}k\Ch{C}{en \Ch{Em}{}to} \Ch{D}{me }
\end{SBVerse}
\begin{SBVerse}
And \Ch{G}{I, \Ch{D}{}  \Ch{Em}{}  }\Ch{D}{  I}'m desperate for\Ch{C}{ yo}u\Ch{Em}{   } \Ch{D}{   }

And \Ch{G}{I, \Ch{D}{}  \Ch{Em}{}  }\Ch{D}{  I}'m lost without\Ch{C}{ yo}u\Ch{Em}{   } \Ch{D}{   }
\end{SBVerse}
\end{song}\begin{song}{Cares Chorus}{C}
{Kelly Willard}
{Kelly Willard}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
I \Ch{C}{cas}t all my \Ch{G}{car}es upon \Ch{F}{You},\Ch{C}{   }

I \Ch{F}{lay} all of my \Ch{C}{bur}dens \Ch{Dm}{dow}n at Your \Ch{G}{fee}t.

And \Ch{C}{any} time \Ch{G}{I d}on't know just \Ch{C}{wha}\Ch{C7}{t t}o \Ch{F}{do,}\Ch{Fm}{   }

I will \Ch{C}{cas}t all my \Ch{G}{car}es upon \Ch{F}{You}.\Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
I\Ch{C}{ ca}st all my\Ch{G}{ ca}res upon\Ch{F}{ Yo}u\Ch{C}{,  }

I \Ch{F}{lay} all of my \Ch{C}{bur}dens \Ch{Dm}{dow}n at Your \Ch{G}{fee}t.

And \Ch{C}{any} time \Ch{G}{I d}on't know just \Ch{C}{wha}\Ch{C7}{t t}o \Ch{F}{do,}\Ch{Fm}{   }

I will \Ch{C}{cas}t all my \Ch{G}{car}es upon \Ch{Am}{You}.\Ch{F}{   }

I will \Ch{C}{cas}t all my \Ch{G}{car}es upon \Ch{F}{you} \Ch{C}{   }
\end{SBVerse}
\end{song}\begin{song}{Change My Heart, Oh God}{C}
{Eddie Espinosa}
{Eddie Espinosa}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Cmaj7}{   } Ch\Ch{Em7}{ang}e my heart oh \Ch{Dm7}{God}

\Ch{G}{   } Make it ever t\Ch{C}{rue}

\Ch{Cmaj7}{   } Ch\Ch{Em7}{ang}e my heart oh \Ch{Dm7}{God}

\Ch{F/G}{   } May I \Ch{G}{be }like y\Ch{C}{ou }
\end{SBVerse}
\begin{SBVerse}
\Ch{Esus}{   }  Y\Ch{E}{ou }are the \Ch{Am}{pot}ter,\Ch{Dm7}{   } I \Ch{Gsus}{am }   \Ch{G}{the} \Ch{C}{cla}y

\Ch{Esus}{   }  M\Ch{E}{old} me and \Ch{Am}{mak}e me, \Ch{D}{thi}s is what I \Ch{Gsus}{pra}y   \Ch{G}{   }
\end{SBVerse}
\end{song}\begin{song}{Come Just As You Are}{F}
{Joseph Sabolick}
{Joseph Sabolick}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{F}{Com}e just\Ch{C/A}{ as} you\Ch{Bb}{ ar}e\Ch{C}{   }

\Ch{Dm7}{Hea}r the \Ch{C/E}{Spi}r-\Ch{F}{it }\Ch{Bb}{cal}l\Ch{Bb/D}{   }   \Ch{C}{   }

\Ch{F}{Com}e just\Ch{C/A}{ as} you\Ch{Bb}{ ar}e

\Ch{Gm7}{Com}e and see, c\Ch{F/A}{ome} receive,

\Ch{Bb}{Com}e and live fo\Ch{Csus4}{r-e}v - \Ch{C}{er }
\end{SBVerse}
\begin{SBVerse}
\Ch{Bb}{Lif}e everlas\Ch{F}{tin}\Ch{Dm7}{g, } \Ch{C}{   } and s\Ch{Bb}{tre}ngth for \Ch{F}{tod}\Ch{Dm7}{ay }  \Ch{C}{   }

\Ch{Bb}{Tas}te the Living\Ch{Dm7}{ Wa}ter, and\Ch{Gm7}{ ne}ver thirst\Ch{Csus4}{ a-}gain\Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
Come just as you are

Hear the Spirit call

Come just as you are

Come recieve, Christ the King,

Come and live forevermore
\end{SBVerse}
\end{song}\begin{song}{Come Thou Fount}{D}
{Robert Robinson}
{Robert Robinson}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Come, Thou F\Ch{D}{oun}t of every b\Ch{Asus}{les}sing, tune my h\Ch{G}{ear}t to s\Ch{A}{ing} Thy gr\Ch{D}{ace}

Streams of m\Ch{Bm}{erc}y, never c\Ch{Em}{eas}ing, \Ch{D/F#}{cal}l  for   s\Ch{G}{ong}s of l\Ch{A}{oud}est pr\Ch{D}{ais}e

Te\Ch{A}{ach} me s\Ch{D}{ome} \Ch{D/F#}{ me}l-od\Ch{G}{iou}s s\Ch{D}{onn}et, s\Ch{A}{ung} by \Ch{D}{fla}m\Ch{D/F#}{-in}g  to\Ch{G}{ngu}es a\Ch{D}{bov}e

Praise the m\Ch{Bm}{oun}t, I'm fixed u\Ch{Em}{pon} it, mount of T\Ch{G}{hy }red\Ch{D}{eem}ing l\Ch{D}{ove}
\end{SBVerse}
\begin{SBVerse}
Here I raise mine Ebenezer, hither by Thy help I come

And I hope by Thy good pleasure, safely to arrive at home

Jesus sought me when a stranger, wandering from the fold of God

He to rescue me from danger, interposed His precious blood
\end{SBVerse}
\begin{SBVerse}
Oh to grace how great a debtor, daily I'm constrained to be

Let Thy goodness, like a fetter, bind my wandering heart to Thee

Prone to wander, Lord I feel it, prone to leave the God I love

Here's my heart, take and seal it, seal it for Thy courts above
\end{SBVerse}

\end{song}\begin{song}{Come, Now is the Time to Worship}{D}
{Brian Doerksen}
{Brian Doerksen}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Com}e, now is the time to w\Ch{G}{ors}h\Ch{D}{ip }

\Ch{A}{Com}e, now is the time to g\Ch{Em}{ive} y\Ch{D}{our} h\Ch{G}{ear}t

\Ch{D}{Com}e, just as you are to w\Ch{G}{ors}h\Ch{D}{ip }

\Ch{A}{Com}e just as you are be\Ch{Em}{for}e y\Ch{D}{our} G\Ch{G}{od,} C\Ch{D}{ome}
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{One} day every tongue will con\Ch{D}{fes}s you are God 

\Ch{G}{One} day every knee will b\Ch{D}{ow }

\Ch{G}{Sti}ll the greatest treasure remains for tho\Ch{Bm}{se }

Who gl\Ch{G}{adl}y choose you \Ch{Asus4}{now}.   \Ch{A}{   }
\end{SBVerse}


\end{song}\begin{song}{Create in Me a Clean Heart}{G}
{Keith Green}
{Keith Green}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Cre\Ch{G}{ate} in me a c\Ch{D}{lea}n heart, \Ch{C}{O G}o\Ch{G}{d, }

and renew a right s\Ch{D}{pir}it within \Ch{C}{me.}\Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
C\Ch{C}{ast} me not a\Ch{D}{way} from Thy p\Ch{G}{res}ence, O L\Ch{Em}{ord}

and t\Ch{C}{ake} not Thy H\Ch{D}{oly} Spirit from \Ch{G}{me.}  \Ch{G7}{   }

Res\Ch{C}{tor}e unto \Ch{D}{me }the j\Ch{G}{oy }of \Ch{Bm}{Thy} salv\Ch{Em}{ati}on,

\Ch{C}{and} renew a right s\Ch{D}{pir}it within \Ch{G}{me.}
\end{SBVerse}

\end{song}\begin{song}{Cry Mercy}{D}
{David Crowder}
{David Crowder}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Bm}{   } \Ch{D}{I w}ill \Ch{G}{wai}t,\Ch{Bm}{   } \Ch{D}{I w}ill \Ch{G}{wai}t for your peace

\Ch{Bm}{   } \Ch{D}{I w}ill \Ch{G}{wai}t,\Ch{Bm}{   } \Ch{D}{I w}ill \Ch{G}{wai}t and you comfort me
\end{SBVerse}
\begin{SBVerse}
\Ch{F#7sus}{  I} lift my \Ch{G}{hea}d\Ch{F#7sus}{, I} lift my \Ch{G}{hea}rt my soul

\Ch{F#7sus}{  I} lift my \Ch{G}{han}ds\Ch{F#7sus}{, I} give mys\Ch{G}{elf}, my l\Ch{A}{ife}, my \Ch{Bm}{all}
\end{SBVerse}
\begin{SBVerse}
\Ch{Bm}{ An}d I\Ch{Asus}{ cr}y  \Ch{G}{ me}rcy

\Ch{Bm}{ A }cry\Ch{Asus}{ of} fr\Ch{G}{eed}om to be heard

\Ch{Bm}{ An}d I\Ch{Asus}{ cr}y m\Ch{G}{erc}y

\Ch{Bm}{   }A \Ch{Asus}{cry} of \Ch{G}{fre}edom from this world
\end{SBVerse}

\end{song}\begin{song}{Cry Of My Heart}{D}
{Terry Butler}
{Terry Butler}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
     \Ch{D}{It }is the \Ch{G}{cry} of my \Ch{A}{hea}rt to \Ch{G}{fol}low \Ch{D}{you}.

     It is the \Ch{G}{cry} of my \Ch{A}{hea}rt to be \Ch{Bm}{clo}se \Ch{A}{to }\Ch{D}{you}.

     It is the \Ch{G}{cry} of my \Ch{A}{hea}rt to \Ch{F#}{fol}low

     \Ch{G}{All} of the \Ch{A}{day}s of my \Ch{D}{lif}e.
\end{SBVerse}
\begin{SBVerse}
\Ch{Bm}{Tea}ch me your \Ch{G/B}{hol}y \Ch{A}{way}s oh \Ch{D}{Lor}d.

\Ch{Bm}{So }I can \Ch{E}{wal}k in your \Ch{A}{tru}th.

\Ch{Bm}{Tea}ch me your \Ch{G/B}{hol}y ways, \Ch{A}{oh }\Ch{D}{Lor}d

and make me \Ch{G}{who}lly \Ch{A}{dev}oted to \Ch{D}{you}, oh oh whoa.
\end{SBVerse}
\begin{SBVerse}
\Ch{Bm}{Ope}n my \Ch{G/B}{eye}s so \Ch{A}{I c}an \Ch{D}{see}

The won\Ch{Bm}{der}ful \Ch{E}{thi}ngs that you \Ch{A}{do.}

\Ch{Bm}{Ope}n my \Ch{G/B}{hea}rt up \Ch{A}{mor}e and \Ch{D}{mor}e

And make it \Ch{G}{who}lly \Ch{A}{dev}oted to \Ch{D}{you}, oh oh whoa.
\end{SBVerse}


\end{song}\begin{song}{Days of Elijah}{G}
{Robin Mark}
{Robin Mark}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{The}se are the days of E\Ch{C}{lij}ah,

De\Ch{G}{cla}ring the \Ch{D}{Wor}d of the L\Ch{G}{ord}

And \Ch{G}{the}se are the days of Your \Ch{C}{ser}vant, Moses,

\Ch{G}{Rig}hteousness \Ch{D}{bei}ng rest\Ch{G}{ore}d

And though \Ch{Bm}{the}se are the days of great \Ch{Em}{tri}al,

Of \Ch{C}{fam}ine and \Ch{Am}{dar}kness and \Ch{D}{swo}rd

Still \Ch{G}{we }are the voice in the desert, \Ch{C}{cry}ing,

\Ch{G}{"Pr}epare ye the \Ch{D}{way} of the \Ch{G}{Lor}d!"
\end{SBVerse}
\begin{SBVerse}
Behold, He \Ch{G}{com}es riding on the \Ch{C}{clo}uds

Shining like the \Ch{G}{sun}, at the trumpet \Ch{D}{cal}l

Lift your \Ch{G}{voi}ce, in the year of jubi\Ch{C}{lee}

For out of Zion's \Ch{G}{hil}l sa\Ch{D}{lva}tion \Ch{G}{com}es
\end{SBVerse}
\begin{SBVerse}
These are the days of Ezekiel,The dry bones becoming as flesh

And these are the days of Your servant, David,Rebuilding a temple of praise

These are the days of the harvest,The fields are as white in the world

And we are the labourers in Your vineyard,

Declaring the Word of the Lord.
\end{SBVerse}

\end{song}\begin{song}{Desert Song}{D}
{Brooke Fraser}
{Brooke Fraser}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Am}{Thi}s is my pr\Ch{G}{aye}r in the \Ch{F}{des}ert  \Ch{C}{   }

When \Ch{Am}{all} that's with\Ch{G}{in }me feels \Ch{F}{dry}  \Ch{C}{   }

\Ch{Am}{Thi}s is my \Ch{G}{pra}yer in my \Ch{F}{hun}ger and \Ch{C}{nee}d

My \Ch{Am}{God} is the \Ch{G}{God} who \Ch{F}{pro}vides
\end{SBVerse}
\begin{SBVerse}
\Ch{Am}{Thi}s is my \Ch{G}{pra}yer in the \Ch{F}{fir}e \Ch{C}{   }

In \Ch{Am}{wea}kness or \Ch{G}{tri}al or p\Ch{F}{ain}  \Ch{C}{   }

\Ch{Am}{The}re is a \Ch{G}{fai}th proved of \Ch{F}{mor}e worth than \Ch{C}{gol}d

So r\Ch{Am}{efi}ne me \Ch{C/E}{Lor}d through the \Ch{F}{fla}me
\end{SBVerse}
\begin{SBVerse}
And I will bring \Ch{C}{pra}ise, I will bring \Ch{G}{pra}ise

No weapon \Ch{F}{for}med against me shall \Ch{C}{rem}ain

\Ch{G/B}{I w}ill re\Ch{G}{joi}ce, I will de\Ch{Am}{cla}re

God is my victory and He is here  (play intro)
\end{SBVerse}
\begin{SBVerse}
\Ch{Am}{Thi}s is my \Ch{G}{pra}yer in the \Ch{F}{bat}tle \Ch{C}{   }

When \Ch{Am}{tri}umph is \Ch{G}{sti}ll on its \Ch{F}{way}  \Ch{C}{   }

\Ch{Am}{I a}m a \Ch{G}{con}queror and \Ch{F}{co-}heir with \Ch{C}{Chr}ist

So \Ch{Am}{fir}m on His \Ch{G}{pro}mise I'll \Ch{F}{sta}nd
\end{SBVerse}
\begin{SBVerse}
\Ch{Csus4}{All} of my \Ch{C}{lif}e, \Ch{Csus4}{In }every \Ch{C}{sea}son

\Ch{Am}{You} are still God

I have a reason to \Ch{G}{sin}g

\Ch{F}{I h}ave a reason to \Ch{C}{wor}ship
\end{SBVerse}
\begin{SBVerse}
\Ch{Am}{Thi}s is my \Ch{G}{pra}yer in the h\Ch{F}{arv}est \Ch{C}{   }

When \Ch{Am}{fav}or and \Ch{G}{pro}vidence \Ch{F}{flo}w   \Ch{C}{   }

\Ch{Am}{I k}now I'm \Ch{G}{fil}led to be \Ch{F}{emp}tied \Ch{C}{aga}in

The \Ch{Am}{see}d I've rec\Ch{G}{eiv}ed I will \Ch{F}{sow}
\end{SBVerse}
\end{song}\begin{song}{Draw Me Close}{A}
{Kelly Carpenter}
{Kelly Carpenter}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{Dra}w me close to y\Ch{D}{ou }

\Ch{E}{   }Never let me g\Ch{A}{o  }

\Ch{E}{   }I'll lay it all d\Ch{D}{own} again

\Ch{F#m}{   }To hear you say that \Ch{Dmaj7}{ I'}m your friend
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{You} are my des\Ch{D}{ire}

\Ch{E}{   }No one else will d\Ch{A}{o  }

\Ch{E}{   }Cause no one else could ta\Ch{D}{ke }your place

\Ch{F#m}{   }I feel the warmth of \Ch{Dmaj7}{You}r embrace

\Ch{A}{   }Help me find the w\Ch{D}{ay }

\Ch{E}{Lea}d me back to \Ch{A}{you}
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{You}'re a\Ch{E}{ll }I w\Ch{D}{ant}

\Ch{A}{You}'re a\Ch{E}{ll }I've \Ch{D}{eve}r\Ch{Esus-E}{ ne}eded

\Ch{A}{You}'re \Ch{E}{all} I w\Ch{D}{ant}

\Ch{Bm}{Hel}p me know Yo\Ch{E}{u a}re ne\Ch{A}{ar }
\end{SBVerse}
\end{song}\begin{song}{Emmanuel}{C}
{Bob McGee}
{Bob McGee}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
His name is \Ch{Dm}{cal}led\Ch{G7}{   }Emmanu\Ch{C}{el }
\end{SBVerse}
\begin{SBVerse}
God with \Ch{F}{us,}\Ch{Dm}{  r}e\Ch{G7}{vea}led in \Ch{C}{us }
\end{SBVerse}
\begin{SBVerse}
His name is \Ch{Dm}{cal}led\Ch{G7}{   }Emmanu\Ch{C}{el }
\end{SBVerse}
\end{song}\begin{song}{Enough}{G}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{  Y}ou are \Ch{C}{my }\Ch{D}{sup}ply

My \Ch{G/B}{bre}ath of \Ch{C}{lif}e

Still more \Ch{Am7}{awe}some than I \Ch{D2/F#}{kno}w

\Ch{G}{  Y}ou are \Ch{C}{my }re\Ch{D}{war}d

Worth \Ch{G/B}{liv}ing \Ch{C}{for}

Still more \Ch{Am7}{awe}some than I \Ch{D2/F#}{kno}w
\end{SBVerse}
\begin{SBVerse}
All of \Ch{G}{You} is \Ch{C}{mor}e than \Ch{D}{eno}ugh for \Ch{C}{   }

All of m\Ch{G}{e f\Ch{C}{}or} every \Ch{D}{thi}rst and\Ch{C}{ ev}ery \Ch{G}{nee}d

\Ch{C}{You} satis\Ch{D}{fy }me\Ch{C}{ wi}th Your \Ch{G}{lov}e

And \Ch{C}{all} I have in \Ch{D}{You} is \Ch{C}{mor}e than en\Ch{G}{oug}h    \Ch{C}{   \Ch{D}{}  \Ch{C}{}  \Ch{G}{}  }
\end{SBVerse}
\begin{SBVerse}
You're my sacrifice

Of greatest price

Still more awesome than I know

You're my coming King

You are everything

Still more awesome than I know
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{  M}ore than \Ch{C}{all} I \Ch{D}{wan}t

More than \Ch{C}{all} I \Ch{G/B}{nee}d  \Ch{C}{   }

You are \Ch{D}{mor}e than \Ch{C}{eno}ugh for me

\Ch{G}{  M}ore than \Ch{C}{all} I \Ch{D}{kno}w

More than \Ch{C}{all} I can \Ch{G/B}{see}   \Ch{C}{   }

You are \Ch{D}{mor}e than enough
\end{SBVerse}
\end{song}\begin{song}{Everlasting God}{G}
{Ken Riley}
{Ken Riley}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Str}ength will rise as\Ch{G/B}{ we}  \Ch{C2}{wai}t upon the \Ch{G}{Lor}d,

we \Ch{G/B}{wil}l \Ch{C2}{wai}t upon the \Ch{G}{Lor}d

we \Ch{G/B}{wil}l \Ch{C2}{wai}t upon the \Ch{G}{Lor}d (repeat)
\end{SBVerse}
\begin{SBVerse}
\Ch{G/B}{Our}  \Ch{C2}{God} \Ch{G/B}{You} r\Ch{C2}{eig}n \Ch{D}{for} - \Ch{Em7}{ev }- \Ch{D}{er }

\Ch{G/B}{Our} h\Ch{C2}{ope} \Ch{G/B}{Our} s\Ch{C2}{tro}ng \Ch{D}{de }- \Ch{Em7}{liv} - \Ch{D}{rer}
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{You} are the everlasting \Ch{C2}{God}

the everlasting \Ch{Em7}{God}

You do not faint You \Ch{C}{won}'t \Ch{D/C}{gro}w \Ch{C}{wea}r\Ch{D/C}{y  }

and \Ch{G}{You}'re the defender of the w\Ch{C}{eak}

You comfort those in n\Ch{Em}{eed}

You lift us up on \Ch{C}{win}gs \Ch{D/C}{lik}e \Ch{C}{eag}l\Ch{D/C}{es }
\end{SBVerse}
\end{song}\begin{song}{Every Move I Make}{G}
{David Ruis}
{David Ruis}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Eve}ry move I \Ch{C}{mak}e I make in \Ch{D}{You}, (You make\Ch{C}{ me} move Jesus)

\Ch{G}{Eve}ry Breath I \Ch{C}{tak}e I Breath in \Ch{D}{You}    \Ch{C}{   }

\Ch{G}{Eve}ry step I \Ch{C}{tak}e I take in \Ch{D}{You}, (You are \Ch{C}{my }way Jesus)

\Ch{G}{Eve}ry Breath I \Ch{C}{tak}e I Breath in \Ch{D}{You}      \Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Wav}es of \Ch{Am7}{Mer}cy \Ch{Bm}{Wav}es of \Ch{C}{Gra}ce

\Ch{G}{Eve}ry\Ch{Am7}{whe}re I \Ch{Bm}{Loo}k, I \Ch{C}{See} Your Face

\Ch{G}{You}r \Ch{Am7}{Lov}e has \Ch{Bm}{cap}tured \Ch{C}{Me }

\Ch{G}{Oh }My \Ch{Am7}{God} this \Ch{Bm}{Lov}e, How \Ch{C}{can} it Be!
\end{SBVerse}
\end{song}\begin{song}{Everyday}{B}
{Joel Houston}
{Joel Houston}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Wha}t to sa\Ch{B}{y L}ord? it's \Ch{G#m}{You} who \Ch{F#}{gav}e me life and \Ch{E}{I  }

Can't expl\Ch{B}{ain} just how \Ch{G#m}{muc}h You \Ch{F#}{mea}n to me now

\Ch{E}{Tha}t You have \Ch{B}{sav}ed me Lord, \Ch{G#m}{I g}ive all \Ch{F#}{tha}t I am to You

\Ch{E}{Tha}t every\Ch{B}{day} I can \Ch{G#m}{be }a \Ch{F#}{lig}ht that shines Your \Ch{E}{nam}e \Ch{B}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{Eve}ry\Ch{B}{day} Lord, I'll \Ch{G#m}{lea}rn to \Ch{F#}{sta}nd upon Your Word\Ch{E}{   }

And I \Ch{B}{pra}y that I, \Ch{G#m}{tha}t I might \Ch{F#}{com}e to know You more

\Ch{E}{Tha}t You would \Ch{B}{gui}de me in \Ch{G#m}{eve}ry single \Ch{F#}{ste}p I take

That \Ch{E}{eve}ry\Ch{B}{day} I can \Ch{G#m}{be }a \Ch{F#}{lig}ht unto the world
\end{SBVerse}
\begin{SBVerse}
\Ch{B}{Eve}ryd\Ch{E}{ay,} it's \Ch{G#m}{You} I'll \Ch{F#}{liv}e for

\Ch{B}{Eve}ryd\Ch{E}{ay,} I'll \Ch{G#m}{fol}low \Ch{F#}{aft}er You

\Ch{B}{Eve}ryd\Ch{E}{ay,} I'll \Ch{G#m}{wal}k with \Ch{F#}{You} my \Ch{B}{Lor}d
\end{SBVerse}
\begin{SBVerse}
It's \Ch{B}{You} I \Ch{E}{liv}e for, \Ch{G#m}{eve}ryd\Ch{F#}{ay }

It's \Ch{B}{You} I \Ch{E}{liv}e for, \Ch{G#m}{eve}ryd\Ch{F#}{ay }

It's \Ch{B}{You} I \Ch{E}{liv}e for, \Ch{G#m}{eve}ryd\Ch{F#}{ay }
\end{SBVerse}
\end{song}\begin{song}{Famous One}{G}
{Jesse Reeves}
{Jesse Reeves}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
And for \Ch{Am7}{all} You've done and \Ch{G/B}{yet} to do

With \Ch{C}{eve}ry breath \Ch{G}{I'm} praising You

\Ch{Am7}{Des}ire of nations an\Ch{G/B}{d e}very heart

You\Ch{C}{ al}one are God, You\Ch{D}{ al}one are God
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{You} are the \Ch{G/B}{Lor}d the \Ch{C}{fam}ous One, famous One

\Ch{Em7}{Gre}at is Your \Ch{D}{nam}e in all the \Ch{C}{ear}th

The \Ch{G}{hea}vens de\Ch{G/B}{cla}re You're \Ch{C}{glo}rious, glorious

\Ch{Em7}{Gre}at is Your \Ch{D}{fam}e beyond the \Ch{G}{ear}th  \Ch{G/B}{   } \Ch{F}{   \Ch{C}{}  \Ch{D}{}  }
\end{SBVerse}
\begin{SBVerse}
The morning star is shining through

And every eye is watching You

Revealed by nature and miracles

You are beautiful, You are beautiful (x2)
\end{SBVerse}
\end{song}\begin{song}{For the Cross}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Bm}{I w}ill \Ch{A}{lov}e You \Ch{G}{for} the C\Ch{Bm}{ros}s   \Ch{A}{   }   \Ch{G}{   }

\Ch{Bm}{And} I will lov\Ch{A}{e Y}ou f\Ch{G}{or }the co\Ch{Bm}{st }  \Ch{A}{   } \Ch{G}{   }

\Ch{A}{Man} of sufferings, \Ch{G}{Bri}nger of my pea\Ch{Bm}{ce.} \Ch{A}{   } \Ch{G}{   }

\Ch{Bm}{You} came i\Ch{A}{nto} a w\Ch{G}{orl}d of s\Ch{Bm}{ham}e  \Ch{A}{   }   \Ch{G}{   }

\Ch{Bm}{And} paid the \Ch{A}{pri}ce we \Ch{G}{cou}ld not \Ch{Bm}{pay}  \Ch{A}{   } \Ch{G}{   }

\Ch{A}{Dea}th that brought me li\Ch{G}{fe,}

\Ch{G}{Blo}od that brought me ho\Ch{Bm}{me.}   \Ch{A}{   }  \Ch{G}{   }

\Ch{A}{Dea}th that brought me life\Ch{G}{,  }

\Ch{G}{Blo}od that brought me ho\Ch{Bm}{me.}   \Ch{A}{   }  \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{Bm}{And} I love You for the cro\Ch{G}{ss,}

\Ch{A}{I'm} overwhelmed by the mys\Ch{G}{ter}y,

\Ch{Bm}{I l}ove You for the cros\Ch{G}{s, }

\Ch{A}{Tha}t Jesus You would do th\Ch{G}{is }for me.

When\Ch{Bm}{ Yo}u were broken, Y\Ch{G}{ou }were beaten,

\Ch{A}{You} were punished,  I g\Ch{G}{o f}ree,

\Ch{Bm}{Whe}n You were wounded a\Ch{G}{nd }rejected,

\Ch{A}{In }Your mercy,  I am hea\Ch{Bm}{led}.  \Ch{G}{   }  \Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
Jesus Christ the sinner's Friend

Does this kindness know no bounds?

With Your precious blood You have purchased me.

O,  the mystery of the cross

You were punished, You were crushed

But that punishment has become my peace

Yes, that punishment has become my peace.
\end{SBVerse}
\end{song}\begin{song}{Forever}{E}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Giv}e thanks to the Lord our God and King 
\end{SBVerse}
\begin{SBVerse}
His love endures forever 

\Ch{A}{For} He is good, He is above all things 

His love endures forever        \Ch{E}{   }

Sing pra\Ch{B}{ise}, sing praise    \Ch{A/C#}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{Wit}h a mighty hand and outstretched arm 
\end{SBVerse}
\begin{SBVerse}
His love endures forever 

\Ch{A}{For} the life that's been reborn 

His love endures forever        \Ch{E}{   }

Sing praise,\Ch{B}{ si}ng praise     \Ch{A/C#}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{For}ever God is faithful 

\Ch{E/C#}{For}ever God is strong 

\Ch{B}{For}ever God is with us 

\Ch{A}{For}ever 
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{Fro}m the rising to the setting sun 
\end{SBVerse}
\begin{SBVerse}
His love endures forever 

\Ch{A}{By }the grace of God we will carry on 

His love endures forever        \Ch{E}{   }

Sing praise,\Ch{B}{ si}ng praise     \Ch{A/C#}{   }
\end{SBVerse}
\end{song}\begin{song}{Free}{E}
{Mark Spencer}
{Mark Spencer}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{You} are the \Ch{B/Eb}{way} the life

\Ch{C#m}{You} are the Tr\Ch{A}{uth} the Christ

\Ch{E}{You} came and \Ch{B/Eb}{gav}e Your life to \Ch{A}{me }   \Ch{B}{   }

(Repeat)
\end{SBVerse}
\begin{SBVerse}
\Ch{C#m}{Tha}t I might be f\Ch{B}{ree}

\Ch{C#m}{And} know that lib\Ch{B}{ert}y

\Ch{C#m}{Tha}t I might be f\Ch{B}{ree}, free i\Ch{A}{nde}ed
\end{SBVerse}
\begin{SBVerse}
\Ch{C#m}{You} have come to set us free

And b\Ch{B}{rin}g that perfect liberty

Who\Ch{A}{eve}r the Son has set free

Is f\Ch{B}{ree}...
\end{SBVerse}
\end{song}\begin{song}{Friend Of God}{E}
{Michael Gungor}
{Michael Gungor}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Who} am I that you are mindful \Ch{C#m7}{of }me 

That you \Ch{F#m7}{hea}r me, when I c\Ch{E}{all} 

\Ch{E}{Is }it true that you are thinking \Ch{C#m7}{of }me

That you \Ch{F#m7}{lov}e me

Its am\Ch{D}{azi}ng
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{I a}m a friend of God, \Ch{C#m7}{I a}m a friend of God

\Ch{F#m7}{I a}m a friend of God He calls me \Ch{E}{fri}end
\end{SBVerse}
\begin{SBVerse}
\Ch{A2}{God} almighty, \Ch{G#m7}{Lor}d of glory

\Ch{F#m7}{You} have called me \Ch{A2}{fri}end
\end{SBVerse}
\end{song}\begin{song}{Friend of Sinners}{E}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Fri}end of s\Ch{A}{inn}ers, L\Ch{B}{ord} of t\Ch{E}{rut}h,

I am f\Ch{A}{all}ing in l\Ch{B}{ove} with Y\Ch{E}{ou }

Friend of s\Ch{A}{inn}ers, L\Ch{B}{ord} of tr\Ch{E}{uth},

I have f\Ch{A}{all}en in l\Ch{B}{ove} with Y\Ch{E}{ou }
\end{SBVerse}
\begin{SBVerse}
Jes\Ch{E}{us,}\Ch{A}{ I }l\Ch{B}{ove} Your n\Ch{E}{ame},

the name\Ch{A}{ by} w\Ch{B}{hic}h we're s\Ch{E}{ave}d.

Jesus,\Ch{A}{ I }l\Ch{B}{ove} Your n\Ch{E}{ame}.

the name\Ch{A}{ by} w\Ch{B}{hic}h we're s\Ch{E}{ave}d
\end{SBVerse}
\begin{SBVerse}
Friend of sinners, Lord of truth,

I am giving my life to You

Friend of sinners, Lord of truth,

I have given my life to You
\end{SBVerse}
\end{song}\begin{song}{From The Inside Out}{C}
{Joel Houston}
{Joel Houston}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{   }A thousand \Ch{F}{tim}es I've failed

Still Your me\Ch{C}{rcy} remains

\Ch{G}{   }And should I \Ch{F}{stu}mble again

I'm ca\Ch{C}{ugh}t in Your gr\Ch{G}{ace}

Everl\Ch{Am}{ast}ing

Your li\Ch{F}{ght} will shine when \Ch{C}{all} else fa\Ch{G}{des}

Never \Ch{Am}{ending}

Your \Ch{F}{glo}ry goes bey\Ch{C}{ond} all f\Ch{G}{ame}\Ch{F}{   }\Ch{C}{   }\Ch{G}{   }\Ch{F}{   }\Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{   }Your will a\Ch{F}{bov}e all else

My pur\Ch{C}{pos}e remains

\Ch{G}{   }The art of \Ch{F}{los}ing myself

In b\Ch{C}{rin}ging You p\Ch{G}{rai}se

Everl\Ch{Am}{ast}ing

Your li\Ch{F}{ght} will shine when \Ch{C}{all} else fa\Ch{G}{des}

Never \Ch{Am}{ending}

Your \Ch{F}{glo}ry goes bey\Ch{C}{ond} all f\Ch{G}{ame}
\end{SBVerse}
\begin{SBVerse}
\Ch{F}{In }my heart and my soul \Ch{C}{   }

Lord I give You contr\Ch{Am}{ol }

Consume me from the \Ch{G}{ins}ide out

Lord\Ch{F}{ le}t justice and praise\Ch{Am}{   }

Become my embrace\Ch{G}{   }

To love You from the \Ch{Dm}{ins}ide out (repeat)
\end{SBVerse}
\begin{SBVerse}
Everl\Ch{Am}{ast}ing

Your li\Ch{F}{ght} will shine when \Ch{C}{all} else fa\Ch{G}{des}

Never \Ch{Am}{ending}

Your \Ch{F}{glo}ry goes bey\Ch{C}{ond} all f\Ch{G}{ame}

And the cry\Ch{C}{ of} my heart\Ch{F}{   }

Is to bring\Ch{G}{ Yo}u pr\Ch{Am}{ais}e

From the i\Ch{F}{nsi}de o\Ch{G}{ut }

Lord my soul\Ch{F}{ cr}ies \Ch{G}{out}
\end{SBVerse}
\begin{SBVerse}
Other:
\end{SBVerse}
\end{song}\begin{song}{Give Me Jesus}{C}
{Fernando Ortega}
{Fernando Ortega}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
In the morn\Ch{C}{-in}g when I ri\Ch{Am}{se,}

In the morn\Ch{F2}{-in}g when I ri\Ch{C}{se,}

In the morn\Ch{Am}{-in}g when I ri\Ch{F}{se }\Ch{Fmaj7}{giv}e   \Ch{F6}{me } \Ch{Dm}{Je } \Ch{G}{-  }\Ch{C}{sus}.
\end{SBVerse}
\begin{SBVerse}
Give me J\Ch{Em}{e -} s\Ch{Am}{us,} give me Je\Ch{F}{ - }s\Ch{C}{us.}

You can h\Ch{F/A}{ave} all this wo\Ch{C/G}{rld},

But give me Je\Ch{F2}{ - }s\Ch{C}{us.}
\end{SBVerse}
\begin{SBVerse}
[\Ch{Csus}{ / }/ / / |\Ch{C}{ / }/ / / |\Ch{Csus}{ / }/ / / ]
\end{SBVerse}
\begin{SBVerse}
And w\Ch{C}{hen} I am alo\Ch{Am}{ne,}

Oh, and w\Ch{F}{hen} I am alo\Ch{C2}{ne,} \Ch{C}{   }

And w\Ch{F2}{hen} I am alo\Ch{C/E}{ne }give me J\Ch{Dm7}{e  } -\Ch{G}{  s}\Ch{C}{us.}
\end{SBVerse}
\begin{SBVerse}
And w\Ch{C}{hen} I come to d\Ch{Am}{ie,}

Oh, and w\Ch{F}{hen} I come to d\Ch{C2}{ie,} \Ch{C}{   }

And w\Ch{F2}{hen} I come to d\Ch{C/E}{ie,} give me J\Ch{Dm7}{e  } -\Ch{G}{  s}\Ch{C}{us.}
\end{SBVerse}
\begin{SBVerse}
You can h\Ch{F/A}{ave} all this wo\Ch{C/G}{rld}, \Ch{Cmaj7/G}{   }

You can h\Ch{F2}{ave} all this wo\Ch{C/E}{rld},

You can h\Ch{Dm7}{ave} all this wo\Ch{C/E}{rld},

But give me Je\Ch{F2}{ - }s\Ch{C}{us.}
\end{SBVerse}
\end{song}\begin{song}{Give Thanks}{G}
{Henry Smith}
{Henry Smith}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Give t\Ch{G}{han}ks with a g\Ch{Bm7}{rat}eful heart

Give \Ch{Em7}{tha}nks unto the \Ch{Bm}{Hol}y One

Give t\Ch{C}{han}ks because He's \Ch{G/B}{giv}en Jesus C\Ch{F}{hri}st, His \Ch{Dsus}{Son}  \Ch{D}{  (}repeat)
\end{SBVerse}
\begin{SBVerse}
And \Ch{Bm}{now} let the \Ch{Em7}{wea}k say, "I am s\Ch{Am}{tro}ng"

Let the p\Ch{D7}{oor} say, "I am \Ch{Gmaj7}{ric}h

Because of \Ch{Em}{wha}t the Lord has d\Ch{F}{one} for u\Ch{D7}{s" } (repeat)
\end{SBVerse}
\begin{SBVerse}
Give th\Ch{G}{ank}s
\end{SBVerse}
\end{song}\begin{song}{Give Us Clean Hands}{G}
{Charlie Hall}
{Charlie Hall}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{  W}e bow our hearts,\Ch{D/F#}{ we} bend our knees

\Ch{C2}{  O} Spirit come make us hum\Ch{G}{ble} \Ch{D}{   }

\Ch{G}{We }turn our eye\Ch{D/F#}{s f}rom evil things

\Ch{C2}{O L}ord we cast down our\Ch{G}{ id}o\Ch{D}{ls }
\end{SBVerse}
\begin{SBVerse}
Give us clean \Ch{G}{han}ds, give us pure \Ch{D/F#}{hea}rts

Let us \Ch{Em}{not} lift our \Ch{D}{sou}ls to \Ch{C2}{ano}ther

Give us clean \Ch{G}{han}ds, give us pure \Ch{D/F#}{hea}rts

Let us \Ch{Em}{not} lift our \Ch{D}{sou}ls to \Ch{C2}{ano}ther
\end{SBVerse}
\begin{SBVerse}
O God let us \Ch{G}{be }a generation that \Ch{D/F#}{see}ks

that seeks your \Ch{Em}{fac}e O \Ch{D}{God} of \Ch{C2}{Jac}ob

O God let us \Ch{G}{be }a generation that \Ch{D/F#}{see}ks

that seeks your \Ch{Em}{fac}e O \Ch{D}{God} of \Ch{C2}{Jac}ob
\end{SBVerse}
\end{song}\begin{song}{Glorify Thy Name}{C}
{Donna Adkins}
{Donna Adkins}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{Fat}her, we \Ch{F}{lov}e You

We \Ch{G}{wor}ship and adore \Ch{C}{You}

\Ch{C}{Glo}rify Thy \Ch{F}{Nam}e in all the \Ch{C}{ear}t\Ch{G}{h  }
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Glo}rify Thy \Ch{F}{Nam}e

\Ch{G}{Glo}rify Thy \Ch{Am}{Nam}e

\Ch{F}{Glo}rify Thy \Ch{G}{Nam}e in all the \Ch{C}{ear}th
\end{SBVerse}
\begin{SBVerse}
Jesus, we love You

We worship and adore You

Glorify Thy Name in all the earth
\end{SBVerse}
\begin{SBVerse}
Spirit, we love You

We worship and adore You

Glorify Thy Name in all the earth
\end{SBVerse}
\end{song}\begin{song}{Glory to God}{G}
{Steve Fee}
{Steve Fee}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G/B}{Bef}ore the \Ch{C}{wor}ld was \Ch{G}{mad}e, before you \Ch{D/F#m}{spo}ke it to be

\Ch{G/B}{You} were the \Ch{C}{Kin}g of Ki\Ch{G}{ngs}, Yeah you were,\Ch{D/F#m}{  y}eah you were

\Ch{G/B}{And} now you're r\Ch{C}{eig}ning s\Ch{G}{til}l,  Enthroned \Ch{D/F#m}{abo}ve all things

\Ch{G/B}{Ang}els and s\Ch{C}{ain}ts cry \Ch{G}{out}, We join them\Ch{D/F#m}{ as} we sing
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Glo}ry to \Ch{G}{God}, G\Ch{D}{lor}y to \Ch{Em}{God}

\Ch{C}{Glo}ry to G\Ch{G}{od,} For\Ch{D}{eve}r     (2x)
\end{SBVerse}
\begin{SBVerse}
\Ch{G/B}{Cre}ator g\Ch{C}{od }you g\Ch{G}{ave} me breath so \Ch{D/F#m}{I c}ould praise

\Ch{G/B}{You}r great and \Ch{C}{mat}chless \Ch{G}{nam}e, all my day\Ch{D/F#m}{s, }all my days

\Ch{G/B}{So }let my wh\Ch{C}{ole} life be\Ch{G}{ a }blazing o\Ch{D/F#m}{ffe}ring

\Ch{G/B}{A l}ife that s\Ch{C}{hou}ts and s\Ch{G}{ing}s the greatn\Ch{D/F#m}{ess} of the King
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Tak}e my life and l\Ch{G}{et }it be

\Ch{D}{All} for you and \Ch{Em}{for} your glory
\end{SBVerse}
\end{song}\begin{song}{God Of This City}{G}
{Peter Kernaghan}
{Peter Kernaghan}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
You're the God of this \Ch{Em}{cit}y

You're the King of\Ch{D/F#}{ th}ese people

You're the Lord o\Ch{C}{f t}his nation

You \Ch{Am7}{are}
\end{SBVerse}
\begin{SBVerse}
You're the lig\Ch{Em}{ht }in this darkness

You're the hope t\Ch{D/F#}{o t}he hopeless

You're the p\Ch{C}{eac}e to the restless

You \Ch{Am7}{are}
\end{SBVerse}
\begin{SBVerse}
\Ch{Em}{The}re is \Ch{D/F#}{no }one like our \Ch{C}{God}

\Ch{Em}{The}re is \Ch{D/F#}{no }one like our \Ch{C}{God}
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Gre}ater things have yet to come

\Ch{D}{Gre}ater things are still to be done 

In thi\Ch{G}{s c}it\Ch{D/F#}{y  }     \Ch{C}{   }

\Ch{C}{Gre}ater things have yet to come

\Ch{D}{Gre}ater things are still to be done [\Ch{G}{her}e]

[We\Ch{D/F#}{ be}lieve, we \Ch{C}{bel}ieve in you God]
\end{SBVerse}
\begin{SBVerse}
Instrumental:
\end{SBVerse}
\end{song}\begin{song}{God of Wonders}{G}
{Steve Hindalong}
{Steve Hindalong}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
CAPO 3rd Fret
\end{SBVerse}
\begin{SBVerse}
\Ch{D4}{Lor}d\Ch{Em}{ of} all creati\Ch{C2}{on }

\Ch{D4}{   }Of \Ch{Em}{wat}er earth and \Ch{C2}{sky}

\Ch{D4}{Hea}vens are\Ch{Em}{ yo}ur tabernac\Ch{C2}{le }

\Ch{D4}{Glo}ry to \Ch{Em}{the} Lord on hig\Ch{C2}{h  }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{God} of wonders beyond our galax\Ch{D4}{y  }\Ch{D}{   }

\Ch{Em}{You} ar\Ch{C2}{e h}oly, holy

\Ch{G}{The} universe declares your ma\Ch{D4}{jes}\Ch{D}{ty }

\Ch{Em}{You} ar\Ch{C2}{e h}oly, holy 
\end{SBVerse}
\begin{SBVerse}
\Ch{C2}{Hal}lelujah to the \Ch{D4}{Lor}d of heaven and earth (4x)
\end{SBVerse}
\end{song}\begin{song}{Good to Me}{G}
{Craig  Musseau}
{Craig  Musseau}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{I c}ry \Ch{C}{out}

for your \Ch{Em}{han}d of \Ch{D}{mer}cy to \Ch{C}{hea}l me

\Ch{G}{I a}m \Ch{C}{wea}k

I \Ch{Em}{nee}d your \Ch{D}{lov}e to \Ch{C}{fre}e me
\end{SBVerse}
\begin{SBVerse}
Oh \Ch{G/B}{Lor}d, my \Ch{C}{roc}k

My \Ch{G/B}{str}ength in \Ch{C}{wea}kness,

Come \Ch{Em}{res}cue \Ch{Bm7}{me }oh \Ch{C2}{Lor}d
\end{SBVerse}
\begin{SBVerse}
You are my \Ch{D}{hop}e,

your \Ch{G/B}{pro}mise \Ch{C}{nev}er \Ch{Dsus}{fai}ls\Ch{D/F#}{   }   \Ch{G}{me }

And my \Ch{D}{des}ire

Is to \Ch{G/B}{fol}low \Ch{C}{you} for \Ch{Dsus}{- e} -\Ch{D/F#}{ ve}r. \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
For you are \Ch{C}{goo}d

For you are \Ch{G/B}{goo}d

For you are \Ch{Am7}{goo}d \Ch{G}{to }\Ch{D/F#}{me }

\Ch{D}{For} you are \Ch{C}{goo}d

For you are \Ch{G/B}{goo}d

For you are \Ch{Am7}{goo}d \Ch{G}{to }\Ch{D/F#}{me.}
\end{SBVerse}
\end{song}\begin{song}{Grace Flows Down}{D}
{Louie Giglio}
{Louie Giglio}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Ama}zing \Ch{Bm}{gra}ce, \Ch{G}{how} sweet the \Ch{A}{sou}nd

\Ch{D}{Ama}zing \Ch{Bm}{lov}e, \Ch{G}{now} flowing \Ch{A}{dow}n

\Ch{G}{Fro}m hands and \Ch{A}{fee}t, that were \Ch{D}{nai}led to the \Ch{Bm}{tre}e

\Ch{G}{Gra}ce flows \Ch{A}{dow}n and covers \Ch{D}{me }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{It }covers \Ch{G}{me } \Ch{A}{   }

\Ch{A}{It }covers \Ch{G}{me } \Ch{A}{   }

\Ch{A}{It }covers \Ch{G}{me } \Ch{A}{   }

\Ch{A}{And} covers \Ch{D}{me.}  \Ch{Bm}{   }
\end{SBVerse}
\end{song}\begin{song}{Great is Thy Faithfulness}{D}
{Thomas O. Chilsholm}
{Thomas O. Chilsholm}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Gr\Ch{D}{eat} is thy f\Ch{G}{ait}hfulness,\Ch{A7}{ O }God my F\Ch{D}{ath}er,

T\Ch{G}{her}e is no sh\Ch{D}{ado}w of t\Ch{E}{urn}ing with T\Ch{A}{hee};

T\Ch{A7}{hou} changest n\Ch{D}{ot,} Thy comp\Ch{D}{ass}ions they \Ch{Em7}{fai}l not

\Ch{G}{As }Thou has b\Ch{D}{een} Thou f\Ch{A}{ore}ver w\Ch{A7}{ilt} \Ch{D}{be.}
\end{SBVerse}
\begin{SBVerse}
G\Ch{A}{rea}t is Thy f\Ch{D}{ait}hfulness!

G\Ch{B}{rea}t is Thy f\Ch{Em}{ait}hfulness!

M\Ch{A7}{orn}ing by m\Ch{D}{orn}ing new mer\Ch{E}{cie}s I s\Ch{A}{ee.}

\Ch{A7}{All} I have n\Ch{D}{eed}ed Thy h\Ch{D}{and} hath pro\Ch{Em7}{vid}ed

\Ch{G}{Gre}at is Thy f\Ch{D}{ait}hfulness, \Ch{A}{Lor}d u\Ch{A7}{nto} \Ch{D}{me.}
\end{SBVerse}
\begin{SBVerse}
Summer and winter, and springtime and harvest,

Sun, moon, and stars in their courses above

Join with all nature in manifold witness

To Thy great faithfulness, mercy and love.
\end{SBVerse}
\begin{SBVerse}
Pardon for sin and a peace that endureth,

Thy own dear presence to cheer and to guide. 

Strength for today and bright hope for tomorrow

Blessings all mine, with ten thousand beside.
\end{SBVerse}
\end{song}\begin{song}{Great Light Of The World}{G}
{Bebo Norman}
{Bebo Norman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Sometimes at n\Ch{Em	}{igh}t  When \Ch{G2}{I a}m \Ch{G}{afr}aid

I cover my \Ch{Em}{eye}s  And I cover my s\Ch{G2}{ham}e \Ch{G}{   }

So here in the \Ch{Em}{dar}k  Broken ap\Ch{C}{art}

Come with your l\Ch{Am}{igh}t  And fill up my h\Ch{D}{ear}t\Ch{Gsus}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Oh }great light of the world

Fill up my \Ch{Em}{sou}l

           Am      C                  Dsus  D  (C/D, second time)

I'm half a man here  So come make me whole

\Ch{G}{Oh }great light of the world

Come to i\Ch{Em}{mpa}rt

The light of your \Ch{C}{gra}c\Ch{D}{e t}o fill up my h\Ch{G}{ear}t
\end{SBVerse}
\begin{SBVerse}
The wind of this w\Ch{Em}{orl}d  Can push us a\Ch{G2}{rou}nd \Ch{G}{   }

Folding us \Ch{Em}{up } Backing us d\Ch{G2}{own}   \Ch{G}{   }

Here in the d\Ch{Em}{ark}  I'm not al\Ch{C}{one}

So come with your st\Ch{Am}{ren}gth  And carry me \Ch{D/F#}{hom}e   \Ch{G}{   } \Ch{Dsus}{   }
\end{SBVerse}
\end{song}\begin{song}{Grow Something New}{G}
{Matt Frazier}
{Matt Frazier}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Lor}d, you're the keeper of \Ch{Am7}{wha}t you grow

You \Ch{G}{wat}er, you guard, \Ch{Am7}{for} the fruit to show;

for \Ch{C}{mer}cy and \Ch{Em}{jus}tice to \Ch{F7}{flo}w.

You \Ch{C}{pla}nted the \Ch{Em}{vin}eyard,

our \Ch{F7}{nee}ds \Ch{Am7}{you} \Ch{D}{kno}w...
\end{SBVerse}
\begin{SBVerse}
Grow something \Ch{G}{new} in our lives, oh \Ch{C}{God}.

Grow something \Ch{Am7}{pea}ceful,

\Ch{Bm7}{Gro}w something \Ch{Em}{tru}e.

Grow something \Ch{G}{new} in our lives, oh \Ch{C}{God}.

Grow something \Ch{Em}{new},

Turn our \Ch{D}{hop}e back to \Ch{G}{you}.
\end{SBVerse}
\begin{SBVerse}
You broke down the wall of hostility.

You bring us near you so we can see

Who you want us to be:

Not many but one for eternity.
\end{SBVerse}
\end{song}\begin{song}{Hallelujah (Your Love Is Amazing)}{G}
{Brian Doerksen}
{Brian Doerksen}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Your love is a\Ch{G}{maz}ing, steady and unc\Ch{C2}{han}ging

Your love is a \Ch{Dsus}{mou}ntain, firm beneath my \Ch{C2}{fee}t

Your love is a \Ch{G}{mys}tery, how you gently \Ch{C2}{lif}t me

When I am su\Ch{Dsus}{rro}unded, your love carries \Ch{C2}{me }
\end{SBVerse}
\begin{SBVerse}
Hallelu\Ch{G}{jah}, hallel\Ch{Dsus}{uja}h

Hallelu\Ch{Em7}{jah}, \Ch{C2}{you}r love makes me sing

Hallelu\Ch{G}{jah}, hallel\Ch{Dsus}{uja}h

Hallelu\Ch{Em7}{jah}, \Ch{C2}{you}r love makes me sing
\end{SBVerse}
\begin{SBVerse}
Your love is su\Ch{G}{rpr}ising, I can feel it r\Ch{C2}{isi}ng

All the joy that's g\Ch{Dsus}{row}ing deep inside of m\Ch{C2}{e  }

Every time I s\Ch{G}{ee }you, all your goodness s\Ch{C2}{hin}es through

And I can feel this \Ch{Dsus}{God} song, rising up in \Ch{C2}{me }
\end{SBVerse}
\end{song}\begin{song}{He Has Made Me Glad}{D}
{Leona Von Brethorst}
{Leona Von Brethorst}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
I will \Ch{D}{ent}er His g\Ch{G}{ate}s with thanksg\Ch{D}{ivi}ng in my he\Ch{D}{art},

I will \Ch{D}{ent}er His c\Ch{G}{our}ts with pr\Ch{A}{ais}e!

I will s\Ch{D}{ay }this is the d\Ch{G}{ay }that the L\Ch{D}{ord} has m\Ch{Bm}{ade},

I w\Ch{G}{ill} rejoice for H\Ch{A}{e h}as made me gl\Ch{D}{ad.}
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{He }has made me gl\Ch{G}{ad!}  \Ch{D}{He }has made me g\Ch{Bm}{lad}!

I w\Ch{G}{ill} rejoice for H\Ch{A}{e h}as made me gl\Ch{D}{ad.}\Ch{G}{   }\Ch{D}{   }

\Ch{D}{He }has made me gl\Ch{G}{ad,} \Ch{D}{He }has made me g\Ch{Bm}{lad}.

I w\Ch{G}{ill} rejoice for \Ch{A}{He }has made me gl\Ch{D}{ad.}
\end{SBVerse}
\end{song}\begin{song}{He Is Exalted}{G}
{Twila Paris}
{Twila Paris}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{He }is exalted the \Ch{G/B}{Kin}g is exalted on \Ch{C}{hig}h, I will \Ch{C}{pra\Ch{/E}{}is}e \Ch{D/F#}{Him}
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{He }is exalted for\Ch{G/B}{eve}r exalted and \Ch{C}{I  }\Ch{D/C}{wil}l   \Ch{C}{pra\Ch{/D}{}is}e \Ch{D}{His} \Ch{Esus}{nam}e  \Ch{E}{   }\Ch{E/D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{Am}{He }\Ch{Em/G}{is }the \Ch{D/F#}{Lor}d, \Ch{D}{for}e\Ch{G}{ver} His t\Ch{Bm7}{rut}h shall r\Ch{C}{eig}\Ch{G/B}{n  }
\end{SBVerse}
\begin{SBVerse}
\Ch{Am}{Hea}\Ch{Em/G}{ven} and \Ch{D/F#}{ear}th,\Ch{D}{  r}e\Ch{G}{joi}ce in His \Ch{Bm7}{hol}y \Ch{C}{nam}\Ch{G/B}{e  }
\end{SBVerse}
\begin{SBVerse}
\Ch{Am}{He }is ex\Ch{Am/G}{alt}ed the \Ch{Fmaj9}{Kin}g is ex\Ch{Am7/D}{alt}ed on \Ch{G}{hig}h
\end{SBVerse}
\end{song}\begin{song}{He Knows My Name}{D}
{Tommy Walker}
{Tommy Walker}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{I  }\Ch{A}{hav}e a \Ch{D/F#}{Mak}er \Ch{G}{   }

\Ch{D}{He }\Ch{G}{for}med my \Ch{A}{hea}\Ch{Asus}{rt }

\Ch{D/F#}{Be }for\Ch{A}{e e}ven \Ch{D/F#}{tim}e be\Ch{G}{gan}

My \Ch{D}{lif}e was \Ch{A}{in }his \Ch{D}{han}ds\Ch{Dsus}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{He }\Ch{D}{kno}ws my \Ch{A}{nam}\Ch{Asus}{e  }   \Ch{A}{   }

\Ch{G}{He }\Ch{D}{kno}ws my \Ch{A}{eve}ry \Ch{D}{tho}ught

\Ch{G}{He }\Ch{D}{see}s each \Ch{A}{tea}r that \Ch{Bm}{fal}ls

and \Ch{G}{He }hears \Ch{A}{me }when \Ch{D}{I c}all
\end{SBVerse}
\begin{SBVerse}
I have a Father

He calls me His own

He'll never leave me

No matter where I go
\end{SBVerse}
\end{song}\begin{song}{Hear The Music Of My Heart}{G}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
 \Ch{Em}{Lor}d, hear the music \Ch{G}{of }my heart;

 \Ch{G7/B}{Hea}r all the pourings o\Ch{C}{f m}y soul.

 \Ch{Em}{Son}gs telling of a li\Ch{G}{fe }of live:

\Ch{Fmaj7}{ Je}sus, this is all for You.\Ch{C2}{   }

 \Ch{Em}{You}'ve become the ruler o\Ch{G}{f m}y heart;

 \Ch{G7/B}{You}'ve become the lover o\Ch{C}{f m}y soul.

 \Ch{Em}{You}'ve become the saviour of\Ch{G}{ th}is life:

\Ch{Fmaj7}{ Yo}u're everything to \Ch{C2}{me.}
\end{SBVerse}
\begin{SBVerse}
 Oh now \Ch{Em}{Jes}us, Jesus, \Ch{G}{I w}ill pour my praise on You.

 \Ch{A7/C#}{Wor}ship, worship, \Ch{Cmaj9}{dem}onstrate my love for You.

 \Ch{Em}{May} I come to \Ch{G}{be }a blessing to Your heart.

 \Ch{A7/C#}{Jes}us, Jesus, \Ch{Cmaj9}{who} can tell how wonderful You are.

\Ch{G}{ Ho}w wonderful Y\Ch{A7/C#}{ou }are.\Ch{Cmaj9}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{Em7+11}{ O,} how \Ch{Am11/D}{won}derful\Ch{Em9sus4/B}{   }     You \Ch{Cmaj9}{are}.     \Ch{Em}{   }

 (Repeat)
\end{SBVerse}
\end{song}\begin{song}{Here I Am A Sinner Free}{A}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{Her}e am I a sinner free, pardoned by your majesty

\Ch{D}{You}r love has led me into lib\Ch{A}{ert}y.

\Ch{A}{Hol}y King upon the throne, You've made this heart Your very own

\Ch{D}{I f}eel like the leper who's beed he\Ch{A}{ale}d!
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Los}t and dirty yet You found me

\Ch{A/C#}{Sta}ined by sin but you have cleansed me

\Ch{Bm7}{Can} it be I'm precious in you \Ch{A}{sig}ht?

\Ch{D}{Wha}t is a man and who am I?

\Ch{A/C#}{I'm} a child of God my father's pride

\Ch{Bm7}{Wha}t a joy to be the Lord's d\Ch{A}{eli}ght!
\end{SBVerse}
\begin{SBVerse}
I have known a love so sweet, a saving love that brings relief

A healing love that makes the blind eyes see.

King of love and Prince of peace, Your sheperds love is tending me

A love that satisfies my deepest needs.
\end{SBVerse}
\end{song}\begin{song}{Here I Am To Worship (Light of the World)}{E}
{Tim Hughes}
{Tim Hughes}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Lig}ht of the \Ch{Bsus}{wor}ld

You stepped \Ch{F#m}{dow}n into darkness

\Ch{E}{Ope}ned my \Ch{Bsus}{eye}s, let m\Ch{E/A}{e s}ee

\Ch{E}{Bea}uty that \Ch{Bsus}{mad}e this \Ch{F#m}{hea}rt adore You

\Ch{E}{Hop}e of a \Ch{Bsus}{lif}e spent with\Ch{E/A}{ Yo}u
\end{SBVerse}
\begin{SBVerse}
Here I \Ch{Bsus}{am }to \Ch{E}{wor}ship

Here I am to \Ch{B/D#}{bow} down

Here I am to \Ch{E/G#}{say} that You're my \Ch{A}{God}

You're altogether \Ch{E}{lov}ely

Altogether \Ch{B/D#}{wor}thy

Altogether \Ch{E/G#}{won}derful to \Ch{A}{me }
\end{SBVerse}
\begin{SBVerse}
King of all days

Oh so highly exalted

Glorious in Heaven above

Humbly You came to the earth You created

All for love's sake became poor
\end{SBVerse}
\begin{SBVerse}
Ill n\Ch{B/D#}{eve}r k\Ch{E/G#}{now} how m\Ch{A}{uch} it cost

To \Ch{B/D#}{see} my \Ch{E/G#}{sin} upon\Ch{A}{ th}at cross
\end{SBVerse}
\end{song}\begin{song}{His Banner Over Me}{G}
{Kevin Prosch}
{Kevin Prosch}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
He bo\Ch{G}{ugh}t me to his banqueting table. (echo) 

He bo\Ch{G}{ugh}t me to his banqueting table. (echo) 

And His banner,\Ch{C}{ ov}er me, is love, is lov\Ch{G}{e. }\Ch{C}{   }   \Ch{G}{   }\Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
We can feel t\Ch{G}{he }love, of God in thi\Ch{Am}{s p}lace. 

We beli\Ch{G/B}{eve} Your goodness, we receive your grace. \Ch{C}{   }

We delig\Ch{G}{ht }ourselves in at Your table, oh God.\Ch{Am}{   }

You do all t\Ch{G/B}{hin}gs well, just look at ou\Ch{C}{r l}ives. 
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{I a}m my Beloved's and He is mine. (echo) 

\Ch{G}{I a}m my Beloved's and He is mine. (echo) 

And His banner,\Ch{C}{ ov}er me, is love, is lov\Ch{G}{e. }\Ch{C}{   }   \Ch{G}{   }\Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
His ba\Ch{G}{nne}r over you, His banner over \Ch{C}{me,} 

His ban\Ch{G}{ner} over us, is love, lo\Ch{C}{ve,} l\Ch{G/B}{ove}, l\Ch{Am}{ove}. \Ch{D}{   }
\end{SBVerse}
\end{song}\begin{song}{History Maker}{C}
{Martin Smith}
{Martin Smith}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Is it \Ch{Am}{tru}e today that when \Ch{F}{peo}ple pray

Cloudless \Ch{Am}{ski}es will break, Kings and \Ch{F}{Que}ens will shake?

Yes it's \Ch{G}{tru}e!! And I believ\Ch{F}{e i}n it:

I'm living for \Ch{C}{you\Ch{G/B}{}. } \Ch{Am}{   } \Ch{F}{   }
\end{SBVerse}
\begin{SBVerse}
Is it \Ch{Asus4}{tru}e today that when \Ch{F}{peo}ple pray

We'll see \Ch{Asus4}{dea}d men rise, and the \Ch{F}{bli}nd set free?

Yes it's \Ch{G}{tru}e!! And I be\Ch{F}{lie}ve in it:

I'm living for \Ch{C}{you\Ch{G/B}{}. } \Ch{Am}{   } \Ch{F}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{I'm} gonna be a History \Ch{Am}{Mak}er in this \Ch{F}{lan}d:

\Ch{C}{I'm} gonna be a speaker of \Ch{Am}{tru}th to all man\Ch{F}{kin}d;

\Ch{C}{I'm} gonna st\Ch{G/B}{and}, \Ch{Am}{I'm} gonna run\Ch{F}{ in}to your \Ch{C}{arm}s\Ch{G/B}{,  }

Into your \Ch{Am}{arm}s a\Ch{F}{gai}n.
\end{SBVerse}
\begin{SBVerse}
Well it's true to\Ch{Am}{day} that when peo\Ch{F}{ple} stand

With the \Ch{Am}{fir}e of God and the trut\Ch{F}{h a}t hand

We'll see \Ch{Am}{mir}acles, we'll see \Ch{F}{ang}els sing

We'll see \Ch{Am}{bro}ken hearts making \Ch{F}{his}tory!!

Yes it's \Ch{G}{tru}e!! And I be\Ch{F}{lie}ve in it:

We're living for \Ch{C}{you}\Ch{G/B}{.  }  \Ch{Am}{   } \Ch{F}{   }
\end{SBVerse}
\end{song}\begin{song}{Holy Is The Lord}{G}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{We }stand and l\Ch{C}{ift} up our h\Ch{D}{and}s

for the jo\Ch{Em}{y o}f the Lo\Ch{C}{rd }is our st\Ch{D}{ren}gth

\Ch{G}{We }bow d\Ch{C}{own} and worship Him n\Ch{D}{ow }

How gr\Ch{Em}{eat} how awe\Ch{C}{som}e is \Ch{D}{He }
\end{SBVerse}
\begin{SBVerse}
And together we si\Ch{A}{ng }
\end{SBVerse}
\begin{SBVerse}
Holy is the L\Ch{G}{ord} G\Ch{C}{od }Almi\Ch{D}{ght}y

the \Ch{Em}{ear}th is f\Ch{C}{ill}ed with His g\Ch{D}{lor}y

Holy is the L\Ch{G}{ord} G\Ch{C}{od }Almi\Ch{D}{ght}y

the \Ch{Em}{ear}th is f\Ch{C}{ill}ed with His g\Ch{D}{lor}y

the \Ch{Em}{ear}th is f\Ch{C}{ill}ed with His g\Ch{D}{lor}y
\end{SBVerse}
\begin{SBVerse}
It's \Ch{G}{ris}ing up all a\Ch{D}{rou}nd

It's the a\Ch{F}{nth}em of the L\Ch{C}{ord}'s renown (2x)
\end{SBVerse}
\begin{SBVerse}
And together we s\Ch{A7}{ing} 

Everyone s\Ch{C}{ing}
\end{SBVerse}
\end{song}\begin{song}{Holy, Holy, Holy}{D}
{John B. Dykes}
{John B. Dykes}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Hol}y, \Ch{D/B}{hol}y, \Ch{A}{hol}\Ch{D}{y, }L\Ch{G}{ord} God Alm\Ch{D}{igh}ty

\Ch{A}{Ear}ly \Ch{D}{in }the \Ch{Bm}{mor}ni\Ch{A}{ng }our \Ch{A/E}{son}g shall r\Ch{E7}{ise} to \Ch{A}{The}\Ch{A7}{e  }

\Ch{D}{Hol}y, \Ch{D/B}{hol}y, \Ch{A}{hol}\Ch{D}{y, }m\Ch{G}{erc}iful and m\Ch{D}{igh}ty\Ch{D/C#}{   }

\Ch{Bm}{God} \Ch{D}{in }three \Ch{G}{per}\Ch{D}{son}s, \Ch{Em}{ble}ssed T\Ch{A}{rin}\Ch{D}{ity}
\end{SBVerse}
\begin{SBVerse}
Holy, holy, holy, all the saints adore Thee

Casting down their golden crowns around the glassy sea

Cherubim and seraphim, falling down before Thee

Which, wert and art and ever more shall be
\end{SBVerse}
\begin{SBVerse}
Holy, holy, holy, though the darkness hide Thee

Though the eye of sinful men Thy Glory may not see

Only Thou art holy, there is none beside Thee

Perfect in power, in love and purity
\end{SBVerse}
\begin{SBVerse}
Holy, holy, holy, Lord God Alimighy

All Thy works shall praise Thy Name in earth and sky and sea

Holy, holy, holy, merciful and mighty

God in three persons, blessed Trinity
\end{SBVerse}
\end{song}\begin{song}{Hosanna}{E}
{Brooke Fraser}
{Brooke Fraser}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{I s}ee the king of glory

\Ch{C#m}{Com}ing down the clouds with fire

The whole earth \Ch{F#m}{sha}kes

The whole earth s\Ch{G#m}{hak}es       \Ch{C#m}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{I s}ee his love and mercy

\Ch{C#m}{Was}hing over all our sin

The people \Ch{F#m}{sin}g

The people \Ch{B}{sin}g
\end{SBVerse}
\begin{SBVerse}
Hos\Ch{G#m}{an }- \Ch{A}{na }

Hos\Ch{B}{an }- \Ch{C#m}{na }

Hos\Ch{A}{ann}a in the \Ch{C#m}{hig}hes\Ch{B}{t  }

Hos\Ch{G#m}{an }- \Ch{A}{na }

Hos\Ch{B}{an }- \Ch{C#m}{na }

Hos\Ch{A}{ann}a in the \Ch{B}{hig}h\Ch{C#m}{est}
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{I s}ee a generation

\Ch{C#m}{Ris}ing up to take their place

With selfless \Ch{F#m}{fai}th

With selfless \Ch{G#m}{fai}th
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{I s}ee a near revival

\Ch{C#m}{Sta}ring as we pray and seek

We're on our \Ch{F#m}{kne}es

We're on our \Ch{B}{kne}es
\end{SBVerse}
\begin{SBVerse}
Instumental:
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{Hea}l my heart and make it \Ch{B}{cle}an

\Ch{E}{Ope}n my eyes to the \Ch{C#m}{thi}ngs I see

\Ch{A}{Sho}w me how to love like \Ch{B}{you}, have loved me\Ch{C#m}{   }

\Ch{A}{Bre}ak my heart for what breaks y\Ch{B}{our}s

\Ch{E}{Eve}rything I am for your \Ch{C#m}{kin}gdom's cause

\Ch{A}{As }I walk from earth in\Ch{B}{to }eterni\Ch{E}{ty }
\end{SBVerse}
\begin{SBVerse}
Hos\Ch{G#m}{an }- \Ch{A}{na }

Hos\Ch{B}{an }- \Ch{C#m}{na }

Hos\Ch{A}{ann}a in the \Ch{C#m}{hig}hes\Ch{B}{t  }

Hos\Ch{G#m}{an }- \Ch{A}{na }

Hos\Ch{B}{an }- \Ch{C#m}{na }

Hos\Ch{A}{ann}a in the \Ch{B}{hig}h\Ch{E}{est}
\end{SBVerse}
\end{song}\begin{song}{Hosanna (Praise Is Rising)}{G}
{Brenton Brown}
{Brenton Brown}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G5}{Pra}ise is rising, eyes are turning \Ch{G/B}{to }  \Ch{C2}{You}, we turn to\Ch{G5}{ Yo}u

Hope is stirring, hearts are yearning \Ch{G/B}{for}  \Ch{C2}{You}, we long for Y\Ch{G5}{ou }

'Cause when we s\Ch{D}{ee }You, we find st\Ch{C}{ren}gth to face the \Ch{G5}{day}

In Your Pr\Ch{D}{ese}nce all our f\Ch{C}{ear}s are washed a\Ch{G5}{way}, washed a\Ch{D}{way}
\end{SBVerse}
\begin{SBVerse}
Ho\Ch{Gsus}{san} - \Ch{G}{na,} ho\Ch{Em7}{san}na \Ch{C2}{   }

You are the G\Ch{G5}{od }Who saves\Ch{Dsus}{ us}, worthy of \Ch{Em7}{all} our pra\Ch{C2}{ise}s

Ho\Ch{Gsus}{san} - \Ch{G}{na,} ho\Ch{Em7}{san}na \Ch{C2}{   }

Come have Your \Ch{G5}{way} among \Ch{Dsus}{us }

We welcome You \Ch{Em7}{her}e, Lord J\Ch{C2}{esu}s
\end{SBVerse}
\begin{SBVerse}
\Ch{G5}{Hea}r the sound of hearts returning \Ch{G/B}{to }  \Ch{C2}{You}, we turn to \Ch{G5}{You}

In Your Kingdom broken lives are \Ch{G/B}{mad}e \Ch{C2}{new}, You make us \Ch{G5}{new}

'Cause when we s\Ch{D}{ee }You, we find st\Ch{C}{ren}gth to face the \Ch{G5}{day}

In Your Pr\Ch{D}{ese}nce all our f\Ch{C}{ear}s are washed a\Ch{G5}{way}, washed a\Ch{D}{way}
\end{SBVerse}
\end{song}\begin{song}{How Can I Keep From Singing}{G}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
There is an e\Ch{G}{ndl}ess song, echoes \Ch{D}{in }my soul, I \Ch{Em}{hea}r the music r\Ch{C}{ing}

And though the s\Ch{G}{tor}ms may come, I am h\Ch{D}{old}ing on

\Ch{Em}{To }the rock I cl\Ch{C}{ing}
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{How} can I keep from singing Your pr\Ch{D}{ais}e

How can I \Ch{C}{eve}r say en\Ch{G/B}{oug}h, how am\Ch{C}{azi}ng is Your l\Ch{D}{ove}

\Ch{G}{How} can I keep from shouting Your \Ch{D}{Nam}e

I know I am l\Ch{C}{ove}d by the K\Ch{G}{ing}, and it m\Ch{C}{ake}s my h\Ch{D}{ear}t want to s\Ch{G}{ing}
\end{SBVerse}
\begin{SBVerse}
I will lift m\Ch{G}{y e}yes in the d\Ch{D}{ark}est night, for I k\Ch{Em}{now} my Saviour l\Ch{C}{ive}s

And I will wa\Ch{G}{lk }with You, knowing You'll \Ch{D}{see} me through

\Ch{Em}{And} sing the songs You g\Ch{C}{ive} 
\end{SBVerse}
\begin{SBVerse}
I can s\Ch{m}{ing} in the t\Ch{G/B}{rou}bled times, s\Ch{C}{ing} when I w\Ch{D}{in }

I can s\Ch{Am}{ing} when I \Ch{G/B}{los}e my step and \Ch{C}{fal}l down ag\Ch{D}{ain}

I can \Ch{Am}{sin}g 'cause You \Ch{G/B}{pic}k me up, s\Ch{C}{ing} 'cause You're th\Ch{D}{ere}

I can \Ch{Am}{sin}g 'cause You \Ch{G/B}{hea}r me, Lord, when I c\Ch{C}{all} to You in pr\Ch{D}{aye}r

I can \Ch{Am}{sin}g with my \Ch{G/B}{las}t breath, s\Ch{C}{ing} for I kn\Ch{D}{ow }

That I'll \Ch{Am}{sin}g with the \Ch{G/B}{ang}els and the s\Ch{C}{ain}ts around the thr\Ch{D}{one}
\end{SBVerse}
\end{song}\begin{song}{How Deep the Father's Love for Us}{E}
{Stuart Townend}
{Stuart Townend}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{How} deep the Fa\Ch{	}{the}r's \Ch{F#m}{lov}e \Ch{G#m}{for} \Ch{A}{us }

\Ch{E/G#}{How} vast beyond \Ch{C#m}{all} m\Ch{B}{eas}ure

\Ch{E}{Tha}t He would give\Ch{F#m}{ Hi}s\Ch{G#m}{ on}ly\Ch{A}{ So}n

\Ch{E/B}{To }make a wretch H\Ch{B}{is }t\Ch{E}{rea}sure
\end{SBVerse}
\begin{SBVerse}
\Ch{E/G#}{How} great \Ch{	}{the} pai\Ch{C#m}{n o}f\Ch{B}{ se}a\Ch{A}{rin}g loss

\Ch{E/G#}{The} Father turns \Ch{C#m}{His} f\Ch{B}{ace} away

\Ch{E	}{As }wounds which ma\Ch{F#m}{r t}h\Ch{G#m}{e c}h\Ch{A}{ose}n One

\Ch{E/B}{Bri}ng many so\Ch{B}{ns }\Ch{E}{to }glory
\end{SBVerse}
\begin{SBVerse}
Behold the Man upon a cross

My guilt upon His shoulders

Ashamed, I hear my mocking voice

Call out among the scoffers
\end{SBVerse}
\begin{SBVerse}
It was my sin that held Him there

Until it was accomplished

His dying breath has brought me life

I know that it is finished
\end{SBVerse}
\begin{SBVerse}
I will not boast in anything

No gifts, no powr's, no wisdom

But I will boast in Jesus Christ

His death and resurrection
\end{SBVerse}
\begin{SBVerse}
Why should I gain from His reward?

I cannot give an answer

But this I know with all my heart

His wounds have paid my ransom
\end{SBVerse}
\end{song}\begin{song}{How Great Is Our God}{G}
{Ed Cash}
{Ed Cash}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
The s\Ch{G}{ple}ndor of the King, \Ch{Em7}{clo}thed in majesty,

Let all the earth re\Ch{C2}{joi}ce, all the earth rejoice.

He \Ch{G}{wra}ps Himself in light, and \Ch{Em7}{dar}kness tries to hide,

And trembles at his v\Ch{C2}{oic}e, trembles at his voice.
\end{SBVerse}
\begin{SBVerse}
How \Ch{G}{gre}at is our God, sing with\Ch{D/F#}{ me},

How \Ch{Em7}{gre}at is our God, all will see,

How \Ch{C}{gre}at, how g\Ch{D}{rea}t is our G\Ch{G}{od.}
\end{SBVerse}
\begin{SBVerse}
A\Ch{G}{ge }to age He stands, and \Ch{Em7}{tim}e is in His hands,

Beginning and the \Ch{C2}{end}, beginning and the end.

The G\Ch{G}{odh}ead, three in one: \Ch{Em7}{Fat}her, Spirit, Son,

The Lion and the \Ch{C2}{Lam}b, the Lion and the Lamb.
\end{SBVerse}
\begin{SBVerse}
N\Ch{G}{ame} above all names,\Ch{D/F#}{   }

W\Ch{Em7}{ort}hy of all praise,

My \Ch{C}{hea}rt will sing
\end{SBVerse}
\end{song}\begin{song}{How Great Thou Art}{A}
{Stuart K. Hine}
{Stuart K. Hine}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
O L\Ch{E7}{ord} my G\Ch{A}{od!}  When I in a\Ch{D}{wes}ome wonder

Consider a\Ch{A}{ll }the w\Ch{E7}{ork}s Thy hands have m\Ch{A}{ade},

I \Ch{E7}{see} the st\Ch{A}{ars}, I hear the m\Ch{D}{igh}ty thunder,

Thy power through\Ch{A}{out} the u\Ch{E7}{niv}erse displ\Ch{A}{aye}d.
\end{SBVerse}
\begin{SBVerse}
Then sings my soul, my S\Ch{D}{avi}or God to Th\Ch{A}{ee;}

How great Thou \Ch{E7}{art}!  How great Thou a\Ch{A}{rt!}

Then sings my soul, my S\Ch{D}{avi}or God to T\Ch{A}{hee};

How great Thou \Ch{Bm}{art}!  How g\Ch{E7}{rea}t Thou a\Ch{A}{rt!}
\end{SBVerse}
\begin{SBVerse}
When through the woods, the forest glades I wander

And hear the birds sing sweetly in the trees,

When I look down from lofty mountain grandeur

And hear the brook and feel the gentle breeze...
\end{SBVerse}
\begin{SBVerse}
And when I think that God, His Son not sparing,

Sent Him to die, I scarce can take it in;

That on the cross, my burden gladly bearing,

He bled and died to take away my sin...
\end{SBVerse}
\begin{SBVerse}
When Christ shall come with shout of acclamation

And take me home, what joy shall fill my heart!

Then I shall bow in humble adoration

And there proclaim, my God how great Thou art!
\end{SBVerse}
\end{song}\begin{song}{How He Loves}{C}
{David Crowder}
{David Crowder}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{He }is jealous for me,

\Ch{Am}{Lov}es like a hurricane, I am a tree,

\Ch{G}{Ben}ding beneath the weight of his wind and \Ch{F}{mer}cy.

\Ch{C}{Whe}n all of a sudden,

I am unaware of these\Ch{Am}{ af}flictions eclipsed by glory,

And I\Ch{G}{ re}alize just how beautiful You are,

And how\Ch{F}{ gr}eat Your affections are for me. (2nd time - Oh how He Loves)
\end{SBVerse}
\begin{SBVerse}
And\Ch{C}{ oh}, how He loves us\Ch{Am}{ oh}

Oh how He\Ch{G}{ lo}ves us,

How He loves us\Ch{F}{ al}l
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{He }loves us,

Oh how He\Ch{Am}{ lo}ves us,

Oh how He\Ch{G}{ lo}ves us,

Oh how He\Ch{F}{ lo}ves.
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{We }are His portion and He is our prize,

\Ch{Am}{Dra}wn to redemption by the grace in His eyes,

\Ch{G}{If }grace is an ocean, we're all \Ch{F}{sin}king.

\Ch{C}{So }Heaven meets earth like an unforeseen kiss,

\Ch{Am}{And} my heart turns violently inside of my chest,

\Ch{G}{I d}on't have time to maintain these regrets,

\Ch{F}{Whe}n I think about, the way?
\end{SBVerse}
\end{song}\begin{song}{How Majestic is Your Name}{C}
{Michael W. Smith}
{Michael W. Smith}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
O L\Ch{C}{ord}, our Lord

How maj\Ch{F}{est}ic is Your n\Ch{C}{ame} in all the e\Ch{G}{art}\Ch{C}{h. }

O L\Ch{C}{ord}, our Lord

How maj\Ch{F}{est}ic is Your n\Ch{C}{ame} in all the e\Ch{G}{art}\Ch{C}{h. }
\end{SBVerse}
\begin{SBVerse}
O L\Ch{F}{ord}\Ch{Dm7}{, w}e pra\Ch{G}{ise} Your na\Ch{C}{me!}

O L\Ch{F}{ord}\Ch{Dm7}{, w}e ma\Ch{G}{gni}fy Your na\Ch{C}{me;}

Pr\Ch{B}{inc}e of P\Ch{Em}{eac}e, M\Ch{D}{igh}ty G\Ch{G}{od,}

O L\Ch{C}{ord} G\Ch{F}{od }Alm\Ch{G}{igh}t\Ch{C}{y. }\Ch{(A)}{   }
\end{SBVerse}
\end{song}\begin{song}{Hungry}{E}
{Kathryn Scott}
{Kathryn Scott}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Hun}gry I come \Ch{C#m}{to } you for I \Ch{B}{kno}w You satis\Ch{A}{fy }

\Ch{E}{I a}m empty \Ch{C#m}{but} I know Your l\Ch{B}{ove} does not run d\Ch{A}{ry }
\end{SBVerse}
\begin{SBVerse}
So I w\Ch{B}{ait} for Y\Ch{A}{ou,} and I w\Ch{B}{ait} for Y\Ch{A}{ou }

\Ch{E}{I'm} falling on my kn\Ch{A}{ees}

\Ch{E}{Off}ering all of \Ch{A}{me }

\Ch{E}{Jes}us Your all this h\Ch{A}{ear}t is living f\Ch{E}{or }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{Bro}ken, I run \Ch{C#m}{to }You for Your a\Ch{B}{rms} are open w\Ch{A}{ide}

\Ch{E}{I a}m weary, \Ch{C#m}{but} I know Your t\Ch{B}{ouc}h restore my l\Ch{A}{ife}
\end{SBVerse}
\end{song}\begin{song}{I Could Sing of Your Love Forever}{E}
{Martin Smith}
{Martin Smith}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{  O}ver the mountains and the\Ch{F#m}{ se}a

Your river runs with love for \Ch{A2}{me }

And I will open up my \Ch{B}{hea}rt

And let the healer set me \Ch{E}{fre}e

I'm happy to be in the \Ch{F#m}{tru}th

And I will daily lift my \Ch{A2}{han}ds
\end{SBVerse}
\begin{SBVerse}
For I will always sing

Of \Ch{B}{whe}n your love came down
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{   }I could sing of your \Ch{F#m}{lov}e forever

\Ch{A2}{   }I could sing of your \Ch{B}{lov}e forever

\Ch{E}{   }I could sing of your \Ch{F#m}{lov}e forever

\Ch{A2}{   }I could sing of your \Ch{B}{lov}e forever
\end{SBVerse}
\begin{SBVerse}
\Ch{F#m}{   }Oh I feel like \Ch{E}{dan}cing

\Ch{A2}{   }It's foolishness I \Ch{B}{kno}w

\Ch{F#m}{   }But when the world has \Ch{E}{see}n the light

They will da\Ch{A2}{nce} with joy

Like we're da\Ch{B}{nci}ng now
\end{SBVerse}
\end{song}\begin{song}{I Give You My Heart}{G}
{Reuben Morgan}
{Reuben Morgan}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Th\Ch{G}{is }is my\Ch{D/F#}{ de}sir\Ch{Em}{e  }

To h\Ch{C}{ono}\Ch{G}{ur }\Ch{D/F#}{You}

\Ch{Em}{Lor}d, with all\Ch{D/F#}{ my}  h\Ch{G}{ear}t

I worship \Ch{Fmaj9}{You}      \Ch{C}{   } \Ch{C/D}{   }

\Ch{G}{All} I have \Ch{D/F#}{wit}hin\Ch{Em}{ me}

I g\Ch{C}{ive} Y\Ch{G}{ou }pr\Ch{D/F#}{ais}e

\Ch{Em}{All} that I\Ch{D/F#}{ ad}ore\Ch{G}{   }

Is in \Ch{Fmaj9}{You}     \Ch{C}{   } \Ch{C/D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Lor}d, I give You my \Ch{D/F#}{hea}rt

I give You my \Ch{Am7}{sou}l

I \Ch{C/D}{liv}e for You alone

\Ch{G}{Eve}ry breath that I \Ch{D/F#}{tak}e

Every moment I'm \Ch{Am7}{awa}ke

Lord, \Ch{C/D}{hav}e Your \Ch{D}{way} in \Ch{G}{me }
\end{SBVerse}
\end{song}\begin{song}{I Love You, Lord}{E}
{Laurie Klein}
{Laurie Klein}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
I lov\Ch{E}{e Y}ou, Lord

and I \Ch{B}{lif}t \Ch{E}{my }voice

to \Ch{A}{wor}\Ch{E}{shi}p \Ch{F#m}{You}

\Ch{E}{o m}y \Ch{A}{sou}l, re\Ch{B}{joi}ce!

Take \Ch{E}{joy}, My King, in \Ch{B}{wha}t \Ch{E}{You} hear,

may it be a \Ch{A}{swe}et, \Ch{E}{swe}et \Ch{F#m}{sou}nd

\Ch{B}{in }Your \Ch{A}{ear}. \Ch{E}{   }
\end{SBVerse}
\end{song}\begin{song}{I Surrender All}{D}
{Winfield S. Weeden}
{Winfield S. Weeden}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{All} to Jesus \Ch{A}{I s}urrender

\Ch{Bm}{All} to H\Ch{G}{im }I fr\Ch{A}{eel}y g\Ch{D}{ive}

\Ch{D	}{I w}ill\Ch{A}{ ev}er love and trust Him

\Ch{Bm}{In }His p\Ch{G}{res}ence d\Ch{A}{ail}y l\Ch{D}{ive}
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{I s}urrender \Ch{Em}{all}

\Ch{A}{I s}urrender \Ch{D}{all} \Ch{(G)}{   }

\Ch{D}{All} to Thee my \Ch{D/F#}{ble}ssed \Ch{G}{Sav}ior

\Ch{A}{I s}urrender \Ch{D}{all}
\end{SBVerse}
\begin{SBVerse}
All to Jesus I surrender

Humbly at His feet I bow

Wordly pleasures all forsaken

Take me Jesus, take me now
\end{SBVerse}
\begin{SBVerse}
All to Jesus I surrender

Make me Savior, wholy Thine

Let me feel the Holy Spirit

Truly know that Thou art mine
\end{SBVerse}
\begin{SBVerse}
All to Jesus I Surrender

Lord, I give myself to Thee

Fill me with Thy love and power

Let Thy blessing fall on me
\end{SBVerse}
\end{song}\begin{song}{I Will Follow}{G}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Em}{   } Where You go, I'll go   \Ch{C/E}{   }

Where You stay, I'll stay   \Ch{G/D}{   }

When You move, I'll move    \Ch{D}{   }

I will follow         \Ch{Em7}{   }  \Ch{C2}{   } \Ch{G}{   }\Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{All} Your ways are good    \Ch{Em7}{   }

All Your ways are sure      \Ch{D}{   }

I will tr\Ch{G}{ust} in Yo\Ch{D/F#}{u a}lone\Ch{C}{   }

Higher than my sight     \Ch{Em7}{   }

High above my life     \Ch{D}{   }

I will t\Ch{G}{rus}t in You alone  \Ch{C}{   }

In Yo\Ch{D}{u a}lone
\end{SBVerse}
\begin{SBVerse}
\Ch{Em}{   } Where You go, I'll go   \Ch{C/E}{   }

Where You stay, I'll stay   \Ch{G/D}{   }

When You move, I'll move    \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
I will follow You

\Ch{Em7}{   } Who You love, I'll love \Ch{C2}{   }

How You serve I'll serve    \Ch{G}{   }

If this life I lo\Ch{D}{se,} I will follow You   \Ch{Em7}{   }  \Ch{C2}{   }

I will follow You  \Ch{G}{   } \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Lig}ht unto the world \Ch{Em7}{   }

Light unto my life   \Ch{D}{   }

I will l\Ch{G}{ive} for You\Ch{D}{ al}one \Ch{C}{   }

You're the one I seek      \Ch{Em7}{   }

Knowing I will find     \Ch{D}{   }

All I ne\Ch{G}{ed }in You alone, \Ch{C}{in }You alone\Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{In }You there's life\Ch{G}{ ev}erlastin\Ch{D}{g  }

\Ch{C}{In }You there's free\Ch{G}{dom} for my so\Ch{D}{ul }

\Ch{C}{In }You there's joy,\Ch{G}{ un}ending jo\Ch{D}{y  }    \Ch{C}{   }

\Ch{G}{and} I will follow\Ch{D}{   }
\end{SBVerse}
\end{song}\begin{song}{I Will Never Be}{D}
{Geoff Bullock}
{Geoff Bullock}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{I w}ill never \Ch{G}{be }the \Ch{G}{sam}e \Ch{A}{aga\Ch{D}{}in}

\Ch{G}{I c}an never re\Ch{A}{tur}n, 

I've \Ch{G}{clo}sed \Ch{A}{the} \Ch{D}{doo}r.\Ch{Asus4}{   }

\Ch{D}{I w}ill walk the \Ch{G}{pat}h, I'll \Ch{G}{run} \Ch{A}{the} \Ch{D}{rac}e

and \Ch{G}{I w}ill ne\Ch{A}{ver} be the \Ch{G}{sam}e \Ch{A}{aga}\Ch{D}{in }
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Fal}l like \Ch{G}{fir}e,

\Ch{A}{soa}k like \Ch{D}{rai}n,

\Ch{C}{flo}w like mighty \Ch{G}{wat}ers

a\Ch{A}{gai}n and a\Ch{D}{gai}n:

\Ch{Bb}{Swe}ep away the \Ch{C}{dar}kness,

\Ch{Am7}{bur}n away the \Ch{D}{cha}ff

and \Ch{Em}{let} the flame \Ch{D}{bur}n

to \Ch{G}{glo}rify you \Ch{A}{nam}e. \Ch{D}{   } \Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{The}re are higher \Ch{G}{hei}ghts, there are \Ch{G}{dee}\Ch{A}{per} \Ch{D}{sea}s

\Ch{G}{Wha}tever you need to \Ch{A}{do }

Lord \Ch{G}{do } \Ch{A}{in } \Ch{D}{me } \Ch{Asus4}{   }

\Ch{D}{The} Glory of \Ch{G}{God} \Ch{G}{fil}ls \Ch{A}{my }\Ch{D}{lif}e

And \Ch{G}{I w}ill n\Ch{A}{eve}r be the \Ch{G}{sam}e \Ch{A}{aga}\Ch{D}{in }
\end{SBVerse}
\end{song}\begin{song}{I Will Not Be Silent}{G}
{David Crowder}
{David Crowder}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{B7sus}{Mak}e a joyful noise to the \Ch{D}{Lor}d \Ch{E}{all} the \Ch{B7sus}{ear}th   \Ch{D}{   } \Ch{E}{   }

Make a\Ch{B7sus}{ jo}yful noise to the L\Ch{D}{ord} \Ch{E}{all} the\Ch{B7sus}{ ea}rth  \Ch{D}{   } \Ch{E}{   }  (Repeat)
\end{SBVerse}
\begin{SBVerse}
\Ch{C2}{The} flowers of the fields are \Ch{G/B}{cry}ing to be heard

\Ch{C2}{The} trees of the forest si\Ch{G/B}{ngi}ng

\Ch{C2}{And} all of the mountains \Ch{G/B}{wit}h one voice

\Ch{C2}{Wil}l join in the chorus o\Ch{G/B}{f t}hi\Ch{Dsus}{s w}orld
\end{SBVerse}
\begin{SBVerse}
\Ch{G2}{And} I will no\Ch{D/F#}{t b}e silent

\Ch{Em7}{And} I will no\Ch{C2}{t b}e quiet anymore

\Ch{G2}{I w}ill\Ch{D/F#}{ no}t be silent

\Ch{Em7}{I w}il\Ch{C2}{l n}ot be quiet anymore

\Ch{G2}{Run}ning Through the \Ch{D/F#}{for}est

Dive into the l\Ch{Em7}{ake} bare\Ch{C2}{ fe}et on beaches \Ch{G2}{whi}te

Stan\Ch{D/F#}{din}g in the canyon painted hills \Ch{Em7}{aro}und

the \Ch{C2}{win}d against my skin

\Ch{G2}{Eve}ry ocean every sea

\Ch{D/F#}{Eve}ry river every stream

\Ch{Em7}{Eve}ry mountain every tree

\Ch{C2}{Eve}ry blade of grass will sing
\end{SBVerse}
\begin{SBVerse}
Make a j\Ch{G2}{oyf}ul n\Ch{D}{ois}e to the \Ch{Em7}{Lor}d   all the \Ch{C2}{ear}th   (4x)
\end{SBVerse}
\end{song}\begin{song}{I Will Offer Up My Life}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{I w}ill \Ch{D/F#}{off}er up my \Ch{G}{lif}e

In \Ch{A}{spi}rit and truth\Ch{D}{,  }

Pouring \Ch{D/F#}{out} the oil of \Ch{G}{lov}e

As my \Ch{A}{wor}ship to You \Ch{D}{   }

In \Ch{D/F#}{sur}render I must \Ch{G}{giv}e my \Ch{A}{eve}ry part; \Ch{D}{   }

Lord, \Ch{D/F#}{rec}eive the sacri\Ch{G}{fic}e  

Of a \Ch{A}{bro}ken heart \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
Jesus, what can I \Ch{G}{giv}e, \Ch{A}{wha}t can I \Ch{D}{bri}ng

To so faithful a \Ch{G}{fri}end, to so \Ch{A}{lov}ing a \Ch{D}{Kin}g?

Savior, what can be \Ch{G}{sai}d, \Ch{A}{wha}t can be \Ch{D}{sun}g

As a praise of Your \Ch{G}{nam}e

For the \Ch{A}{thi}ngs You have \Ch{D}{don}e?

Oh my words could not \Ch{Em}{tel}l, \Ch{D/F#}{not} even in \Ch{G}{par}t  \Ch{D}{   }

Of the \Ch{Em}{deb}t of \Ch{D/F#}{lov}e that is \Ch{G}{owe}d

By\Ch{A}{ th}is thankful he\Ch{D}{art}
\end{SBVerse}
\begin{SBVerse}
You deserve my every breath

For You've paid the great cost;

Giving up Your life to death,

Even death on a cross

You took all my shame away,

There defeated my sin

Opened up the gates of heaven

And have beckoned me in
\end{SBVerse}
\end{song}\begin{song}{In Christ Alone}{D}
{Keith Getty}
{Keith Getty}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
In \Ch{G}{Chr}ist a\Ch{D}{lon}e my \Ch{G}{hop}e is \Ch{A}{fou}nd

\Ch{D/F#}{He }is my \Ch{G}{lig}ht my \Ch{A}{str}ength my \Ch{D}{son}g

This \Ch{G}{Cor}ner\Ch{D}{sto}ne, this \Ch{G}{sol}id \Ch{A}{Gro}und

\Ch{D/F#}{Fir}m through the \Ch{G}{fie}rcest \Ch{A}{dro}ught and \Ch{D}{sto}rm

What \Ch{D/F#}{hei}ghts of \Ch{G}{lov}e, what \Ch{D/F#}{dep}ths of \Ch{A}{pea}ce

When \Ch{D/F#}{fea}rs are \Ch{G}{sti}lled when \Ch{D/F#}{str}ivings \Ch{A}{cea}se!

My \Ch{G}{Com}for\Ch{D}{ter} my \Ch{G}{All} in \Ch{A}{All}

\Ch{D/F#}{Her}e in the \Ch{G}{lov}e of \Ch{A}{Chr}ist I \Ch{D}{sta}nd
\end{SBVerse}
\begin{SBVerse}
In \Ch{G}{Chr}ist a\Ch{D}{lon}e! - who \Ch{G}{too}k on \Ch{A}{fle}sh

\Ch{D/F#}{Ful}lness of \Ch{G}{God} in \Ch{A}{hel}pless \Ch{D}{bab}e!

This \Ch{G}{Gif}t of \Ch{D}{lov}e and \Ch{G}{rig}hteous\Ch{A}{nes}s

\Ch{D/F#}{Sco}rned by the \Ch{G}{one}s He \Ch{A}{cam}e to \Ch{D}{sav}e

Till \Ch{D/F#}{on }that \Ch{G}{cro}ss as \Ch{D/F#}{Jes}us \Ch{A}{die}d

The \Ch{D/F#}{wra}th of \Ch{G}{God} was \Ch{D/F#}{sat}is\Ch{A}{fie}d -

For e\Ch{G}{ver}y s\Ch{D}{in }on H\Ch{G}{im }was l\Ch{A}{aid}:

\Ch{D/F#}{Her}e in the \Ch{G}{dea}th of \Ch{A}{Chr}ist I \Ch{D}{liv}e
\end{SBVerse}
\begin{SBVerse}
There \Ch{G}{in }the g\Ch{D}{rou}nd His b\Ch{G}{ody} l\Ch{A}{ay }

\Ch{D/F#}{Lig}ht of the w\Ch{G}{orl}d by d\Ch{A}{ark}ness sl\Ch{D}{ain}

Then b\Ch{G}{urs}ting f\Ch{D}{ort}h in gl\Ch{G}{ori}ous D\Ch{A}{ay }

\Ch{D/F#}{Up }from the gr\Ch{G}{ave} He r\Ch{A}{ose} ag\Ch{D}{ain}!

And\Ch{D/F#}{ as} He st\Ch{G}{and}s in \Ch{D/F#}{vic}tor\Ch{A}{y  }

Sin's \Ch{D/F#}{cur}se has l\Ch{G}{ost} its \Ch{D/F#}{gri}p on \Ch{A}{me }

For \Ch{G}{I a}m H\Ch{D}{is }and \Ch{G}{He }is m\Ch{A}{ine} -

\Ch{D/F#}{Bou}ght with the pr\Ch{G}{eci}ous bl\Ch{A}{ood} of Chr\Ch{D}{ist}
\end{SBVerse}
\begin{SBVerse}
No g\Ch{G}{uil}t in l\Ch{D}{ife} no f\Ch{G}{ear} in d\Ch{A}{eat}h

\Ch{D/F#}{Thi}s is the p\Ch{G}{owe}r of Ch\Ch{A}{ris}t in \Ch{D}{me }

From l\Ch{G}{ife}'s first c\Ch{D}{ry }to f\Ch{G}{ina}l br\Ch{A}{eat}h

\Ch{D/F#}{Jes}us comm\Ch{G}{and}s my d\Ch{A}{est}in\Ch{D}{y  }

No \Ch{D/F#}{pow}er of h\Ch{G}{ell} no s\Ch{D/F#}{che}me of m\Ch{A}{an }

Can \Ch{D/F#}{eve}r pl\Ch{G}{uck} me \Ch{D/F#}{fro}m His h\Ch{A}{and}

Till h\Ch{G}{e r}et\Ch{D}{urn}s or c\Ch{G}{all}s me h\Ch{A}{ome}

\Ch{D/F#}{Her}e in the p\Ch{G}{owe}r of Ch\Ch{A}{ris}t I'll st\Ch{D}{and}!
\end{SBVerse}
\end{song}\begin{song}{In The Secret}{G}
{Andy Park}
{Andy Park}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{In }the secret, in the quiet p\Ch{C}{lac}e

\Ch{Em7}{In }the stillness y\Ch{D}{ou }are th\Ch{C}{ere}

\Ch{G}{In }the secret, in the quiet h\Ch{C}{our} I wait only for you

\Ch{Em7}{'ca}use I want to k\Ch{D}{now} you m\Ch{C}{ore}.
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{  I} want to\Ch{D}{ kn}ow you

\Ch{Em}{  I} want to \Ch{C}{hea}r your voice

\Ch{G}{  I} want to\Ch{D}{ kn}ow you\Ch{C}{ mo}re

\Ch{G}{  I} want to\Ch{D}{ to}uch you

\Ch{Em}{  I} want to \Ch{C}{see} your face

\Ch{G}{  I} want to\Ch{D}{ kn}ow you\Ch{C}{ mo}re
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{I a}m reaching for the highest \Ch{C}{goa}l

\Ch{Em7}{Tha}t I might re\Ch{D}{cei}ve the p\Ch{C}{riz}e

\Ch{G}{Pre}ssing onward, pushing every h\Ch{C}{ind}rance aside out of my way

\Ch{Em7}{I w}ant to know you\Ch{D}{ mo}re    \Ch{C}{   }
\end{SBVerse}
\end{song}\begin{song}{Indescribable}{G}
{Laura Story}
{Laura Story}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Em}{Fro}m the highest of heights to the \Ch{D/F#}{dep}ths of the \Ch{G}{sea}

\Ch{Am}{Cre}ation's rev\Ch{Am7/G}{eal}ing Your majest\Ch{F}{y  }

\Ch{Em}{Fro}m the colors of fall to the \Ch{D/F#}{fra}grance of sp\Ch{G}{rin}g

\Ch{Am}{Eve}ry creature unique in the \Ch{Am7/G}{son}g that it sin\Ch{F}{gs }

\Ch{C2}{All} excl\Ch{D}{aim}ing
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Ind}escribable,\Ch{Dsus}{  u}ncontainable,

\Ch{C2}{You} placed the stars in the sky and You know them by \Ch{Em}{nam}e.

\Ch{Bm7}{You} are amazing \Ch{C2}{  G}od

\Ch{G}{All} powerful,\Ch{Dsus}{  u}ntameable,

\Ch{C2}{Awe}struck we fall to our knees as we humbly proc\Ch{Em}{lai}m

\Ch{Bm7}{You} are amazing \Ch{C2}{  G}od
\end{SBVerse}
\begin{SBVerse}
\Ch{Em}{Who} has told every lightning bolt \Ch{D/F#}{whe}re it should \Ch{G}{go }

\Ch{Am}{Or }seen heavenly storehouses \Ch{Am7/G}{lad}en with sn\Ch{F}{ow }

\Ch{Em}{Who} imagined the sun and gives s\Ch{D/F#}{our}ce to its l\Ch{G}{igh}t  \Ch{G2}{   }

\Ch{Am}{Yet} conceals it to bring us the \Ch{Am7/G}{coo}lness of n\Ch{F}{igh}t

\Ch{C2}{Non}e can f\Ch{D}{ath}om
\end{SBVerse}
\begin{SBVerse}
Chorus Tag: [Chris Tomlin style]

\Ch{G}{Inc}omparable,\Ch{Dsus}{  u}nchangeable

\Ch{C2}{You} see the depths of my heart and You love me the s\Ch{Em}{ame}

\Ch{Bm7}{You} are amazing G\Ch{C2}{od }    \Ch{Em}{   }

\Ch{Bm7}{You} are amazing G\Ch{C2}{od }
\end{SBVerse}
\end{song}\begin{song}{It Is Well With My Soul}{C}
{Philip Paul Bliss}
{Philip Paul Bliss}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
When p\Ch{C}{eac}e, like a r\Ch{Am}{ive}r, att\Ch{F}{end}\Ch{G}{eth} my w\Ch{C}{ay,}

When s\Ch{Am}{orr}ows like s\Ch{F}{ea }billows r\Ch{G}{oll};

Whate\Ch{C}{ver} my l\Ch{F}{ot,} thou hast \Ch{D2}{tau}ght me to \Ch{G}{say},

"It is w\Ch{C}{ell}, it is \Ch{F}{wel}l w\Ch{G}{ith} my s\Ch{C}{oul}."
\end{SBVerse}
\begin{SBVerse}
It is well\Ch{F}{ (I}t is well)

\Ch{G}{Wit}h my \Ch{C}{sou}l (With my soul)

It is w\Ch{F}{ell}, it is w\Ch{G}{ell}, with my \Ch{C}{sou}l.
\end{SBVerse}
\begin{SBVerse}
Though Satan should buffet, though trials should come,

Let this blest assurance control,

That Christ has regarded my helpless estate,

And hath shed his own blood for my soul.
\end{SBVerse}
\begin{SBVerse}
My sin, o, the bliss of this glorious thought!

My sin, not in part but the whole

Is nailed to the cross, and I bear it no more,

Praise the Lord, praise the Lord, O my soul!
\end{SBVerse}
\begin{SBVerse}
And, Lord, haste the day when my faith shall be sight,

The clouds be rolled back as a scroll;

The trump shall resound, and the Lord shall descend,

Even so, it is well with my soul.
\end{SBVerse}
\end{song}\begin{song}{It's Rising Up}{E}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
It's r\Ch{E}{isi}ng up from coast to coast,

from north to south, and \Ch{C#m7}{eas}t to \Ch{B}{wes}t;

the \Ch{E}{cry} of hearts that love your name,

which with one voice we \Ch{C#m7}{wil}l procl\Ch{B}{aim}.   \Ch{E}{   }
\end{SBVerse}
\begin{SBVerse}
The f\Ch{E}{orm}er things have taken place,

can this be the new \Ch{C#m7}{day} of pr\Ch{B}{ais}e?

A h\Ch{E}{eav}'nly song that comes to birth,

and reaches out to \Ch{C#m7}{all} the e\Ch{B}{art}h.
\end{SBVerse}
\begin{SBVerse}
Oh, \Ch{F#m7}{let} the cry to \Ch{G#m7}{nat}ions ring,

that \Ch{A}{all} may come and \Ch{B}{all} may sing:
\end{SBVerse}
\begin{SBVerse}
"\Ch{E}{Hol}y \Ch{A}{is }the \Ch{E}{Lor}d."

"\Ch{C#m7}{Hol}y \Ch{A}{is }the \Ch{B}{Lor}d."
\end{SBVerse}
\begin{SBVerse}
And \Ch{E}{we }have heard the Lion's roar,

that speaks of heaven's \Ch{C#m7}{lov}e and p\Ch{B}{owe}r.

Is t\Ch{E}{his} the time, is this the call

that ushers in Your \Ch{C#m7}{kin}gdom r\Ch{B}{ule}?
\end{SBVerse}
\begin{SBVerse}
Oh, \Ch{F#m7}{let} the cry to \Ch{G#m7}{nat}ions ring,

that \Ch{A}{all} may come and \Ch{B}{all} may sing:
\end{SBVerse}
\begin{SBVerse}
"\Ch{E}{Jes}us \Ch{A}{is }al\Ch{E}{ive}!"

"\Ch{C#m7}{Jes}us \Ch{A}{is }al\Ch{B}{ive}!"
\end{SBVerse}
\end{song}\begin{song}{Jesus Draw Me Close}{C}
{Rick Founds}
{Rick Founds}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Je\Ch{C}{sus} dr\Ch{G}{aw }me c\Ch{Am}{los}e,

Clo\Ch{F}{ser} Lo\Ch{C}{rd }to \Ch{G}{You}

L\Ch{C}{et }the w\Ch{G}{orl}d ar\Ch{Am}{oun}d me f\Ch{F}{ade} a\Ch{G}{way}

Je\Ch{C}{sus} dr\Ch{G}{aw }me cl\Ch{Am}{ose}

Clo\Ch{F}{ser} L\Ch{C}{ord} to Y\Ch{G}{ou }

For \Ch{F}{I d}esi\Ch{G}{re }to w\Ch{Am}{ors}hip a\Ch{G}{nd }ob\Ch{F}{ey } \Ch{C}{   }
\end{SBVerse}
\end{song}\begin{song}{Jesus Keep Me Near The Cross}{G}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G	}{You} led me t\Ch{D/F#}{o t}he cross

\Ch{Em		}{And} I sa\Ch{C		}{w t}he\Ch{G}{ fa}ce of mercy in that place of love

\Ch{D/F#}{You} opened up my eyes

\Ch{Em}{To }believe Your sweet salvation

\Ch{C}{Whe}re I'd been so blind

\Ch{Am	}{Now} that\Ch{C}{ I'}m living in \Ch{G}{You}r all for\Ch{D/F#}{giv}ing \Ch{Am}{lov}e

\Ch{C}{My }every \Ch{D}{roa}d leads \Ch{G}{to }the cross
\end{SBVerse}
\begin{SBVerse}
\Ch{D/F#}{Jes}us, keep me nea\Ch{Em}{r t}he \Ch{C}{cro}ss

\Ch{G}{I w}on't forget the love You've shown

\Ch{D/F#}{Sav}ior, teach me \Ch{Em}{of }the \Ch{C}{cro}ss

\Ch{Am7}{I w}on't forget the love

\Ch{C	}{I w}on\Ch{D}{'t }forget the\Ch{G}{ lo}ve You've shown
\end{SBVerse}
\begin{SBVerse}
And there's an empty tomb

That tells me of Your resurrection and my life in You

The stone lies rolled away

Nothing but those folded grave clothes

Where Your body lay

Now that I'm living as a risen child of God

My every road leads to the cross
\end{SBVerse}
\end{song}\begin{song}{Jesus Lover Of My Soul}{G}
{Daniel Grul}
{Daniel Grul}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Jes}us, \Ch{D}{lov}er of my \Ch{B}{sou}l

\Ch{Em}{Jes}us, I will \Ch{C}{nev}er let you go

\Ch{G}{You}'ve taken me \Ch{D}{fro}m the miry \Ch{B}{cla}y

\Ch{Em}{Set} my feet upon the \Ch{C}{roc}k and now I know

\Ch{G}{I l}ove you, \Ch{D}{I n\Ch{B}{}ee}d you, \Ch{Em}{tho}ugh my world may fall

I'll \Ch{C}{nev}er let you go

\Ch{G}{My }savior, \Ch{D}{my }closest \Ch{B}{fri}end\Ch{Em}{   }

I will worship you \Ch{C}{unt}il the very end.
\end{SBVerse}
\end{song}\begin{song}{Jesus Paid It All}{G}
{Kristian Stanfill}
{Kristian Stanfill}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{I h}ear the Savior say, "Thy \Ch{D}{str}ength indeed is \Ch{G}{sma}ll;

Child of \Ch{Em7}{wea}kness, watch and \Ch{C}{pra}y,Find in \Ch{G}{Me }thine a\Ch{D}{ll }in a\Ch{G}{ll.}"
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Jes}us paid it \Ch{Em7}{all}, A\Ch{G}{ll }to Him I o\Ch{D}{we;}

\Ch{G}{Sin} had \Ch{G/B}{lef}t a \Ch{C2}{cri}mson stain, He \Ch{G}{was}hed it w\Ch{D}{hit}e as s\Ch{G}{now}.
\end{SBVerse}
\begin{SBVerse}
Lord, \Ch{G}{now} indeed I find Thy \Ch{D}{pow}'r, and Thine \Ch{G}{alo}ne,

Can \Ch{Em7}{cha}nge the leper's sp\Ch{C}{ots} And m\Ch{G}{elt} the h\Ch{D}{ear}t of s\Ch{G}{ton}e.
\end{SBVerse}
\begin{SBVerse}
And w\Ch{G}{hen} before the throne, I st\Ch{D}{and} in Him comp\Ch{G}{let}e,

Jesus \Ch{Em7}{die}s my soul to s\Ch{C}{ave} my l\Ch{G}{ips} shall s\Ch{D}{til}l re\Ch{G}{pea}t
\end{SBVerse}
\begin{SBVerse}
O \Ch{G}{pra}ise the One who \Ch{C}{pai}d my debt

And r\Ch{G}{ais}ed this life up \Ch{C}{fro}m the dead

O \Ch{G}{pra}ise the One who \Ch{C}{pai}d my debt

And r\Ch{G}{ais}ed this life up \Ch{C}{fro}m the dead
\end{SBVerse}
\begin{SBVerse}
O \Ch{G}{pra}ise the One \Ch{G/B}{who} p\Ch{C}{aid} my debt

\Ch{G/B}{And}  \Ch{Am7}{rai}sed this life  \Ch{G/B}{up }  f\Ch{C}{rom} the dead

O \Ch{G}{pra}ise the One \Ch{G/B}{who} p\Ch{C}{aid} my debt

\Ch{G/B}{And}  \Ch{Am7}{rai}sed this life  \Ch{G/B}{up }  f\Ch{C}{rom} the dead
\end{SBVerse}
\end{song}\begin{song}{Jesus, All For Jesus}{D}
{Robin Mark}
{Robin Mark}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Jes}us, all for \Ch{G}{Jes}\Ch{D}{us }

All I \Ch{A}{am }and have

And ever hope to \Ch{G}{be \Ch{A}{}  }

\Ch{D}{Jes}us, all for \Ch{G}{Jes}\Ch{D}{us }

All I \Ch{A}{am }and have

And ever hope to \Ch{D}{be }\Ch{D4}{   }\Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{All} of my

Ambitions, \Ch{G}{hop}es, and \Ch{D}{pla}ns

I sur\Ch{A}{ren}der these

Into your \Ch{G}{han}\Ch{A}{ds }

\Ch{D}{All} of my

Ambitions, \Ch{G}{hop}es, and \Ch{D}{pla}ns

I sur\Ch{A}{ren}der these

\Ch{	}{Int}\Ch{D}{o y}our\Ch{D4}{ ha}\Ch{D}{nds}
\end{SBVerse}
\begin{SBVerse}
For it's \Ch{G}{onl}y in

Your will that \Ch{D}{I a}m free

\Ch{	}{For\Ch{G}{} i}t's only in

Your will that \Ch{D}{I a}m \Ch{A}{fre}e
\end{SBVerse}
\end{song}\begin{song}{Joy}{D}
{Jon Ellis}
{Jon Ellis}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
I'll \Ch{D}{lov}e You Lord

I'll \Ch{D}{wor}ship You

I'll \Ch{D}{lov}e You Lord, alwa\Ch{A}{ys }
\end{SBVerse}
\begin{SBVerse}
So \Ch{D}{Tha}nkful, Lord

You \Ch{D}{sav}ed my life

You \Ch{D}{sav}ed my life, to\Ch{A}{day}
\end{SBVerse}
\begin{SBVerse}
Let me be a \Ch{G}{shi}ning light for \Ch{D}{You}

Let me be a \Ch{G}{joy} to You alw\Ch{D}{ays}

Let me be a \Ch{G}{shi}ning light for \Ch{D}{You}

Let me be a \Ch{G}{joy} to \Ch{C2}{You} alway\Ch{D}{s  }

Let me be a \Ch{G}{joy} to \Ch{C2}{You} alway\Ch{D}{s  }
\end{SBVerse}
\end{song}\begin{song}{Just a Closer Walk With Thee}{C}
{William J. Floyd}
{William J. Floyd}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{I a}m weak but Thou art \Ch{G7}{str}ong;  Jesus, keep me from all \Ch{C}{wro}ng;

\Ch{C}{I'l}l be satisfied as \Ch{F}{lon}g  as I \Ch{C}{wal}k, let me \Ch{G7}{wal}k close to \Ch{C}{The}e.
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Jus}t a closer walk with \Ch{G7}{The}e,  grant it, Jesus, is my \Ch{C}{ple}a;

\Ch{C}{Dai}ly walking close to \Ch{F}{The}e,  let it \Ch{C}{be,} dear \Ch{G7}{Lor}d, let it \Ch{C}{be.}
\end{SBVerse}
\begin{SBVerse}
Through this world of toil and snares,  if I falter, Lord, who cares?

Who with me my burden shares?  None but thee, dear Lord, none but Thee.
\end{SBVerse}
\begin{SBVerse}
When my feeble life is o'er,  time for me will be no more;

Guide me gently, safely o'er, to Thy kingdom shore, to Thy shore.
\end{SBVerse}
\end{song}\begin{song}{Just as the Deer}{E}
{Mark Spencer}
{Mark Spencer}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Jus}t as the dee\Ch{B/D#}{r p}ants for the water

\Ch{D}{My }soul thirsts for \Ch{D/C#}{You}

\Ch{E}{Whe}n can I g\Ch{B/D#}{o a}nd meet with God

\Ch{D}{My }tears have been my \Ch{D/C#}{foo}d
\end{SBVerse}
\begin{SBVerse}
\Ch{F#m}{Men} say to \Ch{A}{me }all day l\Ch{B}{ong},

\Ch{F#m}{"Wh}ere is your G\Ch{A}{od?}" But these things I r\Ch{B}{eca}ll
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{Dur}ing the day the Lord commands His lo\Ch{B}{ve }aro\Ch{C#m}{und} me

\Ch{A}{Eve}n during the night His s\Ch{B}{ong} stays with\Ch{C#m}{ me}

\Ch{A}{My }prayers they have risen \Ch{B}{up }to the God of\Ch{C#m}{ my} life

\Ch{A}{Why} so d\Ch{B}{own}cast \Ch{C#m}{sou}l?

\Ch{A}{Put} your h\Ch{B}{ope} in \Ch{C#m}{God}   \Ch{D}{   }
\end{SBVerse}
\end{song}\begin{song}{Justice and Mercy}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{You}'ve \Ch{D/B}{put}   a \Ch{G}{new} song \Ch{A}{in }my \Ch{D}{mou}th\Ch{G}{   }\Ch{A}{   }

\Ch{D}{It }\Ch{D/B}{is }a h\Ch{G}{ymn} of \Ch{A}{pra}ise to \Ch{D}{You}\Ch{G}{   }\Ch{A}{   }

\Ch{D}{Jus}-\Ch{D/B}{tic}e and \Ch{G}{mer}cy \Ch{A}{are} its \Ch{D}{the}me\Ch{G}{   }\Ch{A}{   }

\Ch{Bm}{And} \Ch{A/C#}{ I } will \Ch{G}{liv}e it \Ch{A}{bac}k to \Ch{D}{You}\Ch{G}{   }\Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{Bm}{ Th}e kind of \Ch{Fm}{fas}t You've chosen, \Ch{G}{Lor}d  It must reach out

\Ch{Bm}{ To} broken \Ch{Fm}{liv}es and to the \Ch{G}{poo}r       So change me, Lord
\end{SBVerse}
\begin{SBVerse}
I \Ch{Fm}{kno}w You are the \Ch{G}{orp}han's hope        

I know You\Ch{Fm}{ ar}e the widow's \Ch{G}{son}g 

O \Ch{Bm}{Lor}d, You're \Ch{Fm}{sho}wing me what's on You're \Ch{Em}{hea}rt  \Ch{A}{( C}horus )
\end{SBVerse}
\begin{SBVerse}
\Ch{Bm}{ Lo}rd, I wont \Ch{Fm}{bri}ng an empty \Ch{G}{son}g  It's meaningless

\Ch{Bm}{ Wi}thout com\Ch{Fm}{pas}sion in my \Ch{G}{lif}e     And holiness 
\end{SBVerse}
\begin{SBVerse}
You're \Ch{Fm}{Fat}her were no \Ch{G}{fat}her lives       

And \Ch{Fm}{to }the lonely You're a \Ch{G}{fri}end

O \Ch{Bm}{Lor}d, You're s\Ch{Fm}{how}ing me what's on You're \Ch{Em}{hea}rt  \Ch{A}{( C}horus ) 
\end{SBVerse}
\begin{SBVerse}
I \Ch{Fm}{kno}w You are the \Ch{G}{orp}han's hope        

I \Ch{Fm}{kno}w You are the \Ch{G}{wid}ow's song 

You're \Ch{Fm}{Fat}her were no \Ch{G}{fat}her lives      

And \Ch{Fm}{to }the lonely You're a \Ch{G}{fri}end

O \Ch{Bm}{Lor}d, You're \Ch{Fm}{sho}wing me what's on You're \Ch{Em}{hea}rt  \Ch{A}{( C}horus ) 
\end{SBVerse}
\end{song}\begin{song}{Knowing You (All I Once Held Dear)}{C}
{Graham Kendrick}
{Graham Kendrick}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{All}\Ch{G/B}{ I }   \Ch{Am}{onc}e \Ch{F}{hel}d \Ch{C}{dea}r, built my \Ch{F}{lif}e \Ch{G}{upo}\Ch{C}{n, }

All \Ch{G/B}{thi}s  \Ch{Am}{wor}ld \Ch{F}{rev}\Ch{C}{ere}s and w\Ch{Am}{ars} to o\Ch{G}{wn;}

\Ch{C}{All} I \Ch{F}{onc}e \Ch{G}{tho}ught \Ch{C}{gai}n\Ch{C/E}{ I } have \Ch{F}{cou}n\Ch{G}{ted} \Ch{Am}{los}\Ch{/}{s, \Ch{C}{}  }

Spent \Ch{G/B}{and}   \Ch{Am}{wor}th\Ch{F}{les}s \Ch{C}{now} com\Ch{Am}{par}ed to \Ch{Gsus4}{thi}s.
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Kno}wing \Ch{F6}{You}, \Ch{C}{Jes}us,\Ch{F/G}{   } kno\Ch{G}{win}g \Ch{C}{You}

There \Ch{Am}{is }no \Ch{Em/G}{gre}ater \Ch{F}{thi}ng.

You're my \Ch{C/E}{all}, You're the \Ch{F/A}{bes}t,

You're my \Ch{C/G}{joy}, my righteous\Ch{F/A}{nes}s,

And I \Ch{C/E}{lov}e You \Ch{F/A}{Lor}d.  \Ch{C/G}{   }   \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
Now my heart's desire is to know You more,

To be found in You and know as Yours,

To possess by faith what I could not earn

All surpassing gift of righteousness
\end{SBVerse}
\begin{SBVerse}
Oh to know the power of Your risen life,

And to know You in Your sufferings;

To become like You in Your death, my Lord,

So with You to live and never die.
\end{SBVerse}
\end{song}\begin{song}{Lamb Of God}{A}
{Twila Paris}
{Twila Paris}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Your only \Ch{A}{Son}, no \Ch{D}{sin} to hi\Ch{A}{de }

But you have \Ch{F#m}{sen}t him \Ch{D}{fro}m your sid\Ch{E}{e  }

To walk u\Ch{D}{pon} this guil\Ch{A}{ty }\Ch{F#m}{sod}

And to be\Ch{A}{com}e the La\Ch{E}{mb }of \Ch{A}{God}
\end{SBVerse}
\begin{SBVerse}
Your gift of \Ch{A}{lov}e they \Ch{D}{cru}ci\Ch{A}{fie}d

They laughed and \Ch{F#m}{sco}rned Him \Ch{D}{as }He \Ch{E}{die}d

The humble \Ch{D}{Kin}g, they na\Ch{A}{med} a \Ch{F#m}{fra}ud

And sacrif\Ch{A}{ice}d the \Ch{E}{Lam}b of \Ch{A}{God}
\end{SBVerse}
\begin{SBVerse}
O Lamb of \Ch{F#m}{God}, sweet \Ch{E}{Lam}b of \Ch{A}{God}

I love the \Ch{F#m}{hol}y \Ch{D}{Lam}b of \Ch{E}{God}

O wash me \Ch{D}{in }His \Ch{C#m}{pre}cious \Ch{F#m}{blo}od

My Jesus \Ch{A}{Chr}ist, the \Ch{E}{Lam}b of \Ch{A}{God}
\end{SBVerse}
\begin{SBVerse}
I was so \Ch{A}{los}t I sho\Ch{D}{uld} have \Ch{A}{die}d

But you have \Ch{F#m}{bro}ught me \Ch{D}{to }your sid\Ch{E}{e  }

To be led \Ch{D}{by }your sta\Ch{A}{ff }and \Ch{F#m}{rod}

And to be \Ch{A}{cal}led a \Ch{E}{lam}b of \Ch{A}{God}
\end{SBVerse}
\end{song}\begin{song}{Lamb of God}{G}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Lam}b of God, sweet Lamb of God                    \Ch{C}{   }\Ch{Am}{   }

Light of the world, \Ch{D}{Hol}y One\Ch{C}{   }       \Ch{G}{   }

The name of  Jesus, swee\Ch{G}{t n}ame of Jesus                      \Ch{C}{   }   \Ch{Am}{   }

Rock of  Salvati\Ch{D}{on,} Me\Ch{C}{ssi}ah is come           \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
And we  lift\Ch{G}{ ou}r praise 

With humble hearts w\Ch{Am}{e r}aise 

A song of hope a\Ch{F}{nd }thanks                   \Ch{C}{   }

We rejoice i\Ch{G}{n Y}our grace 
\end{SBVerse}
\end{song}\begin{song}{Let Everything That Has Breath}{E}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{ Le}t everything that,\Ch{E/D#}{ ev}erything that,

\Ch{C#m7}{ Ev}erything that \Ch{A}{has} breath \Ch{B}{pra}ise the Lord.

\Ch{E}{ Le}t everything that,\Ch{E/D#}{ ev}erything that,

\Ch{C#m7}{ Ev}erything that \Ch{A}{has} breath \Ch{B}{pra}ise the Lord.\Ch{F#m7}{   }    \Ch{B}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{ Pr}aise You in the morning,

\Ch{E/D#}{ Pr}aise You in the evening,

\Ch{C#m7}{ Pr}aise You when I'm young and when I'm o\Ch{A2}{ld.}

\Ch{E}{ Pr}aise You when I'm laughing,

\Ch{E/D#}{ Pr}aise You when I'm grieving,

\Ch{C#m7}{ Pr}aise You every season of the so\Ch{A2}{ul.}

 If\Ch{F#m7}{ we} could see how \Ch{E/G#}{muc}h You're worth,

 Your \Ch{F#m7}{pow}er, Your might, Your \Ch{E/G#}{end}less love,

 Then \Ch{F#m7}{sur}ely we would \Ch{E/G#}{nev}er cease to pr\Ch{A}{ais}e.
\end{SBVerse}
\begin{SBVerse}
 Praise You in the heavens, joining with the angels,

 Praising You forever and a day.

 Praise You on the earth now, joining with creation,

 Calling all the nations to Your praise.

 If they could see how much You're worth,

 Your power, your might, your endless love,

 Then surely they would never cease to praise.
\end{SBVerse}
\end{song}\begin{song}{Let It Rise}{E}
{Holland Davis}
{Holland Davis}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Let} the glory of the Lord, rise among us,

\Ch{E}{let} the glory of the Lord, rise among us.

Let the p\Ch{A}{rai}ses of the King rise among us,

Let it \Ch{E}{ris}e.
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{Let} the songs of the Lord, rise among us,

\Ch{E}{let} the songs of the Lord, rise among us.

Let the j\Ch{A}{oy }of the King, rise among us,

Let it \Ch{E}{ris}e.
\end{SBVerse}
\begin{SBVerse}
\Ch{B}{Oh }- \Ch{E}{oh }- \Ch{A}{oh,} let it r\Ch{E}{ise}.

\Ch{B}{Oh }- \Ch{E}{oh }- \Ch{A}{oh,} let it r\Ch{E}{ise}.
\end{SBVerse}
\end{song}\begin{song}{Light of the World}{G}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
O Jesus\Ch{D}{ so}n of \Ch{Em}{God} , so \Ch{D/F}{ful}l of grace and \Ch{G}{tru}th

The \Ch{D}{Fat}her's saving \Ch{Em}{Wor}d, so \Ch{D}{won}derful are \Ch{G}{you}

\Ch{Am7}{   }  The Angels \Ch{G/B}{lon}ged to see\Ch{Cadd9}{, a}nd prophets \Ch{Dsus2}{sea}rched to find

\Ch{Am7}{   }  The glory \Ch{G/B}{we }have seen reveal\Ch{Cadd9}{ed }
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{You} shone\Ch{D}{ up}on the \Ch{Em}{ear}th, but \Ch{D/F}{who} will unders\Ch{G}{tan}d?

You came \Ch{D}{unt}o Your \Ch{Em}{own}, but \Ch{D/F}{who} will recog\Ch{G}{nis}e?

\Ch{Am7}{   }Your birth was \Ch{G/B}{pro}phesied\Ch{Cadd9}{, f}or You were \Ch{D}{the} Messiah

\Ch{Am7}{   }Who came and \Ch{G/B}{wal}ked upon the \Ch{Cadd9}{Ear}th

\Ch{Am7}{   }Your glory \Ch{G/B}{we }have see\Ch{Cadd9}{n, }the one and \Ch{D}{onl}y King

\Ch{Am7}{   }And now You're \Ch{G/B}{liv}ing in our \Ch{Cadd9}{hea}rts
\end{SBVerse}
\begin{SBVerse}
\Ch{C/G}{Lig}ht of the world, light of the world

Li\Ch{			}{ght} of\Ch{	}{ th}e wo\Ch{G}{rld}, You shine upon us
\end{SBVerse}
\begin{SBVerse}
In You all things were made and nothing without You

In heaven and on earth all things are held in You

And yet You became flesh, living as one of us 

Under the shadow of the cross

Where, through the blood you shed, You have made peace again

Peace for a world that God so loves
\end{SBVerse}
\begin{SBVerse}
\Ch{Am7}{   }And yet You \Ch{G/B}{bec}ame flesh, \Ch{Cadd9}{liv}ing as \Ch{D}{one} of us 

\Ch{Am7}{   } Under the \Ch{G/B}{sha}dow of the \Ch{Cadd9}{cro}ss

\Ch{Am7}{  W}here, through the \Ch{G/B}{blo}od you shed\Ch{Cadd9}{, Y}ou have made \Ch{D}{pea}ce again

\Ch{Am7}{   } Peace for a \Ch{G/B}{wor}ld that God so \Ch{Cadd9}{lov}es
\end{SBVerse}
\end{song}\begin{song}{Lord I Lift Your Name on High}{G}
{Rick Founds}
{Rick Founds}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Lor}d, I l\Ch{C}{ift} your name on h\Ch{D}{igh}    \Ch{C}{   }

\Ch{G}{Lor}d, I l\Ch{C}{ove} to sing your pr\Ch{D}{ais}es   \Ch{C}{   }

\Ch{G}{I'm} so gl\Ch{C}{ad }you're in my l\Ch{D}{ife}   \Ch{C}{   }

\Ch{G}{I'm} so gl\Ch{C}{ad }you came to s\Ch{D}{ave} us   \Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{You} came from h\Ch{C}{eav}en to e\Ch{D}{art}h

        to sh\Ch{C}{ow }the w\Ch{G}{ay }

From the e\Ch{C}{art}h to the cr\Ch{D}{oss}

        by d\Ch{C}{ebt} to p\Ch{G}{ay }

From the c\Ch{C}{ros}s to the g\Ch{D}{rav}e

From the g\Ch{Em}{rav}e to the \Ch{Am}{sky}

Lord, I l\Ch{D}{ift} your name on h\Ch{G}{igh}
\end{SBVerse}
\end{song}\begin{song}{Lord Most High}{D}
{Don Harris}
{Don Harris}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
From the\Ch{D}{ en}ds of the earth  (From the\Ch{Dsus4}{ en}ds of the\Ch{D}{ ea}rth)

From the \Ch{Asus2}{dep}ths of the sea  (From the \Ch{A}{dep}ths of the sea)

From the \Ch{Bm}{hei}ghts of the heavens  (From the heights of the heavens)

Your \Ch{G}{nam}e \Ch{D/G}{be }pr\Ch{G}{ais}ed
\end{SBVerse}
\begin{SBVerse}
From the \Ch{D}{hea}rts of the weak  (From the \Ch{Dsus2}{hea}rts of the \Ch{D}{wea}k)

From the \Ch{Asus2}{sho}uts of the strong  (From the \Ch{A}{sho}uts of the strong)

From the \Ch{Bm}{lip}s of all people  (From the lips of all people)

This \Ch{G}{son}g \Ch{D/G}{we }ra\Ch{G}{ise}, \Ch{A}{Lor}d
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Thr}oughout the \Ch{G}{end}less \Ch{A}{age}s \Ch{A7sus4}{   }

\Ch{D}{You} will be \Ch{G}{cro}wned with \Ch{A}{pra}\Ch{A7sus4}{ise}s,  L\Ch{Bm}{ord} \Ch{G}{Mos}t \Ch{Asus4}{Hig}h   \Ch{A}{   }

\Ch{D}{Exa}lted in \Ch{G}{eve}ry \Ch{A}{nat}ion \Ch{A7sus4}{   }

\Ch{D}{Sov}ereign of \Ch{G}{all} cre\Ch{A}{ati}on \Ch{A7sus4}{   }

\Ch{Bm}{Lor}d \Ch{G}{Mos}t \Ch{Asus4}{Hig}h, \Ch{A}{Be }magni\Ch{G}{fie}d \Ch{D}{   }\Ch{G}{   }
\end{SBVerse}
\end{song}\begin{song}{Lord Reign In Me}{C}
{Brenton Brown}
{Brenton Brown}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{ Ov}er \Ch{G}{all} the e\Ch{F}{art}h, You r\Ch{G}{eig}n on high

\Ch{C}{ Ev}ery m\Ch{G}{oun}tain s\Ch{F}{tre}am, every s\Ch{G}{uns}et sky

\Ch{Am7}{ Bu}t my \Ch{G}{one} req\Ch{F}{ues}t, Lord, my o\Ch{G}{nly} aim\Ch{Dm7}{   }

 Is that You'd r\Ch{F}{eig}n in \Ch{G}{me }\Ch{F/G}{aga}i\Ch{C}{n  }
\end{SBVerse}
\begin{SBVerse}
 Lord, r\Ch{G}{eig}n in \Ch{F}{me,} reign \Ch{G}{in }Your p\Ch{C}{owe}r

 Over a\Ch{G}{ll }my dre\Ch{F}{ams}, in my d\Ch{G}{ark}est h\Ch{Am}{our}

 You a\Ch{G}{re }the L\Ch{F}{ord} of \Ch{G}{all} I \Ch{Dm7}{am }

 So won't You r\Ch{F}{eig}n in \Ch{G}{me }aga\Ch{C}{in }\Ch{G}{   }\Ch{F}{   }\Ch{G}{   }\Ch{Am7}{   }  \Ch{G}{   }\Ch{F}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{ Ov}er e\Ch{G}{ver}y th\Ch{F}{oug}ht, over e\Ch{G}{ver}y word

\Ch{C}{ Ma}y my l\Ch{G}{ife} refl\Ch{F}{ect} the beauty \Ch{G}{of }my Lord

\Ch{Am7}{ 'C}ause You mean m\Ch{G}{ore} to \Ch{F}{me }than any e\Ch{G}{art}hly th\Ch{Dm7}{ing}

 So won't You r\Ch{F}{eig}n in \Ch{G}{me }\Ch{F/G}{aga}in \Ch{C}{   }
\end{SBVerse}
\end{song}\begin{song}{Lord You Have My Heart}{D}
{Martin Smith}
{Martin Smith}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Bm}{Lor}d you have my hea\Ch{G}{rt }

And I will search \Ch{D}{for} \Ch{A}{you}rs

\Ch{Bm}{Jes}us take my life\Ch{G}{ an}d \Ch{A}{lea}d me \Ch{D}{on }   \Ch{Dsus}{   }      \Ch{D}{   }   \Ch{Dsus}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{Bm}{Lor}d you have my hea\Ch{G}{rt }

And I will search \Ch{D}{for} \Ch{A}{you}rs

\Ch{Bm}{Let} me be to \Ch{G}{you} a \Ch{A}{sac}rific\Ch{D}{e  }   \Ch{Dsus}{   }      \Ch{D}{   }   \Ch{Dsus}{   }
\end{SBVerse}
\begin{SBVerse}
(men)   \Ch{D}{And} I wi\Ch{Dsus}{ll }   \Ch{G}{pra}ise y\Ch{D}{ou } \Ch{Asus}{ Lo}rd

(ladies)        \Ch{A}{I w}ill praise you Lord

(men)   \Ch{D}{And} I wi\Ch{Dsus}{ll }   \Ch{G}{sin}g of love \Ch{D}{com}e \Ch{Asus}{dow}n

(ladies)        I\Ch{A}{ wi}ll sing of love come down

(men)   And \Ch{D}{as }\Ch{Dsus}{you}    \Ch{G}{sho}w \Ch{D}{you}r \Ch{Asus}{fac}e

(ladies)        Show your fa\Ch{A}{ce }

(all)   \Ch{A}{We'}ll \Ch{G}{see} \Ch{D}{you}r \Ch{Asus}{glo}ry   \Ch{D}{her}e
\end{SBVerse}
\end{song}\begin{song}{Lord, Let Your Glory Fall}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Lor}d let your \Ch{Dmaj7}{glo}ry  \Ch{G}{fal}l,

\Ch{D/F#}{As }on that ancient \Ch{G}{day}.

\Ch{Bm}{Son}gs of en\Ch{D/F#}{dur}ing \Ch{G}{lov}e,

\Ch{Em}{And} then your \Ch{G}{glo}ry \Ch{D}{cam}e.

\Ch{D}{And} as a sign \Ch{Dmaj7}{to }    \Ch{G}{you},

\Ch{D/F#}{Tha}t we would love \Ch{G}{the} same,

\Ch{Bm}{Our} hearts \Ch{D/F#}{wil}l sin\Ch{G}{g t}hat song,

\Ch{Em}{God}, let your \Ch{G}{glo}ry \Ch{D}{com}e.
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{You} are good, \Ch{D}{You} are good,

\Ch{G}{And} your love endures.

\Ch{D}{You} are good, \Ch{D}{You} are good,

\Ch{G}{And} your love endures.

\Ch{Bm}{You} are good, \Ch{D/F#}{You} are good,

\Ch{G}{And} your love \Ch{D}{end}ures today.
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Voi}ces in uni\Ch{G}{son},

\Ch{D/F#}{Giv}ing you thanks and \Ch{G}{pra}ise,

\Ch{Bm}{Joi}ned by the \Ch{D/F#}{ins}tru\Ch{G}{men}ts,

\Ch{Em}{And} then your \Ch{G}{glo}ry \Ch{D}{cam}e.

\Ch{D}{You}r presence like a \Ch{G}{clo}ud,

\Ch{D/F#}{Upo}n that ancient \Ch{G}{day},

\Ch{Bm}{The} priests were \Ch{D/F#}{ove}r--\Ch{G}{whe}lmed,

\Ch{Em}{Bec}ause your \Ch{G}{glo}ry \Ch{D}{cam}e.
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{A s}acrifice was \Ch{G}{mad}e,

\Ch{D/F#}{And} then your fire \Ch{G}{cam}e,

\Ch{Bm}{The}y knelt \Ch{D/F#}{upo}n the \Ch{G}{gro}und,

\Ch{Em}{And} with one \Ch{G}{voi}ce they \Ch{D}{pra}ised.
\end{SBVerse}
\end{song}\begin{song}{Majesty}{G}
{Jack Hayford}
{Jack Hayford}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
M\Ch{G}{aje}st\Ch{C}{y, }\Ch{G}{wor}ship His M\Ch{C}{aje}sty\Ch{Am}{,  }

Unto J\Ch{G}{esu}s, \Ch{			}{be }all gl\Ch{D}{ory}, \Ch{D7}{hon}or and praise!

M\Ch{G}{aje}st\Ch{C}{y, }\Ch{G}{kin}gdom auth\Ch{C}{ori}ty\Ch{Am}{, f}lows from His thr\Ch{G}{one},

Unto His o\Ch{D}{wn,} His anthem r\Ch{G}{ais}e\Ch{C}{.  }\Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
So ex\Ch{D}{alt}, lift up on h\Ch{D7}{igh} the name of J\Ch{G}{esu}s\Ch{C}{.  }\Ch{G}{   }

Magni\Ch{D}{fy,} come glori\Ch{D7}{fy }Christ Jesus the K\Ch{G}{ing}\Ch{D7}{.  }

 \Ch{G}{   } M\Ch{C}{aje}sty, worship \Ch{C}{His} Maj\Ch{Am}{est}y,

Jesus who d\Ch{G}{ied}, now glorif\Ch{D}{ied},

King of all k\Ch{(C)}{ing}s. \Ch{G}{   }
\end{SBVerse}
\end{song}\begin{song}{Make Me A Servant}{G}
{Kelly Willard}
{Kelly Willard}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Mak}e me a \Ch{Em7}{ser}vant, \Ch{Am7}{hum}ble and \Ch{D7sus}{mee}k  \Ch{D7}{   }

\Ch{Am7}{Lor}d, let me l\Ch{D7}{ift} up, \Ch{C/G}{tho}se w\Ch{G}{ho }\Ch{C/G}{are} \Ch{G}{wea}k. \Ch{B7}{   }

\Ch{Em}{And} may the \Ch{Em/D}{pra}y'r of my h\Ch{Dm/C#}{ear}t always \Ch{Cm6}{be;}

\Ch{G/B}{Mak}e me a \Ch{Am7}{ser}vant, \Ch{G/B}{mak}e me a se\Ch{C6/9}{rva}nt,

\Ch{G/D}{Mak}e me a \Ch{D7sus}{ser}vant, \Ch{C/G}{tod}ay. \Ch{G}{   }
\end{SBVerse}
\end{song}\begin{song}{Mighty To Save}{G}
{Reuben Morgan}
{Reuben Morgan}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{  E}veryone needs com\Ch{G}{pas}sion  

Love that's never \Ch{Em}{fai}ling  

Let \Ch{D}{mer}cy fall on \Ch{C}{me }  

  Everyone needs f\Ch{G}{org}iveness   

The kindness of a \Ch{Em}{Sav}ior   

The \Ch{D}{hop}e of nations \Ch{C}{   }\Ch{D}{   }\Ch{C}{   }\Ch{D}{   }   
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Sav}ior, He can move the \Ch{D}{mou}ntains  

My God is m\Ch{C}{igh}ty to \Ch{G}{sav}e   

He is \Ch{Em}{mig}hty to \Ch{D}{sav}e   

\Ch{G}{For}ever Author of sal\Ch{D}{vat}ion  

He rose and \Ch{C}{con}quered the \Ch{G}{gra}ve  

Jesus \Ch{Em}{con}quered the \Ch{D}{gra}ve  
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{  S}o take me as You \Ch{G}{fin}d me  

All my fears and \Ch{Em}{fai}lures  

F\Ch{D}{ill} my life ag\Ch{C}{ain}     

I give my life to \Ch{G}{fol}low   

Everything I \Ch{Em}{bel}ieve in  

Now \Ch{D}{I s}urrender \Ch{C}{   }\Ch{D}{   }\Ch{C}{   }\Ch{D}{   }     
\end{SBVerse}
\begin{SBVerse}
S\Ch{C}{hin}e your light and\Ch{G}{  l}et the whole world s\Ch{D}{ee }     

We're sing - \Ch{Em}{ing} \Ch{C}{ fo}r the glory \Ch{G}{of }the risen K\Ch{D}{ing}...  \Ch{Em}{Jes}us
\end{SBVerse}
\end{song}\begin{song}{More of You}{G}
{Steve Merkel}
{Steve Merkel}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Em}{Mor}e \Ch{D/F#}{of }   Y\Ch{G}{ou,} and \Ch{C}{les}s \Ch{G}{of }\Ch{D}{me;}

\Ch{Em}{Lor}d, I p\Ch{D/F#}{ray} that t\Ch{G}{her}e might \Ch{C}{be }

\Ch{Am7}{Mor}e of Y\Ch{G/B}{ou }and \Ch{Cmaj7}{les}s of m\Ch{D7sus}{e. }    \Ch{D}{   }

\Ch{Em}{Mor}e \Ch{D/F#}{of }   Y\Ch{G}{ou,} and \Ch{C}{les}s \Ch{G/B}{of }**\Ch{D}{me;}

\Ch{Em}{Lor}d, I p\Ch{D/F#}{ray} that t\Ch{G}{her}e might \Ch{C}{be }

\Ch{Am7}{Mor}e of Y\Ch{G/B}{ou }and l\Ch{Cmaj7}{ess} of m\Ch{D7sus}{e. }    \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
Like a \Ch{Em}{gra}in of \Ch{D/F#}{whe}at that f\Ch{G}{all}s to the earth,

\Ch{Am7}{And} dies to \Ch{G2/B}{liv}e  a\Ch{C2}{new};

\Ch{Em}{All} my p\Ch{D/F#}{lan}s and eart\Ch{G}{hly} desires,

I \Ch{Am7}{lay} them d\Ch{G/B}{own} to fo\Ch{Cmj7}{llo}w Y\Ch{D7sus}{ou.}    \Ch{D}{   }
\end{SBVerse}
\end{song}\begin{song}{More Precious Than Silver}{D}
{Lynn DeShazo}
{Lynn DeShazo}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Lor}d, you \Ch{A}{are} more \Ch{G}{pre}cious than \Ch{D}{sil}ver.

Lord, you \Ch{A}{are} more \Ch{Em7}{cos}tly than \Ch{A}{gol}d.

\Ch{D}{Lor}d, you \Ch{A}{are} more \Ch{G}{bea}utiful than \Ch{D}{dia}monds, and

\Ch{G}{not}hing \Ch{D}{I d}es\Ch{Em}{ire} comp\Ch{G}{are}s with y\Ch{D}{ou.}
\end{SBVerse}
\end{song}\begin{song}{More Than a Friend}{G}
{Jeremy Riddle}
{Jeremy Riddle}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Gsus}{In }the q\Ch{C2}{uie}t of my \Ch{G}{sou}l

In the \Ch{C2}{sti}llness I \Ch{G}{hea}r your\Ch{D/F#}{ vo}ice ca\Ch{C2}{ll }

\Ch{Am7}{And} I am overw\Ch{G/B}{hel}med, \Ch{Am7}{and} I am lost for w\Ch{G/B}{ord}s

To descr\Ch{D}{ibe} \Ch{G}{you}
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Jes}us you're \Ch{D/F#}{mor}e than \Ch{Em}{a f}riend

Jesus you're more than m\Ch{C2}{y h}eart could \Ch{Dsus}{ ev} - \Ch{D}{er }\Ch{G}{exp}ress

Your l\Ch{G}{ove} and your \Ch{D/F#}{gra}ce never fa\Ch{Em7}{il }me

Your merciful touch alway\Ch{C2}{s h}eals me

You bring \Ch{Dsus}{ jo}y  \Ch{D}{to }my \Ch{C2}{sou}l
\end{SBVerse}
\begin{SBVerse}
My heart longs to \Ch{C2}{wor}ship, you m\Ch{G}{y K}ing

And I long to brin\Ch{C2}{g y}ou a\Ch{G}{ pl}easing\Ch{D/F#}{ of}ferin\Ch{C2}{g  }

\Ch{Am7}{And} I am overw\Ch{G/B}{hel}med, \Ch{Am7}{and} I am lost for \Ch{G/B}{wor}ds

To desc\Ch{D}{rib}e\Ch{G2}{ yo}u
\end{SBVerse}
\end{song}\begin{song}{My God Reigns}{E}
{Darrell Evans}
{Darrell Evans}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{The}re's nowhere else that I'\Ch{A}{d r}athe\Ch{E}{r b}e			

\Ch{E}{Tha}n dancing with You as Yo\Ch{A}{u s}ing ove\Ch{B}{r m}e

\Ch{E}{The}re's nothing else that I'\Ch{A}{d r}athe\Ch{E}{r d}o

L\Ch{A}{ord} than to w\Ch{B}{ors}hip You   \Ch{E}{   }
\end{SBVerse}
\begin{SBVerse}
So rej\Ch{E}{oic}e be glad rejoice oh my soul
\end{SBVerse}
\begin{SBVerse}
For the Lord Your God reigns forevermore

I rej\Ch{A}{oic}e, for my God reigns\Ch{E}{   }

So rej\Ch{E}{oic}e be glad Your father and Your friend
\end{SBVerse}
\begin{SBVerse}
Is the Lord Your God whose rule will never end

I rej\Ch{A}{oic}e, for my God r\Ch{E}{eig}ns
\end{SBVerse}
\begin{SBVerse}
My God r\Ch{B}{eig}ns and I \Ch{A}{dan}ce the dance of \Ch{E}{pra}ise

My God r\Ch{B}{eig}ns with a\Ch{A}{ sh}out I will \Ch{E}{pro}claim

My God r\Ch{B}{eig}ns and I \Ch{A}{wor}ship without \Ch{E}{sha}me

My God r\Ch{B}{eig}ns and I will rejoice\Ch{A}{ fo}r my God \Ch{E}{rei}gns
\end{SBVerse}
\end{song}\begin{song}{My Hope Is Built On Nothing Less}{D}
{Edward Mote}
{Edward Mote}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
My h\Ch{D}{ope} is built on n\Ch{A}{oth}ing less,

Than J\Ch{G}{esu}s' blood and r\Ch{D}{igh}te\Ch{A}{ous}n\Ch{D}{ess}.

I d\Ch{D}{are} not trust the sw\Ch{A}{eet}est frame,

But wh\Ch{G}{oll}y lean on J\Ch{D}{esu\Ch{A}{}s'} N\Ch{D}{ame}.
\end{SBVerse}
\begin{SBVerse}
On Chr\Ch{D	}{ist} the\Ch{D/F#}{ so} - lid  roc\Ch{G}{k I} stand,

All \Ch{D}{oth}er ground is \Ch{Em}{sin}king s\Ch{A}{and},

All \Ch{D/F#}{oth}er gr\Ch{G}{oun}d is s\Ch{A}{ink}ing s\Ch{D}{and}.
\end{SBVerse}
\begin{SBVerse}
When darkness seems to hide His face,

I rest on His unchanging grace.

In every high and stormy gale,

My anchor holds within the veil.
\end{SBVerse}
\begin{SBVerse}
His oath, His covenant, His blood,

Support me in the whelming flood.

When all around my soul gives way,

He then is all my hope and stay.
\end{SBVerse}
\begin{SBVerse}
When He shall come with trumpet sound,

Oh may I then in Him be found.

Dressed in His righteousness alone,

Faultless to stand before the throne.
\end{SBVerse}
\end{song}\begin{song}{My Savior My God}{D}
{Aaron Shust}
{Aaron Shust}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{I a}m not skilled to understand 

\Ch{				}{Wha}t God\Ch{G}{ ha}s willed, what God has planned 

I only know at his right ha\Ch{A}{nd }

Stands one who is my sa\Ch{D}{vio}r 
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{I t}ake him at his word and deed 

Christ died to save me this I re\Ch{G}{ad }

And in my heart I find a ne\Ch{A}{ed }

For him to be my s\Ch{D}{avi}or 
\end{SBVerse}
\begin{SBVerse}
T\Ch{	}{hat} he would leave his plac\Ch{G}{e o}n high

A\Ch{		}{nd }c\Ch{A}{ome} for sinful man to die

You count it strange, so once di\Ch{G}{d I} 

Before I knew my savio\Ch{D}{r  }
\end{SBVerse}
\begin{SBVerse}
My sa\Ch{Bm}{vio}r loves, my savior li\Ch{G}{ves} 

My savior's \Ch{D}{alw}ays there for \Ch{A}{me }

My God\Ch{Bm}{ he} was, my God he i\Ch{G}{s  }

My God he'\Ch{D}{s a}lways gonna \Ch{A}{be }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Yes}, living, dying; let me bring 

My strength, my solace from this sp\Ch{G}{rin}g 

That he who lives to be my ki\Ch{A}{ng }

Once died to be my sa\Ch{D}{vio}r
\end{SBVerse}
\end{song}\begin{song}{My Soul Waits For The Lord (Psalm 130)}{G}
{Mark Spencer}
{Mark Spencer}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{My }soul \Ch{D/F#}{wai}ts for the \Ch{Em}{Lor}d

More than the watchman w\Ch{C}{ait}s (4x)
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{If }\Ch{D/F#}{ Yo}u  oh L\Ch{Em}{ord} kept a record of s\Ch{C}{ins}

who then could st\Ch{D}{and}?

\Ch{G}{But} with\Ch{D/F#}{ Yo}u there's forg\Ch{Em}{ive}ness

therefore you are to be f\Ch{C}{ear}ed
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Oh }\Ch{D/F#}{ Is}  - r\Ch{Em}{ael} put your hope

in the Lo\Ch{C}{rd'}s unfailing l\Ch{D}{ove}

\Ch{G}{Wit}h \Ch{D/F#}{ Hi}m  there's red\Ch{Em}{emp}tion,

He Himself will re\Ch{C}{dee}m
\end{SBVerse}
\end{song}\begin{song}{Not Be Shaken}{E}
{Norm Strauss}
{Norm Strauss}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
I will \Ch{E}{dec}lare my choice to the nations.

I will \Ch{C#m}{sho}ut for joy to the congregation.

I will \Ch{A}{wor}ship God, all my \Ch{B}{day}s.

Those who \Ch{E}{lov}e the Lord are satisfied,

Those who \Ch{C#m}{tru}st in Him are justified,

I will \Ch{A}{ser}ve me God, all my \Ch{B}{day}s.
\end{SBVerse}
\begin{SBVerse}
(W): \Ch{E}{Whe}n the \Ch{B}{nat}ions \Ch{A}{cru}mble

(M): The \Ch{B}{wor}d of the Lord will stand,

(W): \Ch{E}{Kin}gs may \Ch{B}{ris}e and \Ch{A}{fal}l,

(M): But His \Ch{B}{lov}e endures forever,

(W): \Ch{E}{Tho}ugh the \Ch{B}{str}ong may \Ch{A}{stu}mble

(M): Ah The \Ch{B}{joy} of the Lord is strength.
\end{SBVerse}
\begin{SBVerse}
To my \Ch{B}{sou}l, \Ch{A}{I w}ill not be \Ch{B}{sha}ken,

\Ch{A}{I w}ill not be \Ch{B}{mov}ed, I will not be \Ch{E}{sha}ken.
\end{SBVerse}
\end{song}\begin{song}{Not To Us}{A}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{The} cross before me the world behind

\Ch{F#m7}{No }turning back raise the banner high

\Ch{Esus}{It'}s not for me\Ch{D2}{ It}'s all for you \Ch{A}{   \Ch{Asus}{}  }

\Ch{A}{Let} the heavens shake and split the sky

\Ch{F#m7}{Let} the people clap their hands and cry

\Ch{Esus}{It'}s not for us\Ch{D2}{, i}t's all for you\Ch{A}{   \Ch{Asus}{}  }  \Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{Not} to us,

but to your n\Ch{G/D}{ame}

\Ch{D}{be }the gl\Ch{G/D}{ory} \Ch{D}{(re}peat)
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{Our} hearts unfold before your throne

\Ch{F#m7}{the} only place for those who know

\Ch{Esus}{It'}s not for us\Ch{D2}{, i}t's all for you\Ch{A}{   \Ch{Asus}{}  }

\Ch{A}{sen}d your holy fire on this offering

\Ch{F#m7}{let} our worship burn for the world to see

\Ch{Esus}{It'}s not for us\Ch{D2}{, i}t's all for you\Ch{A}{   \Ch{Asus}{}  }  \Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
The \Ch{A}{ear}th is shaking, the mountains shouting \Ch{D6}{   }

\Ch{D}{It'}s all for you\Ch{D6}{   }\Ch{D}{   }

The \Ch{F#m7}{wav}es are crashing, the \Ch{Esus}{sun} is raging

\Ch{D}{It'}s all for you

The \Ch{A}{uni}verse spinning and singing \Ch{D6}{   }

\Ch{D}{It'}s all for you\Ch{D6}{   }\Ch{D}{   }

Your \Ch{F#m7}{chi}ldren dancing, d\Ch{Esus}{anc}ing, dancing

\Ch{D}{It'}s all for you, It's all for you \Ch{Asus}{   }  \Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
My \Ch{A}{all} for you\Ch{D6}{  M}y \Ch{D}{all} for you (repeat)
\end{SBVerse}
\end{song}\begin{song}{Nothing But the Blood}{E}
{Robert Lowry}
{Robert Lowry}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Wha}t can wash away my sin? \Ch{C#m7}{Not}hing but the \Ch{A2}{blo}od of \Ch{Bsus}{Je } su\Ch{E}{s  }

\Ch{E}{Wha}t can make me whole again? \Ch{C#m7}{Not}hing but the \Ch{A2}{blo}od of \Ch{Bsus}{Je } su\Ch{E}{s  }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{Oh!} precious is the flow

\Ch{Bsus}{Tha}t makes me white as snow;

\Ch{E}{No }other fount I know,

\Ch{C#m7}{Not}hing but the \Ch{A2}{blo}od of \Ch{Bsus}{Je } su\Ch{E}{s  }
\end{SBVerse}
\begin{SBVerse}
For my pardon this I see, nothing but the blood of Jesus;

For my cleansing this my plea, nothing but the blood of Jesus.
\end{SBVerse}
\begin{SBVerse}
This is all my hope and peace, nothing but the blood of Jesus;

This is all my righteousness, nothing but the blood of Jesus.
\end{SBVerse}
\end{song}\begin{song}{O Come Let Us Adore Him}{D}
{C. Frederick Oakley}
{C. Frederick Oakley}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{O c}ome let us adore Him

O c\Ch{D/F#}{ome} let us adore H\Ch{Bm7}{im }  \Ch{A2}{   }

O c\Ch{G}{ome} let\Ch{D/F#}{   }us\Ch{A2}{ ad}o\Ch{Bm7}{re }H\Ch{G}{im }

\Ch{D}{Chr}i\Ch{A2}{st }the Lor\Ch{D}{d  }
\end{SBVerse}
\begin{SBVerse}
For You alone are worthy

For You alone are worthy

For You alone are worthy

Christ the Lord
\end{SBVerse}
\begin{SBVerse}
We'll give you all the glory

We'll give you all the glory

We'll give you all the glory

Christ the Lord
\end{SBVerse}
\end{song}\begin{song}{O For A Thousand Tongues To Sing}{G}
{Charles Wesley}
{Charles Wesley}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
O \Ch{G}{for} a \Ch{D}{tho}usand \Ch{G}{ton}gues \Ch{D}{to }\Ch{Em}{sin}g my \Ch{G}{gre}at \Ch{C}{Red}eemer's \Ch{D}{pra}ise,

The \Ch{G}{glo}ries of my \Ch{C}{God} and King, the \Ch{G/D}{tri}umphs of \Ch{D}{His} \Ch{G}{gra}ce.
\end{SBVerse}
\begin{SBVerse}
Jesus, the name that charms our fears, that bids our sorrows cease;

It's music in the sinner's ears, it's life, and health, and peace.
\end{SBVerse}
\begin{SBVerse}
He breaks the power of cancelled sin, He sets the prisoner free;

His blood can make the foulest clean;  His blood availed for me.
\end{SBVerse}
\begin{SBVerse}
My gracious Master and my God, assist me to proclaim,

To spread through all the earth abroad the honors of your name.
\end{SBVerse}
\begin{SBVerse}
Glo\Ch{A}{ry }to G\Ch{E}{od }and \Ch{A}{pra}ise \Ch{E}{and} \Ch{F#m}{lov}e be \Ch{A}{eve}r, \Ch{D}{eve}r giv\Ch{E}{'n }

By \Ch{A}{sai}nts below and sai\Ch{D}{nts} above, the C\Ch{A/#}{hur}ch in ea\Ch{E}{rth} and h\Ch{A}{eav}'n
\end{SBVerse}
\end{song}\begin{song}{O Praise Him}{G}
{David Crowder}
{David Crowder}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Tur}n your ear to \Ch{D/F#}{hea}ven and hear the \Ch{C2}{noi}se inside

The \Ch{G}{sou}nd of angels' awe, the \Ch{D/F#}{sou}nd of angels' songs

\Ch{C2}{All} this for a king, \Ch{Am7}{we }could join and sing, \Ch{C2}{all} to Christ the King
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{How} constant, how\Ch{C2}{ di}vine, \Ch{D}{ th}is song of ours\Ch{C2}{ wi}ll rise

\Ch{D}{O, }how constant, how\Ch{C2}{ di}vine, \Ch{D}{ th}is love of ours\Ch{C2}{ wi}ll rise, will rise
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{O P}raise Him,\Ch{D/F#}{ O }praise Him, \Ch{Em7}{He }is Holy, \Ch{C2}{He }is Hol\Ch{Am7}{y  }
\end{SBVerse}
\begin{SBVerse}
\Ch{G			}{Tur}n your gaze t\Ch{D/F#}{o h}eaven and raise \Ch{C2}{a j}oyous noise

The \Ch{G}{sou}nd of salvation come, the \Ch{D/F#}{sou}nd of rescued ones

\Ch{C2}{All} this for a king, \Ch{Am}{ang}els join to sing, \Ch{C2}{all} for Christ our King
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{How} infinite and \Ch{C2}{swe}et, \Ch{D}{thi}s love so rescu\Ch{C2}{ing}

\Ch{D}{O, }how infinitely s\Ch{C2}{wee}t, \Ch{D}{thi}s great love that has \Ch{C2}{red}eemed 

as \Ch{C2}{one} we sing
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{All}elulia, \Ch{D/F#}{All}elulia, \Ch{Em7}{He }is Holy, \Ch{C2}{He }is Ho\Ch{Am7}{ly }

\Ch{G}{All}elulia, \Ch{D/F#}{All}elulia, \Ch{Em7}{He }is Holy, \Ch{C2}{He }is Ho\Ch{Am7}{ly }
\end{SBVerse}
\end{song}\begin{song}{Oh Lord Our Lord}{C}
{Doug Bergsma}
{Doug Bergsma}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
O \Ch{C}{Lor}d, our \Ch{G}{Lor}d,

How \Ch{F}{maj}estic is Your \Ch{C}{nam}e in all the \Ch{G7}{ear}th

O \Ch{C}{Lor}d, our \Ch{G}{Lor}d,

How \Ch{F}{maj}estic is Your \Ch{C}{nam}e in all the \Ch{G}{ear}th
\end{SBVerse}
\begin{SBVerse}
We \Ch{F}{giv}e you \Ch{G}{pra}ise, we give you \Ch{C}{glo}ry

And \Ch{F}{mag}ni\Ch{D}{fy }Your holy \Ch{G}{nam}e

We \Ch{F}{hon}our \Ch{G}{you}, we \Ch{E7}{wor}ship \Ch{Am}{you}

And \Ch{Dm}{glo}ri\Ch{G}{fy }your \Ch{C}{nam}e
\end{SBVerse}
\end{song}\begin{song}{Once Again}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Jes}us \Ch{A}{Chr}ist, I thi\Ch{G}{nk }upon Your sacrific\Ch{D/F#}{e  }

\Ch{G}{You} became no\Ch{D/F#}{thi}ng, p\Ch{G}{our}ed out to deat\Ch{A}{h  }

\Ch{D}{Man}y ti\Ch{A}{mes} I've wo\Ch{G}{nde}red at Your gift \Ch{D/F#}{of }life

And \Ch{G}{I'm} in that pl\Ch{A}{ace} once again\Ch{D}{   }

\Ch{G}{I'm} in that pl\Ch{A}{ace} once again\Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
And \Ch{D}{onc}e again I \Ch{D2/F#}{loo}k upon the cr\Ch{G}{oss} where You died\Ch{A}{   }

I'm h\Ch{D}{umb}led by Your \Ch{D2/F#}{mer}cy and I'm br\Ch{G}{oke}n inside\Ch{A}{   }

\Ch{Bm}{Onc}e again I th\Ch{G}{ank} You

\Ch{Bm}{Onc}e again I p\Ch{A}{our} out my life\Ch{G}{   } \Ch{A}{   } \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Now} You \Ch{A}{are} exalted\Ch{G}{ to} the highest \Ch{D}{pla}ce

\Ch{G}{Kin}g of \Ch{D}{the} heavens, where \Ch{G}{one} day I'll \Ch{A}{bow}

\Ch{D}{But} for \Ch{A}{now}, I ma\Ch{G}{rve}l at Your sa\Ch{D}{vin}g grace

And \Ch{G}{I'm} full of pr\Ch{A}{ais}e once again\Ch{D}{   }

\Ch{G}{I'm} full of pra\Ch{A}{ise} once again\Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Tha}nk You for the cr\Ch{A}{oss}

\Ch{G}{Tha}nk You for the cr\Ch{D/F#}{oss}

\Ch{G}{Tha}nk You for the cr\Ch{A}{oss}, my Fr\Ch{D}{ien}d
\end{SBVerse}
\end{song}\begin{song}{One Way}{A}
{Hillsong}
{Hillsong}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
I\Ch{A}{ La}y my life down at your feet,\Ch{F#m7}{ yo}ur the only one i need

\Ch{E}{I t}urn to you and you were always th\Ch{D}{ere}.

\Ch{A}{In }troubled times it's you i seek, \Ch{F#m7}{i p}ut you first thats all i need,

\Ch{E}{I h}umble all i am all to y\Ch{D}{ou!}
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{One} Way\Ch{E}{ Je}sus,\Ch{F#m7}{ yo}ur the only one th\Ch{D}{at }i could live for.

\Ch{A}{One} Way\Ch{E}{ Je}sus,\Ch{F#m7}{ yo}ur the only one th\Ch{G}{at }i could live for.
\end{SBVerse}
\begin{SBVerse}
Instrumental
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{You} were always, always there. \Ch{F#m7}{Eve}ry how and everywhere

\Ch{E}{You}r grace abounds so deeply within \Ch{D}{me }

\Ch{A}{You} will never ever change, y\Ch{F#m7}{est}erday today the same

\Ch{E}{For}ever til forever meets no e\Ch{D}{nd }
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{You} are the way the tr\Ch{E}{uth} and the life

We\Ch{F#m7}{ li}ve by faith \Ch{D}{and} not by sight fo\Ch{F#m7}{r y}ou. We're\Ch{E}{ li}ving all \Ch{D}{for} you
\end{SBVerse}
\end{song}\begin{song}{Open The Eyes of My Heart}{E}
{Paul Baloche}
{Paul Baloche}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Ope}n the eyes of my heart, Lord

\Ch{B}{Ope}n the eyes of my heart

I want to \Ch{A}{see} you

I want to \Ch{E}{see} you   \Ch{G}{   }\Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{Ope}n the eyes of my heart, Lord

\Ch{B}{Ope}n the eyes of my heart

I want to \Ch{A}{see} you

I want to \Ch{E}{see} you  \Ch{E}{   }\Ch{E/D}{   }   \Ch{E}{   }
\end{SBVerse}
\begin{SBVerse}
To see You \Ch{B}{hig}h and lifted \Ch{C#m}{up }

\Ch{A}{Shi}ning in the light of Your \Ch{B}{glo}ry

\Ch{B}{Pou}r out Your power and \Ch{C#m}{lov}e

As we sing \Ch{A}{hol}y, holy, \Ch{B}{hol}y

\Ch{A}{Hol}y, holy, \Ch{B}{hol}y

I want to \Ch{E}{see} you
\end{SBVerse}
\end{song}\begin{song}{Our God}{G}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Em}{Wat}er You t\Ch{C}{urn}ed into win\Ch{G}{e  }

\Ch{Em}{Ope}ned the e\Ch{C}{yes} of the blin\Ch{G}{d  }

There's no one\Ch{Am7}{ li}ke You

None like\Ch{D}{ Yo}u
\end{SBVerse}
\begin{SBVerse}
\Ch{Em}{Int}o the d\Ch{C}{ark}ness You shin\Ch{G}{e  }

\Ch{Em}{Out} of the a\Ch{C}{she}s we ris\Ch{G}{e  }

There's no one \Ch{Am7}{lik}e You

None like\Ch{D}{ Yo}u
\end{SBVerse}
\begin{SBVerse}
\Ch{Em}{Our} God is greater

\Ch{C}{Our} God is stronger

\Ch{G}{God} You are higher than \Ch{D/F#}{any} other

\Ch{Em}{Our} God is healer

\Ch{C}{Awe}some in power

Our \Ch{G}{God}, Our \Ch{D}{God}
\end{SBVerse}
\begin{SBVerse}
\Ch{Em}{Int}o the d\Ch{C}{ark}ness You shin\Ch{G}{e  }

\Ch{Em}{Out} of the a\Ch{C}{she}s we ris\Ch{G}{e  }

There's no one\Ch{Am7}{ li}ke You

None like\Ch{D}{ Yo}u
\end{SBVerse}
\begin{SBVerse}
\Ch{Em}{And} if our God is for us

\Ch{C}{The}n who could ever stop us

\Ch{G}{And} if our God is with us

\Ch{D/F#}{The}n what could stand against
\end{SBVerse}
\end{song}\begin{song}{Pour Out My Heart}{G}
{Craig  Musseau}
{Craig  Musseau}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Here I \Ch{G}{am,} once \Ch{D}{aga}in

I \Ch{Em}{pou}r out my heart for I \Ch{C}{kno}w that you hear

Every \Ch{G}{cry}, you are \Ch{D}{lis}tening

No \Ch{Em}{mat}ter what state \Ch{C}{my }heart is in
\end{SBVerse}
\begin{SBVerse}
You are \Ch{G}{fai}thful to \Ch{D}{ans}wer

With \Ch{Em}{wor}ds that are true and a \Ch{C}{hop}e that is real

As I \Ch{G}{fee}l your \Ch{D}{tou}ch

\Ch{Em}{You} bring a freedom to \Ch{C}{all} that's within
\end{SBVerse}
\begin{SBVerse}
In the \Ch{Am7}{saf}ety \Ch{G}{of }this \Ch{C}{pla}ce

I'm \Ch{D7sus}{lon}ging to...
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Pou}r out my heart to \Ch{D}{say} that I love you

\Ch{Em}{Pou}r out my heart to \Ch{C}{say} that I need you

\Ch{G}{Pou}r out my heart to \Ch{D}{say} that I'm thankful

\Ch{Em}{Pou}r out my heart to \Ch{C}{say} that you're wonderful\Ch{G}{   \Ch{D}{}  \Ch{Em}{}  }\Ch{C}{   }
\end{SBVerse}
\end{song}\begin{song}{Refiner's Fire}{D}
{Brian Doerksen}
{Brian Doerksen}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Pur}i\Ch{A}{fy }my \Ch{Bm}{hea}rt

let me be as \Ch{Em7}{gol}d and \Ch{Asus}{pre}cio\Ch{A}{us }\Ch{Asus}{sil}ve\Ch{A}{r  }

\Ch{D}{Pur}i\Ch{A}{fy }my \Ch{Bm}{hea}rt,

let me be as \Ch{Em7}{gol}d, \Ch{D}{pur}e \Ch{A}{gol}d
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Re-}\Ch{G}{fin}er's\Ch{A}{ fi}re

\Ch{D}{My }heart's \Ch{G}{one} de\Ch{A}{sir}e

is to \Ch{D}{be }\Ch{A}{hol}y

\Ch{D}{set} apa\Ch{G}{rt }for \Ch{Asus}{You}   \Ch{A}{Lor}d.

I choose to \Ch{D}{be }\Ch{A}{hol}y

\Ch{D}{set} a\Ch{G}{par}t for \Ch{D}{you} my \Ch{A}{mas}ter,

\Ch{Em}{rea}dy to \Ch{Asus}{do }   \Ch{A}{you}r \Ch{G}{wil}l.   \Ch{D}{   }

\Ch{D}{Pur}i\Ch{A}{fy }my \Ch{Bm}{hea}rt,

cleanse me from wit\Ch{Em7}{hin} and \Ch{Asus}{mak}e  \Ch{A}{me }\Ch{Asus}{hol}y. \Ch{A}{   }

\Ch{D}{Pur}i\Ch{A}{fy }my \Ch{Bm}{hea}rt,

cleanse me from my \Ch{Em7}{sin}, \Ch{D}{dee}p \Ch{A}{wit}hin
\end{SBVerse}
\end{song}\begin{song}{Revelation Song}{D}
{Jennie Lee Riddle}
{Jennie Lee Riddle}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D2}{  W}orthy is the \Ch{Am7}{  L}amb who was slain\Ch{C2}{.  } Holy, holy i\Ch{G}{s H}e.

\Ch{D2}{  S}ing a new son\Ch{Am7}{g  }to Him who sits on\Ch{C2}{   }Heaven's Mercy S\Ch{G}{eat}.

(REPEAT)
\end{SBVerse}
\begin{SBVerse}
\Ch{D2}{  H}oly, Holy, Holy\Ch{Am7}{  i}s The Lord, God Almighty. 

\Ch{C2}{  W}ho was and is and is to \Ch{G}{com}e.

\Ch{D2}{  W}ith all creation I sing\Ch{Am7}{,  }Praise to The King of Kings,

\Ch{C2}{  Y}ou are my everything. And \Ch{G}{I w}ill adore You.\Ch{D2}{   }  \Ch{Am7}{   }   \Ch{C2}{   }  \Ch{G}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{D2}{  C}lothed in rainbows\Ch{Am7}{,  }of living color. 

\Ch{C2}{  F}lashes of lightening, rolls of \Ch{G}{thu}nder.

\Ch{D2}{  B}lessing and honor, strength and\Ch{Am7}{   }glory and power be,

\Ch{C2}{  T}o You, the only wise \Ch{G}{Kin}g.
\end{SBVerse}
\begin{SBVerse}
\Ch{D2}{  F}illed with wonder,\Ch{Am7}{  a}westruck wonder,

\Ch{C2}{  A}t the mention of Your \Ch{G}{Nam}e.

\Ch{D2}{  J}esus, Your Name is power,\Ch{Am7}{  b}reath and living water.

\Ch{C2}{  S}uch a marvelous my\Ch{G}{ste}ry.
\end{SBVerse}
\end{song}\begin{song}{Salvation}{E}
{Charlie Hall}
{Charlie Hall}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{Sal}vation sp\Ch{A2}{rin}g up from the \Ch{E}{gro}und

Lord, rend the \Ch{A2}{hea}vens and come \Ch{E}{dow}n

Seek the \Ch{A2}{los}t and heal the \Ch{E}{lam}e

Jesus bring \Ch{A2}{glo}ry to Your \Ch{E}{nam}e
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{Let} all the \Ch{A2}{pro}digals run \Ch{E}{hom}e

All of crea\Ch{A2}{tio}n waits and \Ch{E}{gro}ans

Lord, we've \Ch{A2}{hea}rd of Your great \Ch{E}{fam}e

Father, cause all to \Ch{A2}{sho}ut Your \Ch{E}{nam}e
\end{SBVerse}
\begin{SBVerse}
\Ch{Bsus}{Sti}r up our \Ch{C#m7}{hea}rts, oh \Ch{A2}{God}

\Ch{Bsus}{Awa}ken our \Ch{C#m7}{spi}rits to \Ch{A2}{awe} who \Ch{Bsus}{You} are

Put a \Ch{C#m7}{cry} in \Ch{A2}{us }

So \Ch{Bsus}{dee}p in\Ch{A2}{sid}e that we \Ch{Bsus}{can}not \Ch{A2}{fin}d

The \Ch{Bsus}{wor}ds we \Ch{A2}{nee}d

We just \Ch{Bsus		}{wee}p and c\Ch{E}{ry }out to You
\end{SBVerse}
\end{song}\begin{song}{Sanctuary}{D}
{John W. Thompson}
{John W. Thompson}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Lor}d, prepare me \Ch{A}{to }be a sanctuary

Pure and h\Ch{G}{oly}, tried and tru\Ch{D}{e  }\Ch{A}{   }

With thanksg\Ch{D}{ivi}ng, I'll be a liv\Ch{A}{ing}

Sanctu\Ch{G}{ary} \Ch{A}{for} Y\Ch{D}{ou }
\end{SBVerse}
\begin{SBVerse}
It is you,\Ch{D}{ Lo}rd who came to\Ch{A}{ sa}ve

The heart and s\Ch{G}{oul} of every m\Ch{D}{an.}\Ch{A}{   }

It is y\Ch{D}{ou }Lord who knows my we\Ch{A}{akn}ess,

Who gives me str\Ch{G}{eng}th, with th\Ch{A}{ine} own h\Ch{D}{and}.
\end{SBVerse}
\begin{SBVerse}
Lead Me \Ch{D}{on }Lord from tempt\Ch{A}{ati}on,

Puri\Ch{G}{fy }me from with\Ch{D}{in.}\Ch{A}{   }

Fill my h\Ch{D}{ear}t with Your holy sp\Ch{A}{iri}t,

Take aw\Ch{G}{ay }a\Ch{A}{ll }my s\Ch{D}{in.}
\end{SBVerse}
\end{song}\begin{song}{Seek Ye First}{C}
{Karen Lafferty}
{Karen Lafferty}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Se\Ch{C}{ek }ye fi\Ch{Em}{rst} the k\Ch{Am}{ing}dom of Go\Ch{Em}{d  }

A\Ch{Dm7}{nd }His r\Ch{C}{igh}teousn\Ch{G}{ess}  \Ch{G7}{   }

A\Ch{C}{nd }all these th\Ch{Em}{ing}s shall be ad\Ch{Am}{ded} unto y\Ch{Em}{ou }

\Ch{Dm7}{All}elu\Ch{C}{, a}llelu\Ch{G}{ia }\Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
Man does not live by bread alone

But by every word

That proceeds from the mouth of God

Allelu, alleluia
\end{SBVerse}
\begin{SBVerse}
Ask and it shall be given unto you

Seek and ye shall find

Knock and the door shall be opened unto you

Allelu, alleluia
\end{SBVerse}
\end{song}\begin{song}{Shine Jesus Shine}{A}
{Graham Kendrick}
{Graham Kendrick}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{Lor}d the l\Ch{D/A}{igh}t of Your l\Ch{A}{ove} is s\Ch{E/A}{hin}ing

\Ch{A}{in }the \Ch{D/A}{mid}st of the da\Ch{A}{rkn}ess s\Ch{E/A}{hin}ing

\Ch{D}{Jes}us \Ch{E/D}{Lig}ht of the \Ch{C#m}{Wor}ld shine up\Ch{F#m}{on }us

\Ch{D}{set} us \Ch{E/D}{fre}e by the \Ch{C#m}{tru}th you now \Ch{F#m}{bri}ng us

\Ch{G}{shi}ne on \Ch{Esus}{me }   \Ch{E}{   }

\Ch{G}{shi}ne on \Ch{Esus}{me }   \Ch{E}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{Shi}ne \Ch{E/A}{Jes}u\Ch{A}{s s\Ch{D}{}hi}ne

fill \Ch{A/C#}{thi}s l\Ch{Bm}{and} \Ch{Bm/A}{wit}h the \Ch{Esus}{Fat}he\Ch{E}{r's} \Ch{Esus}{glo}ry\Ch{E}{   }

\Ch{A}{Bla}ze \Ch{E/A}{Spi}r\Ch{A}{it }\Ch{D}{bla}ze

set \Ch{A/C#}{our} h\Ch{Bm}{ear}ts\Ch{Bm/A}{ on} f\Ch{G}{ire}  \Ch{Esus}{   }   \Ch{E}{   }

\Ch{A}{Flo}w \Ch{E/A}{riv}e\Ch{A}{r f\Ch{D}{}lo}w

flood\Ch{A/C#}{ th}e \Ch{Bm}{nat}\Ch{Bm/A}{ion}s with \Ch{Esus}{gra}ce \Ch{E}{and}\Ch{Esus}{ me}rc\Ch{E}{y  }

\Ch{A}{Sen}d \Ch{E/A}{for}th Y\Ch{A}{our} w\Ch{D}{ord}, Lord

\Ch{A/C#}{and} l\Ch{Bm}{et }t\Ch{E7}{her}e be l\Ch{A}{igh}t \Ch{D/A}{   } \Ch{E/A}{   } \Ch{D/A}{   }  \Ch{A}{   \Ch{D/A}{}  } \Ch{E/A}{   } \Ch{D/A}{   }  \Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
Lord, I come to Your awesome presence

From the shadows into your radiance

By the blood I may enter Your brightness

Search me, try me consume all my darkness

Shine on me

shine on me
\end{SBVerse}
\begin{SBVerse}
As we gaze on your kingly brightness

So our faces display your likeness

Ever changing from glory to glory

Mirrored here may our lives tell your story

Shine on me

shine on me
\end{SBVerse}
\end{song}\begin{song}{Shine On Us}{D}
{Deborah D. Smith}
{Deborah D. Smith}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Lor}d, \Ch{G/D}{let} your l\Ch{D}{igh}t, light \Ch{F#mA}{of }your \Ch{G2}{fac}e, shine \Ch{A/C#}{on } u\Ch{D}{s. }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Lor}d, \Ch{G/D}{let} your l\Ch{D}{igh}t, light \Ch{F#mA}{of }your \Ch{G2}{fac}e, shine \Ch{A/C#}{on } u\Ch{D}{s. }
\end{SBVerse}
\begin{SBVerse}
\Ch{D/F#}{Tha}t \Ch{G2}{we } \Ch{A/C#}{may} be sa\Ch{D}{ved}, \Ch{D/F#}{tha}t \Ch{G2}{we } \Ch{A/C#}{may} have l\Ch{D}{ife},
\end{SBVerse}
\begin{SBVerse}
To \Ch{D/F#}{fin}d our \Ch{G2}{way} in the d\Ch{F#A#}{ark}est \Ch{Bm-G}{nig}ht, let your \Ch{D/A}{lig}ht shine \Ch{A7}{on }u\Ch{D}{s. }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Lor}d, \Ch{G/D}{let} your g\Ch{D}{rac}e, grace \Ch{F#mA}{fro}m you\Ch{G2}{r h}and, fall \Ch{A/C#}{on } u\Ch{D}{s. }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Lor}d, \Ch{G/D}{let} your g\Ch{D}{rac}e, grace \Ch{F#mA}{fro}m you\Ch{G2}{r h}and, fall \Ch{A/C#}{on } u\Ch{D}{s. }
\end{SBVerse}
\begin{SBVerse}
\Ch{D/F#}{Tha}t \Ch{G2}{we } \Ch{A/C#}{may} be sa\Ch{D}{ved}, \Ch{D/F#}{tha}t \Ch{G2}{we } \Ch{A/C#}{may} have l\Ch{D}{ife},
\end{SBVerse}
\begin{SBVerse}
To \Ch{D/F#}{fin}d our \Ch{G2}{way} in the d\Ch{F#A#}{ark}est \Ch{Bm-G}{nig}ht, let your \Ch{D/A}{gra}ce fall \Ch{A7}{on }u\Ch{D}{s. }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Lor}d, \Ch{G/D}{let} your l\Ch{D}{ove}, love \Ch{F#mA}{wit}h no \Ch{G2}{end}, come \Ch{A/C#}{ove}r \Ch{D}{us.}
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Lor}d, \Ch{G/D}{let} your l\Ch{D}{ove}, love \Ch{F#mA}{wit}h no \Ch{G2}{end}, come \Ch{A/C#}{ove}r \Ch{D}{us.}
\end{SBVerse}
\begin{SBVerse}
\Ch{D/F#}{Tha}t \Ch{G2}{we } \Ch{A/C#}{may} be sa\Ch{D}{ved}, \Ch{D/F#}{tha}t \Ch{G2}{we } \Ch{A/C#}{may} have l\Ch{D}{ife},
\end{SBVerse}
\begin{SBVerse}
To \Ch{D/F#}{fin}d our \Ch{G2}{way} in the d\Ch{F#A#}{ark}est \Ch{Bm-G}{nig}ht, let your \Ch{D/A}{lov}e come o\Ch{A7}{ver} \Ch{D}{us.}
\end{SBVerse}
\begin{SBVerse}
Let your \Ch{G/D}{lig}ht shine \Ch{D}{on }\Ch{G2}{us.}
\end{SBVerse}
\end{song}\begin{song}{Shout to the Lord}{A}
{Darlene Zschech}
{Darlene Zschech}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{My }Jesus,\Ch{E}{ my} Savior,

\Ch{F#m}{Lor}d, there is \Ch{E}{non}e like \Ch{D}{You}

All of my d\Ch{A}{ays}, \Ch{D}{I w}ant to pr\Ch{A}{ais}e,

The wonders of your m\Ch{G}{igh}\Ch{D/F#}{ty } lo\Ch{E}{ve }
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{My }comfort,\Ch{E}{ my} shelter,

\Ch{F#m}{Tow}er of r\Ch{E}{efu}ge and st\Ch{D}{ren}gth

Let every br\Ch{A}{eat}h,\Ch{D}{ al}l that I \Ch{A}{am }

Never cease to \Ch{G}{wor}\Ch{D/F#}{shi}p Y\Ch{E}{ou }
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{Sho}ut to the \Ch{F#m}{Lor}d, all the \Ch{D}{ear}th let us s\Ch{E}{ing},

\Ch{A}{Pow}er and \Ch{F#m}{maj}esty, p\Ch{D}{rai}se to the K\Ch{E}{ing}

\Ch{F#m}{Mou}ntains bow down and the s\Ch{D}{eas} will roar, 

At the \Ch{E}{sou}nd \Ch{F#m}{of }your \Ch{E}{nam}e
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{I s}ing for \Ch{F#m}{joy} at the w\Ch{D}{ork} of your h\Ch{E}{and}s

\Ch{A}{For}ever I'll \Ch{F#m}{lov}e you, for\Ch{D}{eve}r I'll stand\Ch{E}{   }

\Ch{F#m}{Not}hing compares to the \Ch{D}{pro}mise I h\Ch{E}{ave} in \Ch{A}{You}
\end{SBVerse}
\end{song}\begin{song}{Shout To The North}{G}
{Martin Smith}
{Martin Smith}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Men of fa\Ch{G}{ith}, rise \Ch{D}{up }and s\Ch{C}{ing}

Of the g\Ch{G}{rea}t and g\Ch{D}{lor}ious K\Ch{C}{ing}

You are st\Ch{G}{ron}g when y\Ch{D}{ou }feel w\Ch{C}{eak},

In your b\Ch{G}{rok}en-n\Ch{D}{ess}, compl\Ch{C}{ete}.
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Sho}ut to the no\Ch{C}{rth} and the so\Ch{D}{uth}.

\Ch{G}{Sin}g to the e\Ch{C}{ast} and the w\Ch{D}{est}.

\Ch{G}{Jes}us is \Ch{C}{Sav}iour to a\Ch{D}{ll,}

\Ch{C}{Lor}d of h\Ch{D}{eav}en and ea\Ch{G}{rth}.
\end{SBVerse}
\begin{SBVerse}
Rise up women of the truth

Stand and sing to broken hearts

Who can know the healing power

Of our glorious King of love?
\end{SBVerse}
\begin{SBVerse}
\Ch{Em}{We'}ve been through fire, w\Ch{C}{e'v}e been through rain.

\Ch{Em}{We'}ve been refined by the p\Ch{C}{ow'}r of His name

\Ch{Em}{We'}ve fallen deeper \Ch{C}{in }love with You.

You've burned the \Ch{G/B}{tru}th on our \Ch{Dsus}{lip}s. \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
Rise up church with broken wings;

Fill this place with songs again

Of our God who reigns on high.

By His grace again we'll fly.
\end{SBVerse}
\end{song}\begin{song}{Silent Night}{A}
{Joseph Mohr}
{Joseph Mohr}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{Sil}ent night, holy \Ch{A7}{nig}ht

\Ch{E7/Bm}{All} is \Ch{E}{cal}m, \Ch{F#m/A}{All} is \Ch{A7}{bri}ght

\Ch{D}{Rou}nd yon Vir - gin, \Ch{A}{Mot}her and Child

\Ch{D}{Hol}y Infant so \Ch{A}{Ten}der and \Ch{A7}{mil}d,

\Ch{Bm}{Sle}ep in \Ch{E7}{hea}venly \Ch{F#m}{pea}ce,

\Ch{A}{Sle}ep in \Ch{D}{hea}venly \Ch{A}{pea}ce.
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{Sil}ent night, holy \Ch{A7}{nig}ht

\Ch{E7/Bm}{She}pherds \Ch{E}{qua}ke \Ch{F#m/A}{at }the \Ch{A7}{sig}ht,

\Ch{D}{Glo}ries stream from \Ch{A}{hea}ven afar,

\Ch{D}{Hea}venly hosts \Ch{A}{sin}g Alle\Ch{A7}{leu}- lia

\Ch{Bm}{Chr}ist the \Ch{E7}{Sav}iour is \Ch{F#m}{bor}n!

\Ch{A}{Chr}ist the \Ch{D}{Sav}iour is \Ch{A}{bor}n.
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{Sil}ent night, holy \Ch{A7}{nig}ht

\Ch{E7/Bm}{Son} of \Ch{E}{God}, love's \Ch{F#m/A}{pur}e   \Ch{A7}{lig}ht

\Ch{D}{Rad}iant beams from \Ch{A}{Thy} holy face

\Ch{D}{Wit}h the dawn of \Ch{A}{red}eeming \Ch{A7}{gra}ce,

\Ch{Bm}{Jes}us Lord \Ch{E7}{at }thy \Ch{F#m}{bir}th,

\Ch{A}{Jes}us Lord \Ch{D}{at }thy \Ch{A}{bir}th.
\end{SBVerse}
\end{song}\begin{song}{Sing Like The Saved}{A}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{We'}\Ch{			}{re }go\Ch{A}{nna} sing like the saved

\Ch{E			}{We'}re \Ch{A}{gon}na sing like the saved

\Ch{E}{We'\Ch{			}{}re} g\Ch{A}{onn}a sing like the saved

\Ch{E}{We'\Ch{			}{}re} g\Ch{A}{onn}a sing like the saved
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{A j\Ch{	}{}oy}ful noise we \Ch{A}{wil}l make

\Ch{E}{A j\Ch{	}{}oy}ful noise we \Ch{A}{wil}l make

\Ch{E}{A j\Ch{	}{}oy}ful noise we \Ch{A}{wil}l make

\Ch{E}{A j\Ch{	}{}oy}ful noise we \Ch{A}{wil}l make
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{You}\Ch{	}{ pu}t this joy in \Ch{A}{our} hearts

\Ch{E}{You}\Ch{	}{ pu}t this joy in \Ch{A}{our} hearts

\Ch{E}{You}\Ch{	}{ pu}t this joy in \Ch{A}{our} hearts

\Ch{E}{You}\Ch{	}{ pu}t this joy in \Ch{A}{our} hearts
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{We'\Ch{	}{}re} gonna dance like\Ch{A}{ th}e saved

\Ch{E}{We'\Ch{	}{}re} gonna dance like\Ch{A}{ th}e saved

\Ch{E}{We'\Ch{	}{}re} gonna dance like\Ch{A}{ th}e saved

\Ch{E}{We'\Ch{	}{}re} gonna dance like\Ch{A}{ th}e saved
\end{SBVerse}
\end{song}\begin{song}{Step By Step}{G}
{David (Beaker) Strasser}
{David (Beaker) Strasser}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{O G}od, You are m\Ch{D}{y G}od

And \Ch{C}{I w}ill ever praise \Ch{G}{You}. (2x)
\end{SBVerse}
\begin{SBVerse}
I will \Ch{Em}{see}k You in the \Ch{D}{mor}ning

And I will \Ch{C}{lea}rn to walk in Your \Ch{G-Em}{way}s

And \Ch{G}{ste}p by step You'll \Ch{D}{lea}d me

And I will \Ch{C}{fol}low You all of my \Ch{G}{day}s.
\end{SBVerse}
\end{song}\begin{song}{Take My Life and Let It Be}{D}
{Frances R. Havergal}
{Frances R. Havergal}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Tak}e my life and \Ch{G2}{let} it \Ch{D}{be }\Ch{Bm}{con}se\Ch{G}{cra}ted, \Ch{D}{Lor}d, \Ch{A}{to }Th\Ch{D}{ee;}

\Ch{D}{Tak}e my \Ch{A}{han}ds and \Ch{G2}{let} them \Ch{D}{mov}e at the \Ch{G2}{imp}ulse \Ch{D}{of }Thy \Ch{Bm}{lov}\Ch{A}{e, }

\Ch{D}{At }the \Ch{G2}{imp}ulse \Ch{D}{of }T\Ch{A}{hy }l\Ch{D}{ove}.
\end{SBVerse}
\begin{SBVerse}
Take my feet and let them be swift and beautiful for Thee;

Take my voice and let me sing always, only, for my King,

Always, only, for my King.
\end{SBVerse}
\begin{SBVerse}
Take my lips and let them be filled with messages for Thee;

Take my silver and my gold, not a mite would I withhold,

Not a mite would I withhold.
\end{SBVerse}
\begin{SBVerse}
Take my love, my God, I pour at Thy feet its treasure store;

Take myself and I will be ever, only, all for Thee,

Ever, only all for Thee.
\end{SBVerse}
\end{song}\begin{song}{Thank You For The Blood}{G}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Tha}nk You, \Ch{Bm7}{tha}nk You for the blood that You shed\Ch{Em}{,  }

\Ch{C2}{Sta}nding in Your blessing we \Ch{G}{sin}g these fr\Ch{Bm7}{eed}om s\Ch{C2}{ong}s.

\Ch{G}{Tha}nk You, \Ch{Bm7}{tha}nk You for the battle You wo\Ch{Em}{n, }

\Ch{C2}{Sta}nding in Your victory we s\Ch{G}{ing} salv\Ch{Bm7}{ati}on son\Ch{C2}{gs,}

\Ch{G}{We }sing sal\Ch{D}{vat}ion's son\Ch{C2}{g. }  \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
You have \Ch{G}{ope}ned a way to the Fa\Ch{Bm7}{the}r,

Where be\Ch{C2}{for}e we could never have come,

Jesus, c\Ch{G}{oun}t us as Yours now for\Ch{Bm7}{eve}r

As we si\Ch{C}{ng }these \Ch{A/C#}{fre}edom so\Ch{D}{ngs}. \Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
We s\Ch{G}{ing} of all You've do\Ch{C}{ne,}

We \Ch{A/C#			}{sin}g of al\Ch{D}{l Y}ou've done, 

We sing\Ch{B}{ of} all You've don\Ch{Em}{e f}or us,

Wo\Ch{D}{n f}or us, \Ch{C}{pai}d for us.
\end{SBVerse}
\end{song}\begin{song}{That's Why We Praise Him}{C}
{Tommy Walker}
{Tommy Walker}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
He Came to \Ch{C}{liv}e,\Ch{G}{  l}ive a \Ch{F}{per}fect life,

He came to \Ch{C}{be }\Ch{G}{  t}he living \Ch{F}{wor}d, our Light

He Came to \Ch{C}{die} \Ch{G}{ so} we'd be \Ch{F}{rec}onciled,

He came to \Ch{C}{ris}e\Ch{G}{  t}o show His \Ch{F}{pow}'r and might, and
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Tha}t's why we \Ch{G}{pra}ise him, \Ch{F}{tha}t's why we sing

\Ch{C}{Tha}t's why we \Ch{G}{off}er him our \Ch{F}{eve}ry\Ch{G}{thi}ng

\Ch{C}{Tha}t's why we \Ch{G}{bow} down and \Ch{F}{wor}ship this king,

'cause he \Ch{Dm7}{gav}e  \Ch{C/E}{his}   \Ch{F}{eve}-\Ch{G7}{ry-}th\Ch{Am}{ing}  \Ch{Am/G}{   }

'cause he \Ch{Dm7}{gav}e  \Ch{C/E}{his}   \Ch{F}{eve}-\Ch{G7}{ry-}th\Ch{C}{ing}   \Ch{G}{   }    \Ch{F}{   }
\end{SBVerse}
\begin{SBVerse}
He came to \Ch{C}{liv}e,\Ch{G}{  l}ive a\Ch{F}{gai}n in us

He came to \Ch{C}{be }\Ch{G}{  o}ur conquering K\Ch{F}{ing} and Friend

He came to \Ch{C}{hea}l \Ch{G}{ an}d show the l\Ch{F}{ost} ones his love

He came to \Ch{C}{go }\Ch{G}{  p}repare a pl\Ch{F}{ace} for us
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Hal}l\Ch{G}{e, }\Ch{F}{hal}leluj\Ch{G}{ah.} (8x)
\end{SBVerse}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{F}{I h}ave heard so \Ch{F/E}{man}y songs

\Ch{Cm/Eb}{Lis}tened to a \Ch{Bb/D}{tho}usand tongues

\Ch{Gm}{But} there is one that \Ch{F/C}{sou}nds above them \Ch{Dm}{all}     \Ch{C/E}{   }     \Ch{Bb/D}{   }

\Ch{F}{The} Father's song, the \Ch{F/E}{Fat}her's love

\Ch{Cm/Eb}{You} sung it over \Ch{Bb/D}{me }and for e\Ch{Gm}{ter}nity it's w\Ch{F/C}{rit}ten o\Ch{C}{n m}y h\Ch{F}{ear}t
\end{SBVerse}
\begin{SBVerse}
\Ch{F}{Hea}ven's perfect \Ch{Bb/D}{mel}ody \Ch{C/E}{   }

\Ch{F/A}{The} Crea\Ch{Bb}{tor}'s symphony

\Ch{F/A}{You} are singing\Ch{Gm}{ ov}er me

\Ch{Bb/C}{The} Father's \Ch{Dm}{son}g   \Ch{C/E}{   }

\Ch{F}{Hea}ven's perfect m\Ch{Bb/D}{yst}ery \Ch{C/E}{   }

\Ch{F/A}{The} king of \Ch{Bb}{Lov}e has sent for me

\Ch{F/A}{And} now you're sing\Ch{Gm}{ing} over\Ch{Csus/C}{ me}

\Ch{F}{The} Father's song
\end{SBVerse}
\end{song}\begin{song}{The Friendship And The Fear}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{Bm}{Sho}w me the way of the \Ch{G(add6)}{cro}ss once again

\Ch{Bm}{Den}ying myself for the \Ch{G(add6)}{lov}e that I've gain\Ch{Asus}{ed }

\Ch{Em7}{Eve}rything's You \Ch{Asus}{now}, e\Ch{D/F#}{ver}ything's chang\Ch{G}{ed,}

\Ch{A7sus}{It'}s time\Ch{Bm}{ Yo}u had my whole life;

\Ch{G}{You} can \Ch{Asus}{hav}e it all\Ch{D}{.  }
\end{SBVerse}
\begin{SBVerse}
\Ch{A7sus}{(Ye}s,) I \Ch{D}{res}olve \Ch{A7sus}{to }give i\Ch{D}{t a}ll;

\Ch{G}{Som}e things must \Ch{A7sus}{die},

\Ch{D}{Som}e things must l\Ch{G}{ive}.

\Ch{A7sus}{Not}, "What can I gain,"

\Ch{D}{But}, "What can \Ch{G}{I g}ive?"

\Ch{A7sus}{If }much is req\Ch{D}{uir}ed when muc\Ch{G}{h i}s recieved,

\Ch{A7sus}{The}n You ca\Ch{Bm}{n h}ave my whole life;

\Ch{G}{Jes}us, h\Ch{Asus}{ave} it all.\Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{Bm}{I'v}e given like a beggar but l\Ch{G(add6)}{ive}d like the rich

\Ch{Bm}{And} crafted myself a mo\Ch{G(add6)}{re }comfortable cr\Ch{Asus}{oss},

\Ch{Em7}{Yet} what I am\Ch{Asus}{ ca}lled to \Ch{D/F#}{is }deeper tha\Ch{G(add6)}{n t}his,

\Ch{A7sus}{It'}s time\Ch{Bm}{ Yo}u had my whole life;

\Ch{G}{You} can h\Ch{Asus}{ave} it al\Ch{D}{l. }
\end{SBVerse}
\end{song}\begin{song}{The Heart Of Worship}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{ Wh}en the music fa\Ch{A}{des}, all is stripped a\Ch{Em}{way},

And I simply c\Ch{A}{ome}

\Ch{D}{ Lo}nging just to br\Ch{A}{ing} something that's of \Ch{Em}{wor}th

That will bless Your he\Ch{A}{art}
\end{SBVerse}
\begin{SBVerse}
  \Ch{Em}{   }I'll bring You \Ch{D/F#}{mor}e than a s\Ch{A}{ong},

     For a song in it\Ch{Em}{sel}f,

     Is not what \Ch{D/F#}{you} have requ\Ch{A}{ire}d \Ch{A/C#}{   }   \Ch{D}{   }

  \Ch{Em}{   }You search much d\Ch{D/F#}{eep}er with\Ch{A}{in,}

     Through the way things app\Ch{Em}{ear}

     You're looking\Ch{D/F#}{ in}to my h\Ch{A}{ear}t
\end{SBVerse}
\begin{SBVerse}
   \Ch{D}{  I}'m coming back to the \Ch{A2/C#}{hea}rt of worship

     And it's \Ch{Em}{all} about You

     It's a\Ch{G}{ll }about Y\Ch{A}{ou,} Jes\Ch{D}{us }

     I'm sorry, Lord for the \Ch{A2/C#}{thi}ng I've made it

     When it's \Ch{Em}{all} about You

     It's a\Ch{G}{ll }about Y\Ch{A}{ou,} Jes\Ch{D}{us }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{ Ki}ng of endless w\Ch{A}{ort}h, no one could expr\Ch{Em}{ess},

How much You des\Ch{A}{erv}e

\Ch{D}{ Th}ough I'm weak and p\Ch{A}{oor}, all I have is Y\Ch{Em}{our}s,

Every single bre\Ch{A}{ath}
\end{SBVerse}

\end{song}\begin{song}{The Stand}{A}
{Joel Houston}
{Joel Houston}
{}
{}
\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{You stood before creation}

\Ch{D}{eternity in Your hand}

\Ch{A/C#}{You spoke the earth into} \Ch{F#m}{motion}

My soul now \Ch{D}{to stand}
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{You stood before my failure}

And \Ch{D}{carried} the cross for my shame

My \Ch{A/C#}{sin weighed upon Your} shou\Ch{F#m}{lders}

My soul now \Ch{D}{to stand}
\end{SBVerse}
\begin{SBVerse}
So what can I say\Ch{D}{}

\Ch{Dm}{And what could I} do\Ch{F#m}{}

But offer this heart\Ch{D}{ O God}\Ch{E}{}

Complete\Ch{F#m}{ly to You}\Ch{A}{}\Ch{E}{}\Ch{F#m}{}\Ch{D}{}\Ch{A}{}\Ch{E}{}\Ch{F#m}{}
\end{SBVerse}
\begin{SBVerse}
So \Ch{A}{I'll walk upon salvation}

Your \Ch{D}{Spirit alive in me}

This \Ch{A/C#}{life to declare} Your p\Ch{F#m}{romise}

My soul now \Ch{D}{to stand}
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{So I'll st}\Ch{A}{and}

With \Ch{E}{arms high and} \Ch{F#m}{heart abandoned}\Ch{D}{}

In \Ch{A}{awe of the} \Ch{E}{One who }\Ch{F#m}{gave it all}\Ch{D}{}

I'll st\Ch{A}{and}

My s\Ch{E}{oul Lord to} \Ch{F#m}{You surrendered}

\Ch{D}{All I am}\Ch{A}{ is Yours}\Ch{E}{}\Ch{F#m}{}
\end{SBVerse}
\begin{SBVerse}
So what can I say\Ch{D}

\Ch{Bm}{And what could I do}\Ch{F#m}{}

\Ch{A}{But offer this heart}\Ch{Bm7}{ O God}\Ch{E}{}

Complete\Ch{F#m}{ly to You}
\end{SBVerse}
\end{song}\begin{song}{The Wonderful Cross}{D}
{J. D. Walt}
{J. D. Walt}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{Whe}n I survey the \Ch{G}{won}drous \Ch{D}{cro}ss

\Ch{D}{On }which the \Ch{G}{Pri}nce of \Ch{D}{glo}ry \Ch{A}{die}d,

\Ch{D}{My }richest gain I \Ch{G}{cou}nt but \Ch{D}{los}s,

\Ch{D}{And} pour con\Ch{A}{tem}pt on all my \Ch{D}{pri}de.
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{See} from His head, His \Ch{G}{han}ds, His \Ch{D}{fee}t,

\Ch{D}{Sor}row and \Ch{G}{blo}od flow \Ch{D}{min}gled \Ch{A}{dow}n:

\Ch{D}{Did} e'er such love and \Ch{G}{sor}row \Ch{D}{mee}t,

\Ch{D}{Or }thorns compose so \Ch{A}{ric}h a \Ch{D}{cro}wn?
\end{SBVerse}
\begin{SBVerse}
Oh the \Ch{G}{won}derful \Ch{D}{Cro}ss, oh the \Ch{G}{won}derful \Ch{D}{Cro}ss

Bids me \Ch{G}{com}e and die and \Ch{D}{fin}d that I may \Ch{A}{tru}ly live

Oh the \Ch{G}{won}derful \Ch{D}{Cro}ss, oh the \Ch{G}{won}derful \Ch{D}{Cro}ss

All who \Ch{G}{gat}her here by \Ch{D}{gra}ce draw near

And \Ch{A}{ble}ss Your name
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Wer}e the whole realm of \Ch{G}{Nat}ure m\Ch{D}{ine},

\Ch{D}{Tha}t were an \Ch{G}{off}ering \Ch{D}{far} too s\Ch{A}{mal}l;

\Ch{D}{Lov}e so amazing, \Ch{G}{so }div\Ch{D}{ine},
\end{SBVerse}
\end{song}\begin{song}{Trading My Sorrows}{A}
{Darrell Evans}
{Darrell Evans}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{A}{I'm} t\Ch{D}{rad}ing my \Ch{F#m}{sor} - r\Ch{E}{ows}

\Ch{A}{I'm} t\Ch{D}{rad}ing my \Ch{F#m}{sha} - \Ch{E}{ame}

\Ch{A}{I'm} l\Ch{D}{ayi}ng them d\Ch{F#m}{own} 

For the \Ch{E}{joy} of the L\Ch{A}{ord} \Ch{D}{   }\Ch{F#m}{   }  \Ch{E}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{I'm} t\Ch{D}{rad}ing my \Ch{F#m}{sic}k - n\Ch{E}{ess}

\Ch{A}{I'm} t\Ch{D}{rad}ing my \Ch{F#m}{pa }- \Ch{E}{in }

\Ch{A}{I'm} l\Ch{D}{ayi}ng them d\Ch{F#m}{own}

For the \Ch{E}{joy} of the L\Ch{A}{ord} \Ch{D}{   }\Ch{F#m}{   }  \Ch{E}{   }
\end{SBVerse}
\begin{SBVerse}
We say...

\Ch{A}{Yes} Lord, \Ch{D}{Yes} Lord, \Ch{F#m}{Yes} Yes \Ch{E}{Lor}d

\Ch{A}{Yes} Lord, \Ch{D}{Yes} Lord, \Ch{F#m}{Yes} Yes \Ch{E}{Lor}d

\Ch{A}{Yes} Lord, \Ch{D}{Yes} Lord, \Ch{F#m}{Yes} Yes \Ch{E}{Lor}d, \Ch{A}{Ame}n\Ch{D}{.  }\Ch{F#m}{   }  \Ch{E}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{A}{I'm} pressed but not \Ch{D}{cru}shed

perse\Ch{F#m}{cut}ed not a\Ch{E}{ban}doned

\Ch{A}{Str}uck d\Ch{D}{own} but not destr\Ch{F#m}{oye}d  \Ch{E}{   }

\Ch{A}{I'm} blessed beyond the \Ch{D}{cur}se

For His \Ch{F#m}{pro}mise will endu\Ch{E}{re }

And His j\Ch{A}{oy }is gonna \Ch{D}{be }my st\Ch{F#m}{ren}gth \Ch{E}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{Tho}ugh the sorrow may last for a night

J\Ch{D}{oy }comes in the mo\Ch{E}{rni}ng
\end{SBVerse}
\end{song}\begin{song}{Trust and Obey}{C}
{John H. Sammis}
{John H. Sammis}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
W\Ch{C}{hen} we walk with \Ch{G7}{the} L\Ch{C}{ord}

In the l\Ch{G7}{igh}t of H\Ch{F}{is }W\Ch{C}{ord}

What a gl\Ch{F}{ory} He s\Ch{C}{hed}s on our w\Ch{G7}{ay!}

While we \Ch{C}{do }His g\Ch{G7}{ood} w\Ch{C}{ill},

He ab\Ch{G7}{ide}s with \Ch{F}{us }st\Ch{C}{ill},

And with a\Ch{F}{ll }who will tr\Ch{C}{ust} and \Ch{G7}{obe}y\Ch{C}{.  }
\end{SBVerse}
\begin{SBVerse}
Tr\Ch{G7}{ust} and o\Ch{C}{bey}, for there's \Ch{A}{no }other w\Ch{Dm}{ay }

To be h\Ch{G}{app}y in J\Ch{C}{esu}s,

But to tr\Ch{G}{ust} and o\Ch{G7}{bey}.\Ch{C}{   }
\end{SBVerse}
\begin{SBVerse}
For we never can prove the delights of his love

Until all on the altar we lay.

For the favor he shows and the joy he bestow

Are for those who will trust and obey.  So we'll...
\end{SBVerse}
\begin{SBVerse}
Then in fellowship sweet we will sit at his feet,

Or we'll walk by his side in the way.

What he says we will do; where he sends we will go.

Never fear: only trust and obey.  So we'll ...
\end{SBVerse}
\end{song}\begin{song}{Undignified (I Will Dance, I Will Sing)}{D}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D}{I w}ill dance, \Ch{G}{I w}ill sing

To be \Ch{D/F#}{mad}   \Ch{A/E}{for} my Ki\Ch{A}{ng.}

\Ch{D}{Not}hing Lord, is h\Ch{G}{ind}ering

The passion \Ch{D/F#}{in }  my s\Ch{A/E}{oul}. \Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
And \Ch{D}{I'l}l bec\Ch{G}{ome} even \Ch{D/F#}{mor}e un\Ch{A/E}{dig}ni-f\Ch{A}{ied} than t\Ch{D}{his}. \Ch{G}{   }

(Some would \Ch{D/F#}{say} it's \Ch{A/E}{foo}lish-n\Ch{A}{ess} but)

\Ch{D}{I'l}l bec\Ch{G}{ome} even \Ch{D/F#}{mor}e un\Ch{A/E}{dig}ni-f\Ch{A}{ied} than t\Ch{D}{his}. \Ch{G}{   }  \Ch{D/F#}{   }   \Ch{A/E}{   }  \Ch{A}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Na,} na, na, na, na, \Ch{G}{na!} Hey!  \Ch{D/F#}{   }   \Ch{A/E}{   }  \Ch{A}{   }

\Ch{D}{Na,} na, na, na, na, \Ch{G}{na!} Hey!  \Ch{D/F#}{   }   \Ch{A/E}{   }  \Ch{A}{   } \Ch{(D)}{   }
\end{SBVerse}
\end{song}\begin{song}{We Bow Down}{C}
{Twila Paris}
{Twila Paris}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
You are \Ch{C}{Lor}d of \Ch{F}{cre}ation and \Ch{G}{Lor}d of my \Ch{C}{lif}e

Lord of the \Ch{G}{lan}d and the sea

You were \Ch{C}{Lor}d of the \Ch{F}{hea}vens be\Ch{G}{for}e there was \Ch{Am}{tim}e

And \Ch{F}{Lor}d of all \Ch{G}{Lor}ds you will \Ch{C}{be }
\end{SBVerse}
\begin{SBVerse}
We bow \Ch{C}{dow}\Ch{F}{n a}nd we \Ch{G}{wor}ship You \Ch{C}{Lor}d  (repeat 3x)

\Ch{F}{Lor}d of all \Ch{G}{Lor}ds You will \Ch{C}{be }
\end{SBVerse}
\begin{SBVerse}
You are \Ch{C}{Kin}g of \Ch{F}{cre}ation and \Ch{G}{Kin}g of my \Ch{C}{lif}e

King of the \Ch{G}{lan}d and the sea

You were \Ch{C}{Kin}g of the \Ch{F}{hea}vens be\Ch{G}{for}e there was \Ch{Am}{tim}e

And \Ch{F}{Kin}g of all \Ch{G}{Kin}gs you will \Ch{C}{be }
\end{SBVerse}
\end{song}\begin{song}{We Fall Down}{E}
{Chris Tomlin}
{Chris Tomlin}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{E}{We }fall down

We l\Ch{B}{ay }our c\Ch{C#m}{row}ns

At the fee\Ch{A}{t o}f Jesus  \Ch{B}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{E}{The} greatness of\Ch{B}{ me}rcy a\Ch{C#m}{nd }love

At the feet\Ch{A}{ of} Jesus  \Ch{B}{   }
\end{SBVerse}
\begin{SBVerse}
And \Ch{E}{we }c\Ch{B}{ry,} "H\Ch{A}{oly}, H\Ch{C#m}{oly}, Ho\Ch{B}{ly"}

And \Ch{E}{we }c\Ch{B}{ry,} "H\Ch{A}{oly}, \Ch{C#m}{Hol}y, H\Ch{B}{oly}"

And \Ch{E}{we }c\Ch{B}{ry,} "H\Ch{A}{oly}, \Ch{C#m}{Hol}y, H\Ch{B}{oly}"

Is the Lamb\Ch{E}{   }
\end{SBVerse}
\end{song}\begin{song}{What A Friend I've Found}{C}
{Martin Smith}
{Martin Smith}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{C}{Wha}t a friend I've fo\Ch{Dm}{und},

\Ch{C}{Clo}ser than a br\Ch{Dm}{oth}er;

\Ch{C}{I h}ave felt Your to\Ch{Dm}{uch},

More \Ch{C}{int}imate that l\Ch{Dm}{ove}rs.
\end{SBVerse}
\begin{SBVerse}
Fr\Ch{F}{ien}d \Ch{C/E}{ fo}r -\Ch{G/D}{ ev} - \Ch{C}{er.}
\end{SBVerse}
\begin{SBVerse}
\Ch{C}{Wha}t a hope I've fo\Ch{Dm}{und},

More fa\Ch{C}{ith}ful than a mo\Ch{Dm}{the}r;

\Ch{C}{It }would break my he\Ch{Dm}{art}

To \Ch{C}{eve}r lose each ot\Ch{Dm}{her}.
\end{SBVerse}
\end{song}\begin{song}{When I Survey the Wondrous Cross}{D}
{Isaac Watts}
{Isaac Watts}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
(key of D)

\Ch{D}{Whe}n I survey the w\Ch{G}{ond}rous c\Ch{D}{ros}s

On which the \Ch{Em}{Pri}nce of g\Ch{G}{lor}y di\Ch{A}{ed }

\Ch{D}{My }richest gain I c\Ch{G}{oun}t but lo\Ch{D}{ss }

And pour cont\Ch{Em}{emp}t on a\Ch{G}{ll }m\Ch{A}{y p}r\Ch{D}{ide}
\end{SBVerse}
\begin{SBVerse}
(key of E)

\Ch{E}{For}bid it Lord, that \Ch{A}{I s}hould b\Ch{E}{oas}t

Save in the d\Ch{C#m}{eat}h of Ch\Ch{A}{ris}t my G\Ch{B}{od }

\Ch{E}{All} the vain things that c\Ch{A}{har}m me m\Ch{E}{ost}

I sacri\Ch{C#m}{fic}e them \Ch{A}{to }His b\Ch{B}{loo}d
\end{SBVerse}
\begin{SBVerse}
See, from His head, His hands, His feet

Sorrow and love flow mingled down

Did e'er such love and sorrow meet

Or thorns compose so rich a crown?
\end{SBVerse}
\begin{SBVerse}
Were the whole realm of nature mine

That were a present far too small

Love so amazing, so divine

Demands my soul, my life, my all
\end{SBVerse}
\end{song}\begin{song}{You Are Holy (Prince Of Peace)}{G}
{Tammi Rhoton}
{Tammi Rhoton}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{You} are holy (You are holy)

You are mig\Ch{C}{hty} (You are mighty)

You are wor\Ch{Am}{thy} (You are worthy)

Worthy of pr\Ch{D}{ais}e (Worthy of praise)
\end{SBVerse}
\begin{SBVerse}
I will f\Ch{G}{oll}ow (I will follow)

I will \Ch{C}{lis}ten (I will listen)

I will \Ch{Am}{lov}e You (I will love you)

\Ch{D}{All} of my d\Ch{G}{ays} (A\Ch{D}{ll }of my d\Ch{G}{ays})
\end{SBVerse}
\begin{SBVerse}
I will s\Ch{C}{ing} to, and wors\Ch{D}{hip}

the ki\Ch{Em}{ng }who is wo\Ch{Bm}{rth}y.

I will l\Ch{C}{ove} and ado\Ch{D}{re }Him,

i will b\Ch{Em}{ow }down bef\Ch{Bm}{ore} Him.

I will s\Ch{C}{ing} to, and wors\Ch{D}{hip}

the ki\Ch{Em}{ng }who is wo\Ch{Bm}{rth}y.

I will l\Ch{C}{ove} and ado\Ch{D}{re }Him,

I will b\Ch{Em}{ow }down bef\Ch{Bm}{ore} Him.
\end{SBVerse}
\begin{SBVerse}
You're my Pr\Ch{C}{inc}e of Peace, and \Ch{D}{i w}ill live my life for \Ch{G}{you}.
\end{SBVerse}
\end{song}\begin{song}{You Are Merciful To Me}{D}
{Ian White}
{Ian White}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
You are \Ch{D}{mer}ciful\Ch{A}{ to} \Ch{D}{me,}

\Ch{D/F#}{You} are \Ch{G}{mer}ciful to \Ch{D/F#}{me,}

You are \Ch{D}{mer}ciful\Ch{A}{ to} \Ch{G}{me,} \Ch{A}{my }Lord \Ch{D}{   }\Ch{Gmaj7/A}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{A2}{Ev'}ry\Ch{			}{ da}y \Ch{G/D			}{my }disobed\Ch{D}{ien}ce grieves Your loving heart;

but \Ch{Am7}{the}n \Ch{		}{red}eeming love breaks through,

and \Ch{G	}{cau}ses me t\Ch{A}{o w}orship You
\end{SBVerse}
\begin{SBVerse}
Re\Ch{D}{dee}mer, (Redeemer)

\Ch{Bm7}{Sav}ior, (Savior)

\Ch{G}{Hea}ler (Healer)

and \Ch{Asus}{Fri}end (and \Ch{A}{Fri}end)
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Ev'}ry day (Ev'ry day)

re\Ch{Bm7}{new} my ways, (renew my ways)

fill \Ch{G}{me }with love (fill me with love)

that \Ch{Asus			}{nev}er end\Ch{A}{s (}that never ends)
\end{SBVerse}
\end{song}\begin{song}{You Are My All In All}{G}
{Dennis Jernigan}
{Dennis Jernigan}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{You} are my st\Ch{D}{ren}gth when I am w\Ch{Em}{eak}

You are the \Ch{G}{tre}asure that I \Ch{C}{see}k

You are my \Ch{G}{all} \Ch{D}{in }\Ch{G}{all} \Ch{D}{   }

\Ch{G}{See}king You \Ch{D}{as }a precious \Ch{Em}{jew}el

Lord to give \Ch{G}{up,} I'd be a \Ch{C}{foo}l

You are my \Ch{G}{all} \Ch{D}{in }\Ch{G}{all} \Ch{D}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Jes}\Ch{D}{us,} L\Ch{Em}{amb} of G\Ch{G}{od,} w\Ch{C}{ort}hy \Ch{G}{is }Y\Ch{D}{our} \Ch{G}{nam}\Ch{D}{e  }

\Ch{G}{Jes}\Ch{D}{us,} L\Ch{Em}{amb} of G\Ch{G}{od,} w\Ch{C}{ort}hy \Ch{G}{is }Y\Ch{D}{our} \Ch{C}{nam}\Ch{G}{e  }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Tak}ing my \Ch{D}{sin}, my cross, my \Ch{Em}{sha}me

Rising \Ch{G}{aga}in, I bless Your \Ch{C}{nam}e

You are my \Ch{G}{all} \Ch{D}{in }\Ch{G}{all} \Ch{D}{   }

\Ch{G}{Whe}n I fall \Ch{D}{dow}n, You pick me \Ch{Em}{up }

When I am \Ch{G}{dry}, You fill my \Ch{C}{cup}

You are my \Ch{G}{all} \Ch{D}{in }\Ch{G}{all} \Ch{D}{   }
\end{SBVerse}
\end{song}\begin{song}{You Are My King (Amazing Love)}{D}
{Billy James Foote}
{Billy James Foote}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{D/F#}{   } I'm forg\Ch{G2}{ive}n, be\Ch{Asus}{cau}se You were for\Ch{A}{sak}en

\Ch{D/F#}{   } I'm acce\Ch{G2}{pte}d,\Ch{Asus}{   } You were cond\Ch{A}{emn}ed

\Ch{D/F#}{   } I'm ali\Ch{G2}{ve }and well, Your \Ch{Asus}{Spi}rit is with\Ch{A}{in }me

    Bec\Ch{G2}{aus}e you \Ch{A}{die}d and rose a\Ch{D}{gai}n
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{Ama}zing love, \Ch{G}{how} can it be

\Ch{D}{Tha}t You my king would die for \Ch{Asus,}{me?}   \Ch{A}{   }

\Ch{D}{Ama}zing love, \Ch{G}{I k}now it's true

\Ch{D}{And} It's my joy to honor \Ch{Asus,}{You}   \Ch{A}{   }

In all I \Ch{G}{do }\Ch{A}{  I} honor \Ch{D}{You}
\end{SBVerse}
\begin{SBVerse}
\Ch{D}{You} are my king, \Ch{D}{You} are my king

\Ch{D}{Jes}us, You are my king, \Ch{D}{Jes}us, You are my king
\end{SBVerse}
\end{song}\begin{song}{You Never Let Go}{A}
{Matt Redman}
{Matt Redman}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
Even though I \Ch{A2}{wal}k 
\end{SBVerse}
\begin{SBVerse}
through the valley of the shadow of death, 

Your p\Ch{D/F#}{erf}ect love is casting out fear. 

And even when I'm \Ch{A2}{cau}ght 
\end{SBVerse}
\begin{SBVerse}
in the middle of the storms of this life, 

I \Ch{D/F#}{won}'t turn back, I know You are near. 
\end{SBVerse}
\begin{SBVerse}
And I will fear no \Ch{F#m}{ev }  \Ch{E}{-  }\Ch{A2}{il,} 

For my God is \Ch{F#m}{wi }- \Ch{E}{th }\Ch{A2}{me.} 

And if my God is \Ch{F#m}{wi }- \Ch{E}{th }\Ch{A2}{me,} 

Whom then shall I f\Ch{E}{ear}? 

Whom then shall I f\Ch{D2}{ear}? 
\end{SBVerse}
\begin{SBVerse}
\Ch{A2}{Oh }no, You never let go, 
\end{SBVerse}
\begin{SBVerse}
Through the calm and through the storm 

\Ch{F#m}{Oh }no, You never let go, 
\end{SBVerse}
\begin{SBVerse}
In every high and every low 

\Ch{E}{O n}o, You never let go 

\Ch{D2}{Lor}d, You never let go of \Ch{A2}{me.}\Ch{Esus}{   }  \Ch{D2}{   }
\end{SBVerse}
\begin{SBVerse}
And I can see a l\Ch{A2}{igh}t 
\end{SBVerse}
\begin{SBVerse}
that is coming for the heart that holds on 

A g\Ch{D/F#}{lor}ious light beyond all compare. 

And there will be an \Ch{A2}{end} 
\end{SBVerse}
\begin{SBVerse}
to these troubles, But until that day comes, 

We'll \Ch{D/F#}{liv}e to know You here on the earth. 
\end{SBVerse}
\begin{SBVerse}
Yes, I can see a l\Ch{A2}{igh}t that is coming 
\end{SBVerse}
\begin{SBVerse}
for the heart that holds on, 

And there will be an \Ch{F#m}{end} to these troubles, 
\end{SBVerse}
\begin{SBVerse}
but until that day comes, 

\Ch{Esus}{   }Still I will praise You, 

\Ch{D2}{   }Still I will praise You, \Ch{A2}{   }\Ch{Esus}{   }  \Ch{D2}{   }
\end{SBVerse}
\end{song}\begin{song}{Your Grace Is Enough}{G}
{Matt Maher}
{Matt Maher}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{Gre}at is your f\Ch{G/B}{ait}hfulness oh \Ch{C2}{God}

\Ch{Em}{You} wrestle w\Ch{D}{ith} the sinners h\Ch{C2}{ear}t

\Ch{G}{You} lead us \Ch{G/B}{by }still waters \Ch{C2}{and} to mercy

\Ch{Em}{And} nothing \Ch{D}{can} keep us a\Ch{C2}{par}t
\end{SBVerse}
\begin{SBVerse}
So re\Ch{Am7}{mem}ber your \Ch{G/B}{peo}ple

Rem\Ch{C2}{emb}er your ch\Ch{D}{ild}ren

Re\Ch{Am7}{mem}ber your \Ch{G/B}{pro}mise

Oh \Ch{C2}{God}
\end{SBVerse}
\begin{SBVerse}
Your \Ch{G}{gra}ce is en\Ch{D}{oug}h

Your \Ch{Em}{gra}ce is en\Ch{C2}{oug}h

Your \Ch{G}{gra}ce is e\Ch{D}{nou}gh for \Ch{C2}{me }
\end{SBVerse}
\begin{SBVerse}
\Ch{G}{Gre}at is your \Ch{G/B}{lov}e and justice \Ch{C2}{God}

\Ch{Em}{You} use the w\Ch{D}{eak} to lead the s\Ch{C2}{tro}ng

\Ch{G}{You} lead us \Ch{G/B}{in }the song of \Ch{C2}{you}r salvation

\Ch{Em}{And} all your \Ch{D}{peo}ple sing \Ch{C2}{alo}ng
\end{SBVerse}
\begin{SBVerse}
So re\Ch{Am7}{mem}ber your \Ch{G/B}{peo}ple

Rem\Ch{C2}{emb}er your ch\Ch{D}{ild}ren

Re\Ch{Am7}{mem}ber your \Ch{G/B}{pro}mise

Oh \Ch{C2}{God}
\end{SBVerse}
\begin{SBVerse}
Your \Ch{G}{gra}ce is e\Ch{D}{nou}gh

Heav'n \Ch{Em}{rea}ching down to \Ch{C2}{us }

Your \Ch{G}{gra}ce is e\Ch{D}{nou}gh for \Ch{C2}{me }

God, I see Your \Ch{G}{gra}ce is \Ch{G/B}{eno}ugh

I'm \Ch{Em}{cov}ered in your \Ch{C2}{lov}e

Your \Ch{G}{gra}ce is e\Ch{D}{nou}gh for \Ch{C2}{me }
\end{SBVerse}
\end{song}\begin{song}{Your Love Oh Lord}{G}
{David Carr}
{David Carr}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
\Ch{G}{You}r love oh \Ch{C9}{Lor}d reaches to\Ch{G}{ th}e he\Ch{D/F#}{ave}ns

\Ch{Em7}{You}r faithfulness s\Ch{C9}{tre}tches to the s\Ch{G}{ky } \Ch{D/F#}{   }

\Ch{Em7}{You}r righteou\Ch{C9}{sne}ss is like the mighty \Ch{G}{mou}ntain \Ch{D/F#}{   }

\Ch{Em7}{And} Your justic\Ch{C9}{e f}lows like th\Ch{G}{e o}ce\Ch{D/F#}{ans} tides
\end{SBVerse}
\begin{SBVerse}
\Ch{D/F#}{And} I will lift my v\Ch{D}{oic}e to w\Ch{C9}{ors}hip you my \Ch{G}{Kin}g

\Ch{G}{And} I will find my s\Ch{D}{tre}ngth in the s\Ch{C9}{had}ow of Your \Ch{Am}{win}gs\Ch{D}{   }
\end{SBVerse}
\end{song}\begin{song}{Your Name}{G}
{Glenn Packiam}
{Glenn Packiam}
{}
{}

\renewcommand{\RevDate}{October~23,~2012}
\begin{SBVerse}
As \Ch{G/B}{mor}ning \Ch{Cadd9}{daw}ns and \Ch{D}{eve}ning \Ch{G5}{fad}es

\Ch{G/B}{You} ins\Ch{Cadd9}{pir}e   \Ch{D}{son}gs of \Ch{G5}{pra}ise

That \Ch{G/B}{ris}e from \Ch{Cadd9}{ear}th to to\Ch{D}{uch} Your \Ch{Em7}{hea}rt

and \Ch{Cadd9}{glo}ri - \Ch{D}{fy }Your \Ch{G5}{Nam}e
\end{SBVerse}
\begin{SBVerse}
Your N\Ch{Bm7}{ame}  \Ch{Em7}{  i}s a \Ch{G5}{str}ong and mighty \Ch{C2}{tow}er

Your Na\Ch{D}{me }\Ch{Em7}{   } is a \Ch{G5}{she}lter like no \Ch{C2}{oth}er

Your Na\Ch{D}{me,}\Ch{Em7}{   }let the n\Ch{G5}{ati}ons sing it l\Ch{C2}{oud}er

'Cause \Ch{G/B}{not}hing has the p\Ch{C2}{owe}r to \Ch{Dsus}{sav}e  \Ch{D}{   }

But Your \Ch{G/B}{Nam}e \Ch{Cadd9}{   }    \Ch{D/F#}{   }   \Ch{G5}{   } \Ch{G/B}{   }  \Ch{Cadd9}{   }    \Ch{D/F#}{   }   \Ch{G5}{   }
\end{SBVerse}
\begin{SBVerse}
\Ch{G/B}{Jes}us, \Ch{Cadd9}{in }Your \Ch{D}{Nam}e we \Ch{G5}{pra}y

\Ch{G/B}{Com}e and \Ch{Cadd9}{fil}l our \Ch{D}{hea}rts to\Ch{G5}{day}

Lord, \Ch{G/B}{giv}e us st\Ch{Cadd9}{ren}gth to l\Ch{D}{ive} for You

\Ch{Em7}{and} \Ch{Cadd9}{glo}ri - \Ch{D}{fy }Your \Ch{G5}{Nam}e
\end{SBVerse}
\begin{SBVerse}
Other (Musical Interlude):
\end{SBVerse}
\begin{SBVerse}
Your N\Ch{D}{ame}\Ch{Em7}{   } is \Ch{G5}{a s}trong and mighty \Ch{C2}{tow}er

Your N\Ch{D}{ame}\Ch{Em7}{   } is a \Ch{G5}{she}lter like no oth\Ch{C2}{er }

Your N\Ch{D}{ame}\Ch{Em7}{,  } let the \Ch{G5}{nat}ions sing it lo\Ch{C2}{ude}r

'Cause \Ch{G/B}{not}hing has the \Ch{C2}{pow}er to \Ch{Dsus}{sav}e \Ch{D}{   } but

[Repeat Chorus 2x]
\end{SBVerse}
\begin{SBVerse}
(3rd ending for Chorus 2)

'Cause \Ch{G/B}{not}hing has the \Ch{C2}{pow}er to \Ch{Dsus}{sav}e \Ch{D}{   } but Your Name
\end{SBVerse}
\begin{SBVerse}
Outro:

\Ch{G/B}{[Re}pe\Ch{C2}{at]} \Ch{D}{   }\Ch{G5}{   } \Ch{G/B}{   }  \Ch{C2}{   } \Ch{D}{   }\Ch{G5}{   }
\end{SBVerse}
\end{song}

\begin{center}
{\myTitleFont Title Index}\end{center}
\vskip 20pt

\begin{itemize}
\input{abba.tdx}
\end{itemize}

\end{document}  

